Hi, I'm back again!

As the last story was quite long, this one will be a bit shorter (just a bit); on the other hand, I'll try to improve the quality of my language. So just one thing: Enjoy it!
(No, I don't run out of ideas; I only run out of the courage to remember, as such hard pain is difficult to endure.)

\textbf{Here we go again:}
\textbf{[u]The Roots of Evil[/u]}
Today was the day he had feared: The day after the day that should have been perfect. However, as fate always does, it betrayed him: This day was better than the last one, but finally, he didn't really enjoy it, as he seemed to hang around with the wrong crowd. To the normal, untrained eye of a human being he would have looked happy, enjoying these people, but if there ever was to be a person that understood him --- THAT is to say, the person everybody all out the world is searching for --- she would have noticed he was just pretending, hoping to be beamed away every second. Of course, he wasn't; His profiling system was built up so perfect that no doctor could find out what he really felt, as all the endorphines and hormones that give us living creatures the strange feeling of happiness could have been found in his blood. But in a secured area of his brain, he was ill, sick and feeling blue, something only one person could have changed, but this creature was sitting some rooms away. Of course, he could have joined her to watch what she did, but he had noticed that fate wouldn't give him a chance of being talked to. And finally, he had told her and her best friend about a possible meeting at the place where he dwelled at that moment, but both had forgotten, and he was not to be the person to remind them. Enjoying themselves, they were ingored by him in the part of his brain he could control; but his emotions were yet to be killed. 
I guess you all want to know what had happened, who the persons were we caught him thinking of and if he would ever be happy again; I can just answer the first two questions by telling you everything he knew, but the last one still is to become reality under the cruel, but fair influence of the hand of fate. 
We'll now go back to the point where we'd stopped; he had just fallen in love with G. and was now to be controlled by his emotions. However, we all know that pretty women can be roots of evil without knowing what they're doing or intending it; if you didn't ever experience that, you'll now. 
We'll ignore for the moment that he thought of her about 80% of the time, while surprisingly, his marks didn't change for the worse; we'll also ignore his dreams, as today, he's already stowed away nearly all of them and neatly arranged the packet in a corner of his mind where he would never stumble into it again, though this was another trauma that still influences him today. What we'll look at are his encounters, his first contacts, and we'll analyze some of them to find out about his way of thinking. 
Looking back, it happened quite fast: After knowing and secretly loving her for about half a year --- the time he was captured in the depression --- he made real contact for the first time. This included finding out about her character, her style of talking and the art with which she selected her words; the way she cocked her head to the left or to the right when she was explaining or telling something, or the loud laugh that escaped her mouth when she was told something funny. She laughed often, more often than O. did, but when he looks back at it today he thinks that she laughed about things that were too simple. O. preferred more complex jokes, puns --- and already produced them herself. But we'll come to her later; for the moment, we'll try to discover G. the same way he did. 
One of the moments he remembers most strongly was the minute when he presented her something he'd done for school; he'd included a message for her among the things he did for a kind of project. As both O. and G. were quite happy with leading or coordinating such projects, he could give it to her:
She was sitting on a chair in the crowd you always find at a school; he was talking to a group of his "friends". While he was talking, he was watching her by moving his eyes so fast as if you'd seen a lightning; so fast nobody seemed to notice it, and if they did, they didn't mention it. That was a method he used quite often, and he was well acquainted with performing this art. When he realized she was sitting on her own, staring into the crowd, he took out the texts he'd prepared and walked over to her, holding his work in his left hand. After the delivery of that thing he'd prepared for hours, he knew that one of his major errors was that he'd used his left hand, as one may notice that the left part of the body is connected to the right part of the brain which is responsible for thinking with images --- and emotions. Mumbling to her it was something for the project and handing it over, he watched his hand that began to shake violently, at least one inch to the left and back to the right; he couldn't keep it calm, and the more he tried, the worse it was. At the same time, his heart beat so fast he feared he would collapse; of course he didn't, but his major fear was that she'd notice and he'd have to search for an explanation. She didn't, though she blinked at his hand shortly to grab the texts, smiling at him and telling her friends she'd just received some new papers. After she'd thanked him shortly, he went back to his friends as fast as he could, cautiously keeping her in sight and slowly calming down. When he was back to the group that just stood something about one metre away, nobody who wasn't really aware of his senses would have noticed the way he was shaken inside. All of it was over in less than one minute, or even half a minute; time was something he didn't have the time to look at in this moment. 
As trained reader or psychologist you'd have noticed that she wasn't aware of her senses, and that people who are in love are; thus, you'd have found out that she'd never love him or was simply to shallow to be aware of the details all around us, while he was able to sit somewhere and switch inside a conversation, simply listening and understanding several things at the same time, noticing more details in a second than the group that was talking to each other would have noticed in months. 
But also this gift wouldn't save him. 
We could list other events like this, but we'd always end at the same point: A kind of friendship developed, and finally he knew some things about her, but not a sign of love was to be seen. At the same time, another person appeared to play a role in his life: O. was becoming an active part of his life without him noticing it before it was too late. 
But that's a story that belongs to another heading; G. and O. are both having a boyfriend today, everybody has somehow developed to a couple, while he is still searching for himself. You see we are yet to walk a long way together if you like to read all my texts and thus my complete story; I hope you've come to know me by now and developed your own opinion; and I believe that you think that things couldn't be more complex, but you'll see they'll always change for the worse which seems to be one of the rules of life. 
To be continued...
This week, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

The greatest thing
you'll ever learn
is to be in love
and to be loved
in return. 
\emph{(extract from a famous English song; I'm sorry I don't remember it's name, and I'm not sure if the text is completely correct)}

The only good is knowledge and the only evil ignorance. 
\emph{(from a small fortune cookie program)}
