Hi again! Hope you're still with me!

One may ask me how the story is to be continued, but I won't be able to answer, as I'm writing in real-time, and reality can't --- or shouldn't --- be predicted, as we've already found out. Thus, the only thing you can do is join me and wait and see: 

\textbf{The final question is: Shall we}
\textbf{[u]Wait and See?[/u]}
Sunday; and nothing had happened. Two weeks ago, his contacting attempt had been started, and there was still no response, though he'd told her about it. He began thinking she had been playing a kind of game with him, but the anger this offense was causing didn't cease to feed his love, so it grew even more powerful. 
Today, he'd remembered something he just memorized yesterday without understanding it: The moment he was listening to the radio and wondering about the antenna in front of the portrait, he had a look at a cheap clock, which never showed the right time, as it was going faster that it should. 
It showed 3:43 pm, but as this thing wasn't a projecting clock, he didn't see something peculiar, though he felt he was remembered of something special. 
Today, he'd noticed that similarity; it was another sign he didn't want to figure out. 
The day before yesterday, there was another sign he was just contemplating about today, and I want to tell you about it: He'd watched a film with a guy who shared his name. He came back after years to the woman he'd loved when he was young, and she was married to somebody else. An affair seemed inevitable, but she decided to stay with her husband, telling him he was too late. 
Would the same thing happen to him and O.?
Was there always something wrong in life, some timing you didn't get right because you just decided to wait and see?
There's a famous song from Chris de Burgh which is called 'Timing is everything'; There's no need to quote it here, I guess you already know what it's about; However, in that song, the man finally gets it right when he runs into the church and gets her right before she would have married somebody else. 
He thought he would never be able to do such a thing; he'd simply sit there, if he happened to be invited to such a ceremony, and look, with a cold face, while inside him, his heart would be pounding with strong emotions. Maybe, a single tear would drop from his eye, but everything else would be concealed; Maybe, he'd even cease to breathe in the middle of the ceremony and slowly fall to one side without anybody noticing it. That was the way he controlled himself; But somebody who really wished to see into his soul could do so, and she could have done. 
He'd just found an old song, a tune that seemed familiar, but hadn't been so successful:
[quote]
I've seen you twice, in a short time 
Only a week since we started 
It seems to me, for every time 
I'm getting more open-hearted 
 
I was an impossible case 
No-one ever could reach me 
But I think I can see in your face 
There's a lot you can teach me 
So I wanna know.. 
 
What's the name of the game? 
Does it mean anything to you? 
What's the name of the game? 
Can you feel it the way I do? 
Tell me please, 'cause I have to know 
I'm a bashful child, beginning to grow 
 
And you make me talk 
And you make me feel 
And you make me show 
What I'm trying to conceal 
If I trust in you, would you let me down? 
Would you laugh at me, if I said I care for you? 
Could you feel the same way too? 
I wanna know.. 
 
The name of the game 
 
I have no friends, no-one to see 
And I am never invited 
Now I am here, talking to you 
No wonder I get excited 
 
Your smile, and the sound of your voice 
And the way you see through me 
Got a feeling, you give me no choice 
But it means a lot to me 
So I wanna know.. 
 
What's the name of the game? (Your smile and the sound of your voice) 
Does it mean anything to you? (Got a feeling you give me no choice) 
(But it means a lot) 
What's the name of the game? (Your smile and the sound of your voice) 
Can you feel it the way I do? 
Tell me please, 'cause I have to know 
I'm a bashful child, beginning to grow 
 
And you make me talk 
And you make me feel 
And you make me show 
What I'm trying to conceal 
If I trust in you, would you let me down? 
Would you laugh at me, if I said I care for you? 
Could you feel the same way too? 
I wanna know.. 
Oh yes I wanna know.. 
 
The name of the game (I was an impossible case) 
Does it mean anything to you? (But I think I can see in your face) 
(That it means a lot) 
What's the name of the game? (Your smile and the sound of your voice) 
Can you feel it the way I do? (Got a feeling you give me no choice) 
(But it means a lot) 
What's the name of the game? (I was an impossible case) 
Does it mean anything to you? (But I think I can see in your face) 
(That it means a lot) 
\emph{('The Name of the Game', written by Benny Anderson, Stig Anderson and Bjorn Ulvaeus)}
[/quote]
It appeared to him he was asking himself the same questions all the time; He just wanted to \emph{know} without wishing to know anything at the same time, as knowledge might give him a fright. 
He was as bashful as the person in the song before he'd met her, and the only thing anybody would see was the result of his profiling system. When she came, he tried to open up, and now he seemed to be closing again. 
It seemed hopeless, if she didn't come back. 
Like the guy in the song, he'd always \emph{thought} he could see in her face that it meant a lot; But in fact, all of it could have been a part of a vicious game or just an illusion of an equal vicious imagination searching for something beautiful to appreciate. 
He hadn't seen the painted red heart showing the initials of her and her boyfriend since about seven days, but that didn't mean a thing, as it had been drawn in her folder, and she'd decided to get a new one. 
Nothing meant a thing, it occured to him. 
He had a look around, hoping to see something that would remind him of her or cast back some remembrances, but there was nothing outside; He would have to close his eyes, and he feared to do so. 
He did, finally. Seeing her face appear in front of his closed eyes, he opened them again, as a wave of pain was running along his spine and last bits of hope seemed to be flickering along. 
They would be ignored, for the sake of a better future. 
He struggled to open his eyes again, and finally, he managed to do it; He didn't dare to close them again until he'd have to sleep. 
Consciously, he listed all the things he knew about her: Her full name, her nickname, her password she'd always used, her E-Mail-Adress, her phone number, her house number, the place where she lived, even the exact location of the room; but it was nothing, he noticed, as the final question wasn't answered. 
Was he in any way relevant to her?
Maybe he'd find out tomorrow. 
Maybe he'd never know. 
For now, he'd tried to organize everything; an excursion together with another group of students, which she would be in, though it was quite inprobable that they would be able to join that excursion; the contacting attempt he'd started long ago; and these texts she'd probably find, but he was quite sure she wouldn't read them if she didn't know he'd written them just for her. 
Maybe, this condition was to stay; then, hope would have died. 
But for now, we can just wait and see, as further acting would probably make things worse. 
Are you still there? Please give me your opinions...........
To be continued...
This week, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

Life's not controlled by a dice:
Everybody can make a choice between predefined ways. 
Make yours now!
\emph{W.G.}

Life is live;
Don't expect you can simply press Ctrl+S,
to go back later;
Backup is impossible!
Thus,
errors and corrupt data
are natural. 
\emph{W.G.}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_First_Era.tex"
%%% End:
