Hi, it's me again!

A puzzling day dominated by new sensations; read it and find out what has happened!

\textbf{The story of the}
\textbf{[u]Stupefied Soul[/u]}
Thursday, that was the day it was. The day of chaos, when everything would be mixing together. 
And it did. 
In the morning, there was that small girl in the bus again, talking to him, but less than the last time; most of the things one could say had been said already. 
When he arrived at university, two of his lectures had been cancelled; but he'd known about that already the day before. 
Before his first lecture would begin, he sat down in the library, waiting for his best friend to arrive to do some studies together. But as things always decide to go different, they finally just fooled around all the time. When his first lecture would begin, he was waiting in front of the auditorium with his fellow students, when O. passed by, talking to his friends --- but not to him. He knew he had to ask her about that transportation problem he'd have next week, and so he finally managed to stop her and her best friend from leaving by asking her this question. 
Believe it or not; his heartbeat still increased, and he felt his guts contract to increase the amount of endorphines that kept pulsating in his blood. The idea of butterflies being caught in his stomach suddenly occurred to him as something realistic, and he knew that the process of forgetting her hadn't been finished yet. Maybe, this was just some physical reaction he couldn't ever do something about; but when he saw her wearing that white blouse...
CUTOFF!
He'd have to endure and persist. 
This was the only thing he could do. 
You may now ask what had happened after he'd asked that question: She'd told him to ask one of her friends, as she seemed not to be able to use her car that week. Her foot was hurt, he knew that; maybe, this was the cause. 
For everything: The ignorance, the sudden tranquillity and aura of silence that seemed to have befallen her. 
CUTOFF!
He was not allowed to think about such details. 
His plan should be without a flaw. 
Then, finally, she was gone, together with her best friend; he just called "Goodbye!" after her, but she didn't seem to notice. 
CUTOFF!
It was over, she was away, and another memory --- this time, a recent one --- was put in the adamant case. 
After his lecture was finished, both of them had a long break. He saw her, and he heard her voice, while they were residing in the cantine; when she went to the litter bin for the second time, she passed him by and asked from about one metre's distance, whether he'd asked her friend yet. He hadn't, as he hadn't seen her yet, and he told her so. 
Now, he wasn't capable of hearing her voice anymore; it sounded too familiar, and too strong emotions were connected to it; he decided to go to the library again, where he would be alone till L.-B. arrived again and was getting on his nerves --- again. 
However, he managed to be a real bore, and he managed to be alone again about 20 minutes later; some new record!
He was happy about it, but P. wasn't there today to share that feeling --- he didn't know where she was. 
Thus, he was deemed to be alone, but he preferred that to being together with L.-B. 
Finally, he was happy. 
The next lecture began; just after he was seated, he was somehow irritated, as the girl sitting next to him seemed to be completely puzzled. Thursday was the day she hated, she told him. Well, now he was puzzled, too. 
But that was of no real interest to him, as he soon was okay once more --- and she was, too. 
This time, I'll give you some more of my poetry, as I've met O. so often that my method should be enforced several times, this limiting my time to write a longer post --- today. 


Some think, they know life:
"Hey, where's its price?"
But life is not for sale.
Some think, they know love:
"Without it, I'll be better off!"
But love is not to be dumped.
Some think, they know me:
"He's ambitious though he's free!"
But no person is ever to be known. 
\emph{W.G.}


As rain keeps falling down
on me;
thousand people frown
and see.
But you keep standing right inside
not caring about cold or tide;
you now the best is yet to come:
The moment, when the clouds are gone;
you feel the warmth of mighty sun
yet the rain still plays for fun. 
\emph{W.G.}


Think of past and think of future:
They go together, leaving us stuck in between. 
\emph{W.G.}


The flood is coming:
Houses burst and fall apart
some people even call it art
as death now does its masterpiece;
The flood is coming,
killing me, killing you
dragging us apart;
but I know he'll never win
as he can only end our lives
and not our love;
The flood is coming --- the final unity.
\emph{W.G.}


Beware of pride without substance!
\emph{the \textbf{"Book of Changes"} --- I received this answer when enquiring about G. several times; if you want to know more about this divination / fortune-telling method, search on the world wide web for "I Ging"}


There is a smile of Love,
And there is a smile of Deceit,
And there is a smile of smiles
In which these two smiles meet. 
\emph{William Blake (1757-1827), Smile and Frown}


"I wish..." she said, and stopped. There was nothing that could be gained by wishing for it. A final deep shaky breath, and she was ready to go on.
\emph{Philip Pullman, His Dark Materials 1: Northern Lights --- This symbolizes my \textbf{wish} to change something easily, but it's impossible; as we already learned, hopes are never to be fulfilled}


We would often be sorry if our wishes came true. 
\emph{(from a small fortune cookie program) --- Here, you can see one explanation if wishes sometimes happen to come true, as they can only become part of reality if they change it for the worse}

Keep your eyes open, and take advantage of the unexpected. 
\emph{(from a small fortune cookie program) --- that also explains why we shouldn't hope, so that our best possible future can arrive unexpectedly}


In silence man can most readily preserve his integrity. 
\emph{(from a small fortune cookie program) --- That explains why I'm doing these sessions to forget her, and why I like to rather be left alone than to be together with L.-B.; but finally, I don't want to be alone}


Hang on for a minute; there was some German quotation I've heard, I'll search for it, as it fits here perfectly!

There it is: 

Die Einsamkeit ist schoen, aber der Mensch braucht einen, der ihm immer wieder sagt, dass die Einsamkeit schoen ist. 
\emph{Honoré de Balzac}


With these things at hand to contemplate about my situation, I'm saying goodbye again --- till tomorrow. 
Waiting for your opinions...........
To be continued...
This week, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

Sometimes,
being a bore
can be more interesting
than being a genius. 
\emph{W.G.}

The snow was slowly touching the ground. 
A cold wind began to blow; 
all the things and creatures
suddenly held their breaths and watched
standing there in awe;
When the clouds fought the sun, 
he was the only one to know
a summer was to come
as balance --- 
the focus on the number 'zero' --- 
is the basic law of the universe. 
\emph{W.G.}
