Here we go again.............

I'm still longing for your experiences, and I beg you to read those texts; they are my life, and I want to share it with somebody, who doesn't know me and my profiles; Somebody, who will --- through these texts --- gain access to my innermost feelings and the things happening below that shell of profiling I can't escape on my own. 

\textbf{Another time:}
\textbf{[u]The End?[/u]}
Monday --- everything had changed, but he didn't expect anything else; Well, at least subconsciously, as you've already learned that our expectations are never fulfilled. 
This way, reality gains it complexity. 
As he knew that, he tried not to expect things consciously; Thus, his subconscious expectations could be fulfilled. 
And they were. 
Always. 
Even, if he didn't realize them. 
That day, he knew there would be a lot of complexity, and in fact, there was. 
However, somehow, everything was sorted out, all the same. 
But some of these theories we've had a look at here --- and some of the methods he'd used for divination --- seemed to be proved wrong. 
Before we start, we'll have a look at the statement this fortune cookie program gave him today: 
[quote]
Try something new. 
\emph{(from a small fortune cookie program)}
[/quote]
Further inquiries he tried to answer with his fortune telling method told him, that he should be more offensive; and, additionally, that he should concentrate on O. 
Thinking about this results carefully, he requested further information; some parts of the future were forbidden to him, as the knowledge of these would have changed his destiny --- for the worse. 
But he realized that she would do the first step, and that he simply would have to agree. 
But today, she didn't. 
Sometimes, he'd realized, the results he received would apply to the next day; but he didn't believe in these, really, as they'd also told him that O. was single again --- since something about three weeks. 
Well, she wasn't. 
And he knew that for sure, as she'd told him today. 
But we'll now start over with the beginning. 
However, this time, there'll be a lot of details he's bound not to talk about, as otherwise, this post would be far too long. 
That day, he spent more time together with O., her best friend and G. than for the time since the beginning of the year. 
Right now, we'll focus on several details, and analyze his reactions. 
O. was ironically, if possible, even more than on the other days. After she'd told him that she'd take seat next to him before the start of an exam (so as not to fail it), she sat down several metres away; she was just \emph{joking}. 
And she enjoyed it. 
The next peculiar detail was her ignorance, again; Though she seemed to care for him (in some friendly manner), she forgot the few words he'd said to her in a moments time. 
Sometimes, he had to repeat some fact for three times; and she was capable of remembering such simple things after the first time, much better that G. would. 
At some occasions, he was talking to her best friend, as she occasionally also ignored her speaking. 
Finally, when the three of them were \emph{united} again, her best friend talked --- most of the time. When he told her something, she sometims didn't realize it, though her best friend was talking to somebody else, not mentioning something really important. 
He pretended to ignore her once, though he perfectly understood what she had said; She didn't react to that in any way. 
Then, there was something else happening for the second time; Repititions could always be important signs. 
When O. sat next to him, G. made some silly remark that he liked to be sitting back there. Then, she excused herself for having done so, laughing. 
About one month before, he'd sat next to O.; and somebody --- G., in fact --- had said that the two of them were sitting as if waiting for the dentist to come. 
As if in a queue; the two of them; a couple that could never be......
\textbf{CUTOFF!}
It was over; stick to the present!
\textbf{FLASHBACK}
Something that had just happened after G.'s remark, today. 
The memory jumped back into the centre of his thoughts without invitation, and he couldn't simply send it away..........
There was the sun shining, and it met O.'s eyes. 
They were shining in some dark, mysterious, intelligent and interesting brown colour; he could feel the power of this shining rays that mirrored themselves in that mirror of her soul so perfectly......
A power that part of him would never escape; some thing inside him would stick to it, being captured by that alien energy, without any possibility to come back. 
Maybe, this was the best choice he could make: Leaving part of him behind, with her, heading into a new direction.......
Which direction?
He looked into some real mirror just in front of him; G.'s profile, her nose, was perfectly lined in the reflection.......
CUTOFF!
That was over, long ago. 
Memories had buried these emotions, that had never been real. 
Possibly, it was the same with his feelings for O.; but somehow, everything seemed different. 
When he closed his eyes now, there was something he'd see; not O.'s eyes, not her face; something that belonged to her, something she'd remarked something about, the only thing he'd decided to ignore on purpose, and all the same the last image he'd kept of her. 
But it was something material. 
If he crushed that image in his mind, it would be gone. 
However, he was wondering if he would do it; if he should do it. 
Part of him was full of sorrow, and another part longed for salvation from the unendurable pain he was feeling. 
It had been subsiding, but now, it was just waiting for his decision; He knew that this would be the final week. 
The day before yesterday, he'd looked into the mirror, into his own very eyes; they had lost colour, they'd become more transparent. 
Probably, this was one effect of his lack of sleep; on the other hand, this could be the sign of a love that was ignored and silenced by logic. 
An emptiness, a hole of emotion, is comparable to a black hole; it sucks out all emotion, and all colour there is. 
The next day, the colour seemed to come back, as his love wasn't completely forgotten; Still, he couldn't help but think of her. 
He was pretty sure he remembered more details about her life than anybody else; more, than her boyfriend, more, than her best friend; he could nearly \emph{feel} himself listening himself to the exact words she'd once told him, reciting these masses of information all the time; and once, when he was thinking of his own phone number, he just happened to remember hers, and not his. 
22 minutes this time, to wait for the bus, standing in the cold; waiting, and thinking. 
Thinking about the way both of them did the the other wrong. 
Thinking about the way fate would laugh about these happenings. 
Remembering himself having laughed at the craziness --- and the cruelty --- of fate. 
All of it was gone. 
Only emptiness had been left. 
Today, she'd even told him not to join her best friend in her sudden friendship to Y. 
Y..............
She was alone again, since that very day. 
In the morning, she'd told her boyfriend that they are not a couple anymore. 
As far as our protagonist was informed, he must have reacted with something like "Okay", and probably some smile. 
That was the way those foolish, childish relationships were put into practice. 
And he'd always believed that O. was different........
\textbf{FLASHBACK}
It was still the same day, just some hours earlier. 
Several times, O. was talking about her boyfriend --- to him. 
That was the most important fact that told him that there was no such thing as love between them. 
And that there would never be. 
However, he continued to help her as best as he could, answering all the questions she'd asked him --- as long as he was capable of doing so. 
And sometimes --- most times --- he even answered questions she had directed at somebody else, as she didn't ask him a lot of questions. 
But the happiness that was then developing in her face was just some kind of silly vision. 
Just pretending..... profiling.....
Something else the two of them had in common. 
But he could never believe that she was doing the same thing he did. 
She would never apply such harsh, psychological methods to forget a \emph{boy}. She would simply talk to him. 
But she didn't; Thus, all of it was just an image his fantasy had developed. 
This blending, completely logical fact would probably subdue his feelings once more; At least, it was worth a try. 
Another boy had been approaching her for some times, presenting her some gift and talking to her --- too much. 
He knew that guy; He already had a girlfriend, and probably, he'd never presented her a thing. 
O. knew that, but after she'd thanked him, this action was forgotten --- for her. 
She didn't see that he was feeling something, and if she did, she pretended not to have done. 
\textbf{FLASHBACK}
He'd also presented her a gift. 
She hadn't even had a look at it.
And every time he'd asked her she pretended to feel guilty, and called herself an idiot, not changing a thing by doing so. 
She did that on purpose, it occured to him; The same inexplicable purpose that kept her from calling him on the phone, though he'd given her his number and told her she could always ask him for help. 
And he could help, she knew that. 
With nearly everything. 
Just by listening, understanding --- and explaining. 
Probably, that was just the thing she feared.........
And she seemed to believe that her boyfriend knew about everything. 
As our protagonist was acquainted with some parts of psychology, he had just made some discovery: Was this an example for the Oedipus-Complex? Was she searching for some father to love, a person that protects her and knows everything?
Or at least: Somebody who pretends to do so?
He was thinking about it. 
Thinking hard. 
Really hard. 
If that was true, it would explain several interesting details. 
In addition to that, it would show that she was still some sort of child. 
And: She would hopefully find out, in the future. 
Then, she would have changed. 
Would that be the time of his chance?
Probably. 
But he didn't know if there would be some radical change in their lives up to then. 
And most probably, taking into account all the things he knew, there would. 
Which implied, that there wouldn't. 
Which furthermore induced he thought, that it was completely random. 
Crazy. 
Life is crazy. 
Completely. 
You can only sustain this, if you are crazy yourself. Only logical cratures commit suicide, as they don't understand th reality of life. 
Nobody did, and only the crazy people who accepted that would be able to persist. 
Or the other crazy persons who never thought about such things. 
Which group do you belong to?
Decide on you own, and please give me your answer --- and your opinions........
To be continued...
This week, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

The fire 
that never dies 
is a fire of pain; 
The fire 
that's never lighted 
is a fire of cold;
And the fire 
that dies, 
only to be born again, 
all around the clock, 
every minute, 
every second --- 
is the fire of love: 
It's never lighted, 
but it burns forever; 
it's the fire of cold and pain. 
\emph{W.G.}

There is no love, 
without sorrow; 
and there is no sorrow, 
without pain. 
Love pain, 
to be loved in return! 
It's the only chance you're given. 
\emph{W.G.}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_First_Era.tex"
%%% End:
