Let's give it another try............

I'm happy you're with me --- again. I know that these texts are quite long, but life is developing really fast. 
That's the way it is. 

\textbf{Another question that's yet to be answered:}
\textbf{[u]Ignorant Crowd?[/u]}
Tuesday. 
Nice day. 
Like every day, nothing different --- or so it seemed. 
But before we start to focus on today's happenings, we'll just have a look at the things that had happened yesterday evening --- in his mind. 
And, in reality. 
Which is the same, somehow, more or less. 
He was chatting, doing some nice communication on the internet; and one of P.'s friends --- probably, we'll soon give her some name --- had contacted him. 
It's not that easy to baptise her, as she's multi-coloured in some way; and he doesn't know that much about this girl. 
Not yet. 
The colours she'd chosen for herself were some white-blueish colour, some green and some red --- finally, she'd chosen all colour there are. 
But in fact, there was some combination of blue and white --- and red, and that meant something. 
Intelligence, logic --- and fire. 
Did that fit?
Well, probably, but he wasn't sure. 
He just knew that she needed some bright colour, as that was the part of her aura he'd already noticed. 
Until we've found some name for her --- something, that really fits --- we'll call her P.'s friend and --- sometimes --- multi-coloured. 
But for now, let's stick to the reality. 
That's the only thing that can save us, and the only thing that'll ever lead to our destruction. 
She had contacted him, in a way of friendship, and maybe even more --- nobody had contacted him in such a way for quite a long time, and he'd felt ignored, which made these messages even more important for him, though there were some errors in typing. 
And, she'd done something, that he'd done, too, though it was far from perfect; but she'd tried, at least, and doen some steps in the right direction. 
She seemed to notice what he'd said. 
And she had also greeted him happily when she was back from some excursion. 
For some minutes, he thought if he would be able to transfer the remaining pieces of his love for O. on her; he wasn't sure. 
At least, he'd answered her. 
Without any spelling mistakes, he hoped. 
But he'd also met O. today. 
She was really very ironic that time --- and sometimes, he wasn't even sure if he understood all of it, but nobody would have done. 
Once, when her best friend was separated from her, he just started to talk to that girl, and she seemed quite nice, though she wasn't that ironic. 
Something, that occurred to him quite early, was the fact that the two of them --- and most of the people he knew, in fact --- were really spontaneous. 
He wasn't. 
But he decided to adopt something of that vivid energy that made her character. 
So he did, and his --- up to then --- quite pedantic manner was getting normal. 
Once, when she mocked him because he'd done something wrong and had not been \emph{perfect}, he knew he did it right, and the others were wrong. But he didn't tell her; Being perfect was something nobody should try to be. 
On the other hand, everybody should try it; But nobody should agree with other persons believing that he / she was perfect. 
But the story with O. was not that important to his logical analysis anymore --- feelings would last forever, but he was now just developing some kind of friendship. 
For that reason, he'd even sometimes acted like a girl, without really noticing what he was doing, being alone among all those female fellows. 
But he knew that this was part of the profiling system, that had been burned into his mind since his youth. 
We'll now return to have a look at some further details that had happened yesterday. 
He'd met the girl that had stopped her relationship to her boyfriend that morning. 
she was in the bus he would enter, together with her brother; we already knew he'd waited for 22 minutes in the cold. 
And when the bus arrived, he noticed her; Nevertheless, he decided to enter another door, as the driver would probably wonder why the single person that was waiting at that bus stop would not enter through the front door. 
Thus, he could just have some look into her eyes, and she seemed happy --- no difference to the time before and while the relationship. 
Back to the present...........
When O.'s best friend and he would take seat in some vehicle, which B.-B. was driving, actually, the place would be so limited that their coats would touch; And finally, he would feel the warmth of her body next to his, but he was capable of ignoring that. 
Some other time, O. would sit next to him in a similar position. 
For a short time. 
He wouldn't \emph{feel} her, in now way. 
And he didn't know if he really wanted that. 
This time was gone, and now, there was just some sort of special friendship remaining. 
Probably, there will be some change, even after the week of decision (this week) has ended; stay tuned, to find out about that!
Some feelings will never die completely..........
The next second, he was alone. 
And another girl he knew was passing him by, without any sense to recognize him --- he knew that she was in a hurry, but he stopped her nevertheless to say goodbye to her. 
Only when she told him she had to hurry up, he finally let her go. 
But that girl normally seemed to be one of the persons that try to see everything --- something he tried to achieve, too. 
Today, she didn't. 
However, that didn't seem really important to him; we'll go over to something else now, that happened some minutes after, when he said goodbye to O., as there was something special about it. 
Something the two of them had developed in the bus at happier times, when she was walking around the globe without a boyfriend. 
They way they said goodby to each other. 
He'd thought that she had forgotten, but she seemed to remember it. 
The procedure was the same as every time, but now, her best friend was with her, and the happy laugh he heard when she recognized the way they said goodbye to each other gave him energy to carry on. 
The world was big. 
Really big. 
And time was quite eternal. 
The only limitation there was was his life; and he'd try to keep it. 
Something just jumped into his mind now: He hadn't turned around after he'd said goodbye. 
Turning around was the main sign to signal one's love. 
Was he cured, finally?
Or was that just some trick that fate had played upon him?
He wouldn't know. 
Something he knew for sure was that O. was too tolerant. 
When her boyfriend didn't write any SMS, she explained he was simply having some problems with his thumb, which was hurt when driving with the bicycle --- or something like. 
Well, even if the thumb was hurt --- he still had fingers, didn't he?
And, when he decided to have a girlfriend, he'd also taken some responsibility. 
Our protagonist kept quiet, not saying a thing. 
And O.'s friends did the same. 
Then, there were two other important things: When he'd told her best friend that he'd go somewhere, O. must have asked her where he'd gone. 
At some other occasion, when she bought some food, she didn't care for him. 
But as he didn't want some of this food, he didn't know if he should be happy about that, in fact. 
That was something else that separated the two of them. 
Stay with me if you want to learn more!
I'm waiting for your opinions........
To be continued...
This week, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

Purple rain was falling, 
giving the world some peculiar shade; 
everything was hidden, 
and nothing was unique anymore; 
all individuality was gone, 
and who once had been something special, 
was now as good as anybody else;
as when love had burst out, 
when the purple rain had fallen down, 
the fire was extinguished 
by it's own source. 
But finally, rain will never die; 
and fire will always be there. 
Forever. 
\emph{W.G.}

When he closed his eyes, 
she was back again; 
but now, he just saw her back, 
her hair and her favourite jacket. 
He just heard her voice 
and her call for him. 
Soon, 
that emotion 
would be a memory. 
Kept alive forever; 
Also, if his hope --- 
and when the two humans --- 
had died. 
\emph{W.G.}
