Hello, my fellows!

My life's become a rush, and too many things are happening........
Nevertheless, I'll try to stick to the most important things!
Thus, this one is quite short; Sorry for that!

\textbf{Was this the Day of Decision? Read:}
\textbf{[u]Knockin' on Heaven's Door[/u]}
Wednesday. 
The week of decision; he was now to be half-through. 
But now, he felt as if it was nearly over. 
The decision seemed to be final. 
Just before we have a look at today's events, we'll talk about thr most interesting thing that had happened yesterday......
It was evening, and quite late. 
The phone rang. 
He was pretty sure that it would be the boy who G. appreciated, the one he and O. happened to dislike quite strongly. 
But he wasn't. 
To his further astonishment, he heard P.'s voice crackling over the line. 
She had a problem that he could solve, and after assuring her to do so, they talked for several minutes, contemplating about their not having seen each other for days. 
Finally, both of them were happy and when the two of them hung up nearly simultaneously, both were happy. 
He solved her problem, of course. 
Nevertheless, he was astonished by the fact that he was happy; But he was sure that this was something different than love, that this was real friendship. 
And he was one of the single friends she had at that university. 
Wednesday --- let's get back to the present. 
Today, he would knock on her door, so to speak. 
And her boyfriend would open it. 
But as our protagonist and O. had to do something for university, that was to be explained easily. 
Later, he was alone with her. Finally, there would be some song on the radio she liked; and he liked that one, too. 
But he didn't know anybody else who did. 
Nevertheless, he didn't tell her. 
By the way: He had noticed that the fingers of her boyfriend didn't seem to be injured. And he'd seen them kissing, just for a short moment of time. 
And --- she'd told him that some other friend of her was phoning her more often than her boyfriend did. 
But that was something he learned this morning; more interesting were the details that were yet to come. 
When they were alone. 
And, finally, when they weren't. 
This was the day when he'd find out that she really regarded him as some friend; Maybe some special friend, but a friend. 
A real friend. 
He'd given her reason to do so, but she had advanced for the first time, we already know that. 
But you'll now wonder: What had happened today?
Several things; we'll try to have a look at the most important. 
The memory that had been most important to him --- the time when her fingers had touched his lips --- was destroyed today, as the beginning of the scene would repeat; But this time, she would do all that herself, and he wasn't needed anymore. 
That was some kind of sign, probably. 
However, she also talked to him more than ever, since the time she had a boyfriend. 
Probably, she was accepting him as a normal friend. 
Or, something like a special friend, as she told him things about her friends --- and her best friend --- that were just meant for him to hear. 
But, remember that: She'd also told him such things about her boyfriend. 
Her character was something different, something special, and he didn't know if he could really appreciate it \emph{(with the logical part of his thinking, that is)}. 
Normally, she would have finished her studies in something about one year, to go somewhere else; and he'd planned the same, as his studies would be finished, then, too. 
But he was always sure about the place where he'd go to. 
She wasn't, it seemed. 
Up to today, she was sure that she would join her granny and work there; now, she was really planning that she could probably go to the same place he'd go to. 
But that was not really fixed, it was just some idea of her. 
We'll have to add something that had happened yesterday: She seemed a bit sorry when he'd said goodbye. 
Just for a quarter of a second, but it was enough for him to notice. 
Maybe, there would be some chance for him; but it would not be now. 
And he shouldn't hope to gain more time than that year. 
Finally, he shouldn't even hope for that. 
He should just hope for nothing, and turn his head to look the other way. 
He tried, but when he closed his eyes, her face was becoming more and more apparent again. His method had not been perfect. 
Probably, he'd repeat it after that week had passed. 
Perhaps, he'd start with that just now, or tomorrow. 
But he's not at all sure about that. 
Finally, to prove him right, she'd used the special way of saying goodbye; But not with him, but with one of her \emph{(female)} friends. This girl hadn't responded the way he did, and though O. had finally done him a great favour, she didn't use that way to say goodbye with him that day. 
Yes, he was just a friend; Now. 
Maybe, he'd be one forever, maybe, he wouldn't. 
Probably, they would part forever, and on the other hand, they could still unite. 
Time is eternal; quite eternal, at least. 
And though we aren't, our souls are. 
His' was decided to find her's, even if that would be at some distant place and time, and in another life. 
Or, in another form of existence. 
But that's written in the stars, or in something different that's going to last even longer: In the particles of consciousness that make our minds. 
We all have to endure and persist; Hope is pointless and absurd, and most facts are just illusions. 
Our stories are the most valuable things we can pass on, and everybody should do so. 
It helps to cope with all the things you need to endure, and gives you energy, helping you through the day. 
Find that energy; read and write to learn about your innermost feelings, and your real character.......
Please stay tuned, more is yet to come!
For now, I'm completely tired...........
I'm waiting for your opinions........
To be continued...
This week, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

He looked into the sky; 
then, he closed his eyes, 
and saw her face. 
When he opened them again, 
the sun had found her way 
through the clouds. 
And the vault of heaven 
had all burst open; 
and his heart received 
the heavenly power 
that would give him energy; 
Energy, that would finally 
destroy himself. 
\emph{W.G.}

Why do we love our enemies more than our friends? 
Why do we love the emotions though they're driving us crazy? 
And why do we hate the time when all our wishes are fulfilled? 
Are we all masochists?
Maybe. 
But probably, we're all searching for balance, 
'cause we can only achieve an aim
if we don't want to. 
\emph{W.G.}
