Hello, I'm happy to be back again!

That was a harsh day, and I feel flat...

\textbf{Thus, the title is:}
\textbf{[u]Smashed to the Ground --- In Front of Heaven's Door[/u]}
Thursday. 
Now, he had a headache. 
Normally, he never had such a thing as a headache. 
At least, not for such a long time; But this day was the most exhausting ever. 
This was the second, and most probably the last day he'd knocked on her door. 
And, before he did so, the slippery ice in front of it joined his hips with the ground. 
He stood up as fast as he could, and the small children that stood nearby were mocking him; They didn't know who he was, and he didn't know them, either; For that reason, he didn't take away their fun. 
But he was quite sure he wasn't capable of doing so, either. 
Her boyfriend opened the door again, and he wondered if he'd now spend every night at this place. 
Well, a normal greeting and he was in. 
Working for university again , finally alone with her as her boyfriend would have to get to work. 
But not for long, as other friends were to arrive. And he didn't remember a thing he wanted to tell her, his brain was completely empty. 
When the other friends arrived, the smalltalk had ended and she was telling him something of importance; Not only because he was interested in that, but also because she \emph{remembered} that he was. 
She told him, that the chance that she would join him later when they would go to work, to do so at the same place, was --- suddenly --- not that high anymore. 
But she wasn't responsible for that; There's no need to go into detail now. 
Had his hope been too strong?
Maybe. 
Then, he was to be pleaded guilty by himself. 
All of us are. 
And that method which told him, that the things he didn't hope for came true, finally, was some kind of divination. 
Now, he understood \emph{why} one might not wish to know about his future. 
And it occurred to him, that he had found some sulution for a problem nobody at university had been able to solve, including the professor. 
The protagonist in the book \emph{"His Dark Materials"} had access to a method to find out about her future; However, she didn't use it most of the time. 
And, this ability was based on something she'd received by fate. Later, it would be taken away and she would have to learn all of it on her own. 
Now, he understood: Nobody should try to gain access to the future; Not only that it takes away the thrill of not knowing something, but in addition to that it takes away the chance to act differently --- and the feeling to be responsible for one's actions. 
Knowledge can destroy one's life. 
This were the most important things which he'd learned about O. today; but this day wasn't over, not yet. 
He nearly had an accident with the car he was driving that afternoon; and finally, when he arrived home much later, the headache began --- slowly. 
Up to then, it was normal: It would go away when he found time to relax, time to write this text. 
More things were yet to come. 
A professor had phoned him. 
He was offered something. 
He'd neglected it, but he would still be given the possibility to accept it until tomorrow. 
But he was pretty sure he wouldn't do so. 
Before he could phone that professor, he had to search fo the right number, as his granny had noted something wrong. 
His tension was steadily rising; He didn't know what that professor would want to tell him. 
Well, now he knew he was offered a long excursion to learn many interesting things. 
But that was long.......
And he wanted to stay where he was. 
For some time. 
Some years. 
He didn't want to go to some strange place far away, completely on his own. 
That would also mean he'd lose more time to stay with O., though he probably wouldn't even see her at that time. 
But his decision was final. 
It was not to be changed, and even fate didn't have a say in that. 
'Cause some things are sure, and only the things we can't decide can be changed. 
Most times, that is. 
After he'd phoned that professor, his headache had reached climax, and he knew he should take all the inspiration there was to put it in these words you're now reading. 
And while he was writing, the pain was leaving, losing it's tight grip. 
The point where fate had smashed him to the ground still hurt, but he'd learned to endure. 
And then O. explained something about some friend of her's, the one who'd phoned her so often and was now getting on her nerves. 
She would meet him some afternoon, as he'd invited her; But she wished her best friend to be with her, and of course she would be there. 
To show you the ironic way that happened to be part of her character, we'll now try to remember some of the words she'd used, or at least, explain you in other words what she'd said. 
After telling her best friend about that meeting and her taking part in it, that best friend mentioned something like: 
\emph{"Oh, yes, so I can do something if he starts touching your knee..."}
\emph{"Yes, leave us alone then..."}
\emph{"Well, I thought of something like hitting him..."}
Of course, everybody knew that she \emph{didn't} want that guy to do somthing like that. 
But she liked being ironic. 
And it was fun for all the listeners who knew about that, too. 
Finally, he'd also realized that she was doing some kind of profiling, too. 
For when one of her friends exited the room --- one to who she'd talked quite nicely before --- she started explaining her real attitude towards her. 
And he was among the people she seemed to trust; He could never imagine her doing something like that when he went away. 
And trust is the basis of every relationship, of any kind. 
It would stay a friendship; for now, and probably, forever. 
But we don't want to see the future. 
He'd also met P. today --- She was quite nice to him, too. 
And she'd told him that she was finally starting to read something, which was exactly what he'd always told her to do to improve her expression in the language she was learning. 
And then, she'd told him something that matched his story quite perfectly. 
\emph{Too} perfectly?
Another sign?
But read for yourself:
One of her friends seemed to be interested in her, but she didn't want him to be with her. 
He'd decided to leave his former girlfriend because she betrayed him, something he'd done just before. 
And finally, these two persons fitted perfectly together. 
That's what P. told him, and when he was sure that she wouldn't ever do something important \emph{(from his perspective, that is)} he'd asked her to do, she seemed a bit hurt and not so sure about it, though he could tell she wouldn't do it. 
He was pretty sure about that. 
But probably, she wished for more than a friendship........
He doubted it, but he'd be on a lookout to notice it. 
Nevertheless, he wanted their relationship to stay a friendship. 
Crazy. 
Somehow, everything was linked; In some way, all the things that happened were the same. 
Just with other persons, at other places and in other times. 
But always, things were the same. 
Change was everywhere, and that was something that wouldn't ever change, too. 
Life was always interesting, and it would always be. 
His headache was still there; Somehow, he felt physically ill, though this was probably caused by his psychic instability at that moment. 
But he knew how to hide that. 
And there were more surprising signs he'd seen: Two, in fact. 
Well, just one thing was really important, probably. 
But we'll start with the less important to lead over to the other. 
There was some comic, and the two protagonists were called quite similar; The female one was called the same name that was O.'s nickname. 
And he'd just happened to read another piece of that comic series today, as he received a new one just a few minutes ago. 
But the probably more interesting thing is another figure he'd found in some famous comic he was always reading. 
That figure's name was nearly matching P.'s other name. 
What's her other name? There's no need for you to know about that now. 
But the figure was quite similar to her other character, which included some features of her normal personality. 
And he'd just happened to read that comic yesterday. 
The story with that figure was the last one in the book. 
And finally, that figure disappeared, when everything had sorted out, without realizing what was really happening. 
What the heck was the meaning of this?
He wouldn't know, but he feared the intention gripping hold of his spirit, and he tried not to think about all that; In fact, he tried not to think about anything. 
Of course, he would fail, but as he knew that, everything went quite well. 
He doesn't know what's going to happen tomorrow, and he doesn't want to find out right now; if you want to, you'll have to wait until --- well, tomorrow. 
I'm feeling ill now...........
And I'm still waiting for your opinions!
To be continued...
This week, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

O stars,
isn't it from you that the lover's desire for the face of his beloved arises? Doesn't 
his secret insight into her pure features come from the pure constellations?
\emph{from "The Third Elegy" by Rainer Maria Rilke (probably, you'll need the German version to grab the real atmosphere --- this translation seems to simple, and normally, Rainer Maria Rilke is more --- well, simply better!)}

*thud*
He looked around. 
*thud*
He didn't see a thing. 
*thud*
What was that for a cruel sound?
*thud*
And where was it coming from?
*thud*
He covered his ears. 
*thud*
It was still there. 
*thud*
It was coming from inside. 
*thud*
His logic was hitting his emotions in a giant 
*thud*..........
\emph{W.G.}
