It's me; the same person, but another time!

And another situation, though there had not been a lot of things happening today. It was just some kind of summary, but I'll present these events to you nevertheless. 

\textbf{He was waiting, thinking;}
\textbf{[u]Pondering his Voyage[/u]}
Friday; the day he would have some time to write some longer text. 
That's what he thought in the morning, but in fact, his time would be really limited to a couple of minutes, probably just an hour or so. But he was intending to go on, eagerly awaiting the development of his own life.......
This morning began in the bus, as every morning when he'd have to attend university would. That day, there had just been the TV announcement \emph{"not to touch dead birds"} (well, who'd ever done?), as the bird flu was beginning to spread throughout Europe. 
And he was sitting in the bus, reserving a seat for Y., though he was pretty sure she wouldn't come. She'd take another bus, as this one was too late --- and as a matter of fact, fate had ironically gave this bus he was sitting in a horrible speed in the beginning of the week. At the same time, the bus began his voyage so late that Y. would think that this one was late. And in the end, he could make out her face through two windows, when they overtook the bus she was sitting in. 
But none of this happened today. 
This Friday, the bus he was in seemed really empty, and Y. didn't come, of course. O.'s car was standing somewhere he'd never seen in before, just at the other side of the street, in the middle of nowhere. But that was not important, not now......
Y.'s seat was finally presented to one of her friends; she didn't really say more than ten words to him \emph{(well, probably something around 100, but in fact, it was nothing)}. When the bus arrived, Y. was just one hundred metres ahead, or even less, and he'd catch up with her when they reached university, just exchanging some words without sense. That was something all of us did, all the time. 
Later, he was back to the library again, together with P. and her friend who'd embraced him the day before. The internet was accessible again, and thus, they all were struggling in front of one computer, enjoying themselves. When P.'s friend was in her next lecture, he had been left alone with P., who was working at something, but sitting next to him. And another friend of hers was there, too. While he was fighting with the computer, he once said that he'd kill everybody around here if the thing he was doing wouldn't work; as he'd said that once before, when P. was near, she knew he didn't mean it, and one could also see that when having a look into his eyes. 
She laughed, and her reaction was that she told him --- \emph{again} --- that he wouldn't kill her. However, she told him that there was some other reason to it; for a second he assumed she was hinting at some kind of relationship he hadn't happened to notice yet, but then, when the silence was unbearable, she said that she would hinder him from killing her, the same thing she'd said the last time. And something about a minute later, P. asked him whether he'd kill her friend, too; the very same that seemed to be so important to him. Of course, he answered that he wouldn't, as she was not responsible for anything like that happening. 
While he typed these words, he realized that a lecture had been between these two events; thus, P.'s friend was indeed \emph{there}, just at the very moment, seated some metres apart. He was trying to help her installing something on the computer, but she was encountering the same problems; this afternoon, he'd worked out the solution, and that's one of the reasons for his lack of time. But at that time, he'd helped her with something temporary, but on Monday, he'd install the new thing. 
Still, this was not the most important thing that happened today. Even the fact that he was to take an exam he didn't know about, and thus wasn't prepared for, was not as important as the fact that P.'s friend had dropped her head on his shoulder in a state of tiredness. 
And in addition to that, just for some seconds or even less, which meant she must've felt that he was something different than a friend to her --- probably. However, he was still wondering whether there was really some kind of relationship under construction, remembering the second when Y. had dropped her head on his shoulder. 
Y..........
When the last lecture had been finished, Y., her friend, our protagonist and some other friends went to the bus stop together. He assumed that Y. would fetch another bus with the other girls, but he didn't know for sure, which turned this assumption into reality. However, he tried to talk them into staying with him, as 'his' bus would just arrive a minute later. Y. seemed to be changing her opinion, looking at the others, saying something, thinking, looking puzzled; and then going, telling him goodbye, giving him her \emph{'it'll-not-be-as-bad-as-you-think-it-would-be'} smile. 
He entered his bus \emph{(which was late, indeed)} alone; He knew some of the other students, but he'd never had any contact to them. 
And he chose a seat for himself which was located near the middle of the bus, probably a bit closer to the back; Sitting down, he was happy to be alone, finally. But he wasn't feeling that now, and that rescued him of something that could have come. 
Looking out of the window and not seeing something at all, he was thinking, contemplating about everything that had happened, was happening and was yet to happen. He remembered the other scene that took place in the library, when L.-B. walked up to him once again and was getting on his nerves --- once again. P. was sitting next to him, and he was pleading her to help him when he saw L.-B. turning round the corner; In the beginning, P. asked him where L.-B. was, indeed, as she hadn't noticed her, and then, she took the initiative to ask him about something she knew perfectly. Something about the last lecture. But it didn't help at all, as L.-B. was a person without conscience, egocentric in some ways. She wanted to ask him something she \emph{should} have known, but seemed not to know; And he was pretty sure she wasn't just pretending, as the piece of work she showed him was wrong. 
Completely wrong, as she was just learning methods without really understanding what she was doing --- He knew that, and when she asked him something, his profiling system would translate the easy sense of something in the complex method she would learn. 
P. was really doing her best, telling L.-B. that she was asking him something and waiting for some explanation, but L.-B. told her she should hurry up in a really offending manner. Now, when he was contemplating about it, he'd have liked to tell L.-B. that she shouldn't treat P. this way; but he could never have done such a thing, as his profiling system didn't allow him to do so. 
He'd have to regain the memory of the past, and he was in need of going through all of it again; this was the only way to break the chain. But time was running short...........
Still sitting in the bus, an alert from some part of his brain woke him from this state of concentration; the rapid line of thoughts was slowing down, as he recognized the small boy who'd asked the question which lead to the 'First Denial'. Of course, he'd take seat next to him, and his time would be lost once more; but he hoped the child would take his seat together with another friend of his he'd noticed in the fore part of the bus. But as this one had seen him, and as the other friend of the small boy had entered the bus, too, heading towards him, though he wasn't sure he had been noticed, hope left his soul which was soon becoming more heavy, as a loss of a good feeling is always a gain of bad feelings; and these are much heavier that the others. To his astonishment, all those children took seat where he'd hoped them to go to before that hope had been extinguished; Thus, he was rescued. 
The following kilometres, he was getting tired, as his brain was working in an abnormal way; He finally found himself sleeping. Once and then, he'd wake up, having a look around, but accepting the power of sleep to cure his mind; and when he passed next to O.'s house, he woke up too late to see her car or the entrance, though --- or because --- he'd hoped for it. At this moment, the typing protagonist realized the other meaning the idea of 'Heaven's Door' introduced: If you're in heaven, you're not only happy, but your life on earth is finished, as you're dead. 
And he didn't want it to be finished; remembering himself laughing about the persons standing in church before a marriage, suddenly getting afraid because they feared to be bound to one place, to one \emph{person} forever, and finally even running away, fleeing their future --- a future full of hopes........
Though he knew that such a future was probably one of the worst things one could wish for, he dreamed of it. 
And he couldn't help but realize that there was some hope for such a happy ending in all of us. 
Where would his further footsteps lead him, and how is his life going to continue?
Do you still wish to find out?
Have you already left me alone?
Please show me you're still alive..........
To be continued...
This week, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

A head on a shoulder 
is a sign; 
a fist hitting you 
on the tip of your nose 
is a sign, too. 
And both can be signs 
of love, friendship, 
hate and deceit. 
\emph{W.G.}

The water was flowing again, 
carrying his thoughts, his sorrows 
and his hopes far away. 
The fire was burning again, 
doing the same. 
But where did the two antagonists head to? 
Was there such a thing as an aim? 
A target? 
Could --- would --- they return? 
He hoped to know, and he wished never to find out about it. 
\emph{W.G.}
