Hi, nice to see you again!

A lot of things have happened, but my work for university is limiting my time, though there should be enough to write more texts; However, the more time there is, the less you can reserve to do something important. This time, we'll have a look at something pretty interesting. 

\textbf{Stuck between}
\textbf{[u]Proof and Confusion[/u]}
Tuesday and Friday had passed, several things explaining themselves, and several becoming even more complex. In fact, everything became more complicated, in the same way the increasing entropy of the universe would endanger every kind of order, leaving no stability anywhere, just the reality of change itself. 
Tuesday was the day of the carnival, when there would be the party at university. It took place in the morning, and all the people he knew would be there; even some other person from the past, his former best friend, from whom fate had separated him........
But there was something eerie about that; we'll have a look at this later. It all began that morning in the bus, when some girl from the city he was living in tried to disguise him even more, though he didn't want to be. The colour she'd use was the same colour she'd applied to her lips; and in fact, he was pretty sure that she'd use it even \emph{after} having painted him. Holding his face with her left hand, she wished to begin, but he told her not to do so, and it took about half a minute to convince her. However, it showed that she was interested in some way: Nothing seemed to stop her from touching his cheek, and she kept smiling --- and laughing. After he'd sent her away, she was as calm as ever, as if all this had just been an outburst of some profiling system; in a way, everybody used something like. He'd see her again some hours later, on his way home; we'll have a more detailed look at her then. 
Next thing was, that he was --- again --- reserving a seat for one of his friends, as there were Y., or one of the others, though he just guessed that the girl which had opened the doors for him the last time would take her seat there. 
She didn't. 
This time, Y. wasn't there, and the other girl was missing, too. The bus was late, though he'd see her again when arriving at university, as the party took place quite close to the building he had had to enter so many days. Only a year or so was to pass until he'd be finished --- probably. Only a year close to all those friends, and then.......... Emptiness. 
When he arrived, P.'s friend was waiting for P. and the others, and he joined her for some minutes before looking if the party was about to begin, searching for some other friends of his. Talking to her was something he enjoyed, he'd realized. Soon, he'd have a close look at some stories she'd written; this would give him some further insight into her real character, the thing below the surface. 
For now, he entered the room where the party was about to take place, seeing some friends of his. Soon, he was talking to them, then, they were exiting the hall again to search for P. and their friends, who were suddenly not to be found anymore. Going back, he stumpled into P. and the others. The group entered the hall again, talking, taking photos and fooling around. 
All of them where there; not just P., her friends and the boys he knew, but also G., B., O., L.-B., B.-B. and some more. 
G. and O. kept their distance, though G. was smiling at him from far away; at least, when he was in some higher position, having the possibility to see everybody. When going there, he met another girl he'd learned about some year ago; she greeted him as a friend, though she'd often passed him by without a word escaping her lips. Some moments, he thought that she was waiting for him to do something; but he wouldn't know what she was expecting him to do. He was pretty sure that O. had seen him, but she was evading his staring eyes, who were soon jumping through the hall, seeing the irritated P. searching for somebody. For a moment, he thought she was searching for him, but when she'd found one of her friends, he realized she wasn't. On the other hand, she hadn't said goodbye before she was going home, which induced the idea that she had not seen him anymore, while he could see her. 
On the other hand, there was his former best friend, whom he could also watch; However, he didn't realize that this really \emph{was} that person; instead, he thought that it was O.'s boyfriend, just having a look at his hair. There were two persons who resembled her friend, but he thought that this one was the person in question. When the party had been finished, he'd also done something to catch O.'s attention, but she didn't react in any way; not even her eyes seemed to be looking at him. A moment later, somebody was talking to her about that, and he couldn't get the sense of it, as they were too far away; but it seemed that O. was ignoring whatever the other person said, just slowing down a bit and going on. 
That told him that she was ignoring him on purpose, though she hadn't showed him any of this on Monday, when she had been sitting next to him; and he was pretty sure that this was some kind of system to forget about something. 
But then, if she was really trying to forget about him for the sake of her boyfriend, why had she greeted him so happily about six months ago, when these two had been a couple for something about three or four months? Nothing had shown him any of it then........
The new couple seemed to be quite interesting, however; it had just developed some days ago, but the two persons seemed not to be on fire, but in a balanced relationship, having the best foundation for it to last. 
And he had been sure it wouldn't, this probably being one reason for its stability. 
When the party was finished, and O. hadn't reacted in any way, he was waiting for the bus; there, at the bus stop, that boy, his former best friend, was standing with some new friends of his. One of them --- several of them --- were drunk, though he himself seemed to be completely sober. However, one friend of him was making such a noise next to his ear he felt as if he was going to be deaf. His former best friend tried to stop him, and finally, he recognized the voice, and the other guy was gone. The two of them talked about their situation, studying, learning some job, and their outlook on their own future. 
Both seemed to be happy. 
When some bus arrived, his friend had gone with the others, though he could also use the same bus he'd use; both knew that, but he said, without our protagonist asking him something about it, that it seemed that the others took that one, and he entered it, too, saying goodbye once more. 
The old friendship; it seemed to be broken, and the two of them seemed to be strangers to each others. It had once been so strong; but time was the strongest power out there, and only time itself could change that. But as time probably only existed in this universe, this was not really probable; at some other place, time wouldn't exist, whatever this place would look like; \emph{if} it looked like something, that is. 
But that's not the kind of problems we should have a look at right now. When he'd entered the bus, there was another small boy there, who had asked him if he'd like to join him in the car of his parents / his friends to go home. He had denied that proposal, and his friends had told him he should have accepted it, as he'd now have to wait for the bus for quite an hour; and then, they'd stayed with him for more than half of the time. 
And now, that boy was standing at the bus stop, still waiting and then entering the same bus he'd take to go home. The bus driver was quite young, and another one, the same he'd talked to the day before, was standing next to him, giving him advice, and finally taking over when he'd chosen the wrong route and was unable to go back. That girl which had wished to paint him in the morning was there, again, but the seat he had reserved in the beginning had now been given to somebody else. In the morning, another guy had simply sat down after asking, though he'd promised the seat to somebody else if Y. wasn't to come. He'd told that boy about it, and he'd simply said that he hated people who reserved seats for somebody. Well, he was in no mood to start fighting; he rarely was. 
He'd been about once a year in that traumatic time in the past.......
It was gone. He felt dizzy, having drunken too much coffee and some beer; however, he could still go on typing his feelings. And he did so, fast, as it was close to 10 pm. 
Thursday was gone, now; Friday would be the day he'd explore more things about his computer, and finally, it would be gone in no time. However, he'd promised himself to have a look at the texts of P.'s friends that evening, even if that meant he'd read them in bed; everything was prepared to do so. 
And on Saturday, it would be pretty probable that he'd meet her on the internet; then, he'd tell her what he thought about those texts. 
Hopefully, he'd have finished reading them by then. 
This post is finished now, and hopefully, more is to come soon; However, he'd now having some days off, and there will be less new experiences. On the other hand, this will probably be the time to catch up with the past, or to have a look at what is yet to come. 
I'm looking forward to that, and I hope you'll be with me, again..........
Please look forward to the next one......
And what about your opinion?
To be continued...
This week, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

Thoughts rushing, 
through his body, 
through his veins, 
without control; 
feelings unleashed, 
and soul withdrawn. 
What is to come? 
Why is the past unreachable? 
He was going to enter this vicious circle 
of memories 
to find out, 
hoping to find out not only about himself, 
but about past, present --- 
and future. 
\emph{W.G.}

Fear was spreading all around --- 
pulsating feelings, 
terrible memories, 
chasing the crowd. 
Horrible news, 
sensational stories, 
making them tough --- 
and leaving them as blocks of ice, 
incapable to feel or understand, 
as those horrors were normal. 
And their own sensations 
seemed more important than those 
of others; 
Mice, spiders and bad education, 
rumours and financial problems 
rendering them helpless. 
But the most shocking sensations 
of themselves 
were not to be noticed 
consciously; 
their souls were killing themselves, 
and their getting tougher 
was the last sign 
of their death. 
These were the signs of change, 
and it was not to be changed, 
not even by change itself. 
\emph{W.G.}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_First_Era.tex"
%%% End:
