Still there!

Though there's a lot of time, there's a lot of work, too, and no need to start killing time with stupid actions. My To-Do-List simply is too long...

\textbf{Time for}
\textbf{[u]Preparations & Old Sensations[/u]}
This Sunday has been so long and full of work, that it's hard to realize it's only been one day, in the end. In fact, it seems as if the parade had been long ago, and finally, it had just been yesterday. It occured to him that time seemed to be longer than it was; some thoughts were stealing it from ourselves. 
This day, he'd been showing some pictures to his family, and he'd looked at some old --- and recent --- photographs himself. And, in addition to that, he couldn't help but find the now rather old notes he'd once taken on G. --- and O. Some were encrypted, and so as not to lose all the remmebrance there was, he'd passed on signs --- and parts of those messages --- to his friends. They were publicly available, but nobody would ever find out......
Even his own mind couldn't decrypt all the old messages; at least, there was one which was just some months old, and he couldn't make a sense of it. However, he felt that this one was not that important, though it was the last message he'd recorded; all the old ones would be easily understood by himself, while it would be hard for anybody else to find out about the details. 
He remembered the way he'd tried to keep O. in focus this Thursday; finally, when he'd looked away, he'd noticed that she could have looked in his direction, but this was a matter of interpretation. In fact, nobody could be sure about that. Then, he'd taken a look to her right: Another boy was just going next to her, the very same person which had astonished him with the sentence that life was finally just a wave. He'd underestimated him; Some weeks ago, when he'd presented her something though he'd probably never presented anything to his own girlfriend, she'd been happy, but not shown any sign of further emotion. on the other hand, this boy had also been a good friend of another girl he knew --- finally, he'd been interested in all of them. And now, he just stood next to O........
Well, not now, but that Thursday; and finally, O. looked at him once and then, but in the end, she'd rather look somewhere else. 
And then, he noticed G., standing just in an opposed position to O. She looked more beautiful than her at that time, but the outer appearance was not that important, the more if it was only temporary. 
Everything was temporary.......
One wouldn't mind. At least, not him, and not consciously. 
He took another look at those notes he'd taken long ago, some older than a year, which was in fact a long time for somebody who was still trying to find himself. For him, this process was to take a bit longer, but it would be the most important thing for one to do, and not a question of time. 
'Feelish'; he didn't know the exact reason why he had been so crazy to generate that word with just one event connected to O. and G. in mind. In fact, it was not really linked with them, not so closely. And the way which led to that word was so complicated, as it was just a stream of consciousness, and we can't predict that. 
But that was not everything there was to it; things were more complicated, they always were. Now, he was thinking that this word should rather have been 'foolish', as that's what he was. He was wondering what he'd really done, when he had a look at those complicated calculations, and was astonished when he found some unencrypted words in the same way he'd been shocked when seeing calculalation with a matrix. Checksums, complicated encrypted coordinates and other things were to be found, and he could help but smile: Everything he did had to be perfect, and he couldn't change that. 
All those tiny details he'd snatched; just today, he'd seen the end of a film, a fairytale. The king said, that the moral of the story was, that love is the most important (or was it the most wonderful?) thing there is. Some seconds after that, when the credits were to be seen, a name caught his attention; the first name of somebody who'd taken part in he production of that film was O.'s nickname, though this was a czechoslovakian film. 
Well, he smiled, and that was it, as he felt that such signs had betrayed him, though it was of significance that he'd misunderstood or ignored them most of the time. 
Or, he'd just got their meaning too late.........
Yesterday, P.'s friend had reminded him of something he'd promised her to do; it was already on his to-do-list, but he hadn't had the time to take a look at it. Well, today, he'd done, and it was finished, so he could present her the results. 
He'd do this evening, and he'd probably be able to receive her reaction on it the next day. 
He wasn't sure if she was just friendly to him, or.....
Let's wait and see. Everything he did was full of love, and finally, it had to be returned somehow --- by somebody, as he felt it wasn't lost at all. 
'What you give is what you gain'; a sentence repeated in many songs, in the bible, and all through the world. A sentence to sum up the foundation of belief.........
As long as he was well-liked, he should try to keep that status; and, furthermore, to be well-liked by himself, as then, one has reached stability. 
He'd just read an article: 'Virtual Machines for Testing'; the number of the page it was to be found on in that magazine was strongly connected with G. and O. Did that mean that his emotions were just part of a process of development? He knew that nothing was in vain, but he felt that he felt abused, nevertheless. 
Drinking some beer, of course only a bottle or two a day, was his controlled way of living; nearly everything could be healthy, if the dose happened to be right. Even emotions; but he felt he wouldn't like to restict them, though he had done, most of the time. 
He was getting nervous: None of the contacting attempts had been answered, even not the short text he'd written to P.; but that was something different, it was just two days ago that he'd sent it, while O. and her best friend kept quiet, silenced by their happiness which would sometimes keep them from serious thinking. He'd realized that everybody was childish, in some way; However, he felt he was more serious than the others, while he pretended not to be, not knowing whether this was beneficial --- or not. 
In fact, he realized that nothing had happened, and the first day which would bring recent news would be Wednesday --- but then, his time for writing would be limited. Probably, you'll have to wait some days for more news..........
If you're still with me, that is!
Please be patient!
Please tell me what you think, while I'm giving you a break........
To be continued...
This week, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

Realizing, 
can be disgusting. 
Realizing, 
can be killing. 
Realizing, 
can be the future, 
or the end 
of time. 
\emph{W.G.}

Signatures 
are symbols of ourselves. 
He'd copied some lines 
of his, 
from one of O.'s favourite books; 
and he felt, 
that she'd always be a part 
of his soul; 
when she died, 
some part of him 
would break apart 
in quite the same way; 
he wondered what would happen to her 
when he would die. 
\emph{W.G.}
