A new text, and the only thing that hasn't changed is the lack of time. 

This day had been quite interesting, like the start of the week had been, too. He wondered whether some change was lying ahead, and what would happen. However, he felt that a radical change was not to be foreshadowed, at least, not often. 

\textbf{He felt that}
\textbf{[u]Trust is Embarrassing[/u]}
Tuesday had just gone. Familiar faces had told him things and acted in ways he could not have foreseen, and that was --- once again --- a basic law. But before we'll have a look at the recent events, we shall add some tiny details we've forgotten to have a look at yesterday. I'm not sure whether they are of importance, but how can human beings feel so powerful as to be able to decide whether something is important --- or not?
He'd took some notes yesterday evening, when those things came back to his mind. Now, he felt he knew why he hadn't slept that well Sunday night; he'd always had problems to fall asleep, if there were many things he had to deal with; and such moments would accumulate when there was something special about to happen. And that Monday had been special, indeed: He'd talked to O. more than in the weeks before, and he'd been together with so many people........
O. had once more explained her best friend how stupid her boyfriend was, having promised her to do something and now just telling her he'll do that later, though she'd need it pretty soon. And in the evening, when he was at home, he'd noticed that O. would be taking an exam the next day; of course, he could have helped her easily, if she had asked him. Other people did, and those were --- most times --- the persons he didn't like as much as those who didn't. He'd rarely asked people for help himself, and we always like our own features, at least those which are not presented publicly. 
He recalled the peculiar thing that had happened yesterday morning: You may remember that one of the singular things he'd decided to keep was the fact that he always borrowed O. his ruler when she'd need it. He'd laid it next to her that morning, too. In the beginning, she'd used it, and he could see the pinkish colour of one of her favourite pens on it. Then, when other headings waited to be underlined, he wondered why she wasn't taking his ruler anymore, as he'd managed not to look into her direction at all for several minutes. 
Well, and then, he found her using the ruler of her best friend, and it was placed in an equal way next to her. 
He felt dumped, just a bit; and he'd lost one of the last things he had remembered about the once-so-important feelings. 
That had took place just some hours before P.'s friend had said that he was too old for them to be a couple. Yes, that day was giving him a hard time. 
This evening, today, he'd seen an old woman flirting with an old man in a fictional story, which also dealt with the growing fear that bird flu was spreading. He could remember the time, when that two words were just rushing below some pictures on CNN.......
It seemed so far away, without any importance then. Now, there was fear all around. 
But we want to continue with the effect that story of the two old people was having on our protagonist. The woman began flirting with the man, and he accused her of doing so, which she turn answered by denying that in a way one could probably make out by watching and listening closely. 
He hadn't made out something like that with P. or her friend. However, P.'s friend seemed to be \emph{too} friendly --- sometimes. But before we start talking about today, there's still one thing missing about yesterday......
We've already learned about him talking with B. However, we've missed one special moment, when she was unpacking a sweet. A short sideways flick of his eyes which would probably not have been noticed by anybody led to a reaction of her's, and to the feeling that she was indeed someone special, as she told him she just had one of these sweets, but could offer him something else. He denied that politely. 
Girls which offered sweets always reminded him of that story with O. --- it was gone. 
She was gone. 
We should switch over to today. 
The most interesting things took place among P., her friend and him. P. told him something pretty interesting today, leading a 'discussion' again --- the sort of discussion that was in fact just a social game to transfer information, at least for him, as he wouldn't be capable of making up his mind about something that fast. On the other hand, his decisions were pretty stable, and sometimes, even \emph{too} stable, when we remember the stability of his false feelings for G. 
P. told him, that a fixed relationship was always problematic, and in fact, \emph{nothing but problems}. He felt, that the theory he had promoted in the last texts, but not accepted for the sake of his own hope, was accepted by her. The girl that always seemed so happy had learned something fundamental about the world, and this always brings along some character traits: Being thoughtful, serious --- and sad. He'd now learned that she could also act in front of people: She'd even done so in front of hundreds of thousands of people, and this was pretty equal to his profiling system. Everybody did so, but only few would notice what they were really doing --- such a system made things more simple, sometimes. But it could also take away many interesting experiences. 
He was the friend of everybody, everybodies friend --- with the only exception of himself, that is. 
He was captured by his own mind, exploring the fundamental laws and ignoring the easy things which were of equal importance. 
He was thinking all the time, and he couldn't help but go on doing so. 
Interesting things were taking place; tomorrow, he'd be with all those friends for a very long time. However, he'll quite probably be unable to write anything that day. 
But though his time was also limited today, he tried to tell as much as possible without leaving out too much detail --- and without being boring. 
What do you personally think about it? Tell me, please. 
To be continued...
This week, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

Bugs --- 
artificial and vivid --- 
can be signs. 
That day, 
the life of an artificial bug 
had told him 
that P.'s friend 
was more important 
than he'd thought; 
probably. 
It had just been a bug, 
an artificial one; 
but who can decide 
whether a bug's life 
or the life of a man 
is more important? 
Another bug had just forced him to add these lines here: 
He had been reminded of O. by that artificial animal: 
A search without success, 
and a last conclusion of all there was, 
of all there had been, 
in these texts. 
\emph{W.G.}

The rain 
would wash away the pain --- 
and the snow 
would freeze it. 
All the things that came from above 
could only help 
temporarily, 
as feelings 
were never to be destroyed. 
Nothing would ever die. 
Eternal life was all around, 
but we were too ignorant to notice. 
\emph{W.G.}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_First_Era.tex"
%%% End:
