Hi! Nice to see you again!

As you may have noticed, there was quite a long break now; this means that a lot of things have happened, and especially, that I have experienced many developments --- inside myself, and in my environment. You'll find out what I want to tell you if you just go ahead........

\textbf{He was experiencing a}
\textbf{[u]Feeling of Change[/u]}
This week had been hard, and interesting, but this is the same, as good and bad things always go together. This was proved when he'd just written about a quarter of a page, when his editor crashed and the text was lost; he'd have to start over once more. So he did. 
The most shocking event of this week was that thing --- that misunderstanding --- of B., for she'd told him after he'd asked her whether she'd received his explanatory message: "Yes, but I've thought that this discussion was finished, wasn't it?"
Of course, he'd thought that this would mean that her opnion about it was fixed. 
Well, just on Monday evening (or had it been Tuesday?), he'd realized that she was thinking the other way round. 
That thingy wasn't blocked anymore. 
He'd just found out now, and he was \emph{not} eager to tell her the truth about his former thoughts. However, this made him happy once more, as he'd realized that he had \emph{not} estimated her completely wrong. 
On the other hand, this arose some more questions he wouldn't like to answer. 
Today, he had talked to B.'s best friend, realizing that she wasn't feeling pretty well --- as she told him so --- and that she was still as shy as she'd always been. This meant that her intellect, which was indeed something special, would only unfold when in company with B.; however, B. seemed to be a person that liked to be on herself, sometimes, having strong friendships with that girl and especially R. 
People who needed time for themselves --- \emph{eremites} --- would always be interesting for somebody who searched for a complex character. However, he knew he would just watch these interesting beings. 
Then, there was something else he'd forgotten to tell you on Monday: O. had been in need of a piece of paper, and she'd rather turned back to ask her best friend than to ask him. 
Probably, this was just one consequence of the fact that she didn't want to feel as if she exploited him; most people \emph{did} exploit him, and in fact, he wished she did. 
But she didn't, and his mind was left boiling when all those new things closed in and he was lacking time to sleep properly. And then, there were those signs; those things he didn't want to think about. 
Yesterday, it had been the name day of O., in a way, as it was her nickname he found on the piece of paper that was his calendar; he'd never known that there was a day like this. Hadn't he noticed this one the last year? He didn't know, but he remembered the time when he was together with O., just one year ago.......
It was all gone, and it would not return. Then, in a lecture, he'd just opened a book on a page whose number would remind him of O. and G.; he'd think that it would be pretty funny to think that this was in any way connected with O. The contents of the page seemed quite normal, but then.......
The student next to him, who was currently talking to the professor, used a word that would be chosen quite rarely; he'd just heard it about five to ten times \textbf{a year}. Last year --- or the year before, he wasn't so sure about that anymore --- G. had used it to describe him. 
He felt the way she meant it, but when you looked it up in the dictionary, there was a negative association with it. However, he felt that she was thinking the same way he'd always thought about that word: It was something rather positive. And that word had just been used by that student \emph{next} to him, while he'd just looked at \emph{exactly} that page, with \emph{exactly} that thoughts coming to his mind.....
Either, the world was cruel --- or his mind was. Probably, this was to be something positive in the end. For now, he'd just stop thinking about it; it had happened today, on Friday. 
Something else was also quite interesting: He hadn't understood P. when she'd symbolized him to take a seat next to her, and thus, they didn't sit next to each other for one lecture. Then, he'd noticed that this would probably do them some good, as coming too close meant preparing a struggle. Still, he hoped that such thoughts were profoundly wrong, as they were creepy and scared him with their powerful seriousness and the impossibility to doubt them. They seemed to be like facts......
Then, he'd always thought he had an extraordinary kind of moral, but his best friend had not understood the way he was doing something and pleaded him guilty; their friendship wasn't broken, of course, but it would be hard to change his view on that subject --- but he'd try, and probably, he'd be successful. 
His mind was racing once more, so many things he had to do, and such a bunch of information that had arrived; he knew that time was valuable, and that it always ran short. 
And then, there was Y. She'd once more asked him for help \emph{before} she'd need it, and she was feeling as if she exploited his abilities; he'd often reassured her she wasn't, and told her that it was fun for him to help her, but she wouldn't listen. He wondered why she'd listened to that boy which had been her boyfriend for some month, while she'd never have accepted him if she knew something more; but she seemed not to wish to find out. However, she seemed intelligent, and he felt that she could do better --- a lot better. He decided that he'd ask her whether she'd like to learn some methods he was using, if he'd ever meet her alone again, which happens quite rarely in university. 
This was the change in the environment; of course, P. was now also changed, as she'd accept his newly developing character, and P.'s friend did the same. But these are consequences of the changes inside, and we shall now have a look at them. 
The most interesting thing was the fact that he seemed to have managed to forget about O. --- consciously, that is. Only some things that had been burnt in --- like those numbers or the sight her car --- were left, but his on these reactions seemed to vanish, too. Slowly, but they did. 
And this left room for development: Suddenly, he could talk to people, and he was trusting more and more of these other beings out there; P. had teached him to do so by her way of acting, and her friend had done so, too. He knew that the foundation of that development still were the things he'd learned from O., but he'd realized that this \emph{had been}. Now, he was somebody else; he had an identity, and people \emph{knew} him --- and would remember him as somebody special who'd accept them all as his friends, though he still maintained an own opinion. This was a development of his profiling system; it becomes apparent when we have a look at some recent event from today: L.-B. had just beem walking down some path together with many other students, while he was trying to catch up with P., walking now just some 20 metres behind her. L.-B. was some 20 metres away, too, and he hoped she wouldn't see him; no, he \emph{believed} she wouldn't, which meant that she did, of course. Still, even though he was drowsy, he could see her, and he decided not to turn his head and walk on with this silly hope. 
But she catched up quickly; she must've run \emph{very} fast. Only some seconds later, she touched his shoulder, and excused herself as she'd thought she had startled him; she had, in a negative way, but he wouldn't tell her; this was something he'd already discussed with P., and he'd explained her that telling L.-B. about it would lead to a discussion that wouldn't end until she'd feel he'd decided to think differently. He didn't want that, as he could now pretend not to have noticed; then, he would have to lie to her directly to make her go. 
She'd tried to talk to him a bit, btu his answers were short and even an interesting joke of hers wouldn't change a thing. With P., he'd probably have laughed about it, and when he reached the bus stop, he told the complete story to P. 
His mother had told him that he should rather stay without girlfriend, but with good friends, which would make things easier; P. had told the same, as you may remember. He hoped for something special to happen, but he didn't know what was to be. 
For now, he was happy that he was finished, as he could rarely type correctly, because he was --- once more --- tired to the death. 
Nevertheless, you may look forward towards more to come --- later on. 
Please stay with me.........
And what about your opinions?
To be continued...
This week, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

Knowledge 
is full of fear, 
as it gives us the power 
to reason. 
Reason 
is trying to find out 
how to deal with knowledge. 
And this process 
is painful. 
\emph{W.G.}

Sleep 
is close to death. 
And death 
is close to heaven --- 
and to hell. 
There's good and bad 
in everything. 
Why don't we realize? 
Because we want to live 
properly, and happily, 
thus destroying ourselves. 
\emph{W.G.}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_First_Era.tex"
%%% End:
