Hello; it's me once more!

This time, there's more time left to write, but I know that less information is to arrive in the upcoming weeks. Thus, you'll probably have to wait a bit longer, but I guess you an cope with that, if you're still reading. 
Many small things have happened, and fate interfered in several details; signs had been there, and he didn't know what to do about them. You'll see what I'm talking about if you continue reading. 

\textbf{He felt the}
\textbf{[u]Rage of Inversion[/u]}
Several days had gone by, and the most fundamental changes had taken place in his mind; out there, most things seemed to be constant, with the exception of yesterday evening and this morning, but we'll deal with these moments later on. 
Now, it was Friday, and he did not have to go to university for two weeks. The time of Easter would soon arrive, and he knew that the long days he had would pass in no time. This morning, he'd just slept till half past one pm; Now, he was even more tired, as he could realize how tired he had been. We shall deal with yesterday morning  now, and then e could have a look at the signs that appeared in masses after that morning had gone by. 
So, what had happened that morning? Nothing so special, in fact; However, there are still some details left you should know. For a start, he'd seen O. several times, and she hadn't realized he was there, or at least pretended so. In addition to that, he could not recall all the moments when he'd seen her; However, he could still remember the way she acted, ignoring all those things around her. Had he really overestimated the subtle abilities of interpretation he'd thought to be inside that girl?
Now, he wasn't sure. Another professor had phones him yesterday, and it just meant that he'd soon be able to leave something behind for everybody to see; a short article in a book, nothing more. He himself had never really published a thing. 
But today, he'd start writing another story, and you'll be able to read it; For now, just in the forum, but a new version of that page here will arrive soon. 
On the other hand, his mind was changing, realizing the fact that logic was \emph{not} the exclusive basis of everything. There was something inside his mind he couldn't control, and surely enough, it began searching for a person; G. had gone, O. was still there but out of reach, and P. had disappointed him by forcing him to do something; which left P.'s friend and B. His mind had projected the name of P.'s friend quite often the other day, and it was connected with nice memories. However, he noticed what was happening, and he felt that he could still control it. 
And he'd realized that emotions were just a kind of natural program to control logic. 
Yesterday evening, he'd also talked to P.'s best friend, a girl he'd never seen. It was just an online-communication, and he made her laugh, which seemed to be quite easy. On the other hand, her character seemed to be very strong and it wasn't easy to talk her into something. 
The things she'd told him about her boyfriend were pretty interesting, and he was eager to find out more; on the other hand, he was longing to return to silence and quietness in his existence as an hermit. 
Soon enough, she had to go, and he was left alone once more, in the happiness and sadness of contemplation. When he was downloading a file that evening, there was something special about it: Its size was "3.43 MB"; I hope you can still recall the meaning of that number ('343'). He was shocked when other numbers appeared exactly when he had a look at the progress bar, and they were all connected either to O. or to G. 
Then, this morning of today, his computer had just deleted some data though it shouldn't have; it would take him several hours to do the recovery, but the special thing was the fact, that the number '343' appeared once more. 
He was wondering what was going on, but he felt he couldn't do a thing but wait and see. 
And then, while he was typing this text, he had a look at his CPU-temperature; the checksum of it was '2', O.'s number. 
Her best friend had greeted him once happily, and he'd then done so, too; the next time, when she didn't face him directly but noticed his presence, she didn't; Then, he took the initiative and she just answered normally. These details were the foundation of the thought that she was also one of the persons that did not think the thoughts of the others. 
Probably, it was his problem that he did. 
When he saw a person, he was always wondering whether it would be interpreted by him or her in a good manner if he greeted that person in this or that way; most of his actions would have to be double-checked by interpreting the possible reactions of the others before he finally acted. 
Tomorrow, there'd be another day with O.'s checksum; but he doubted that anything would happen. Three weeks and one day later, however, he'd be on a birthday party, and though he was pretty sure that O. would not be invited, he'd like to go there and be among his other friends. 
Suddenly, he realized that he was starting to enjoy life even though there were many hardships out there; but if they had not been there, happiness would have to be cancelled, too. A further look at his CPU-temperature revealed that it was constant; he didn't know what that would mean as a sign. The checksum of the clock, however, was now the checksum he'd associated with her boyfriend. 
Some days ago, he'd also talked to B.-B., who seemed to be interested in that communication, and he shared that interest; However, later on, she wouldn't tell him about the further developments that had probably taken place. 
That was just a marginal thing; L.-B., however, seemed not to give up. Just some days ago, she had inquired him about something he hadn't known, and she didn't let him go until he promised to tell her about it via phone when she would call him. He hoped she wouldn't, but he knew she would, though the piece of information she requested was available freely. 
[quote]
Your uniqueness is more than outer appearance. 
\emph{(from a small fortune cookie program)}
[/quote]
The only problem with that quotation was the fact, that emotions were naturally ruling over logic, and that they were mostly controlled by the outer appearance. Thus, he knew two people who had fallen in love with R.; The reason seemed to be her very smooth skin in addition to the feeling of a need for protection that would be induced when you watched her. 
The only thing logic could control was the amount of time one spended looking at somebody else; Thus, he used this 'exploit' to control his emotions, and he felt it was the only way to do so. 
He was slowly calming down, and the life of an hermit could begin once more; Now, he'd be on a lookout for people whose character was really special. 
The problem was that he still wasn't sure that O.'s character wasn't. 
But for the next days, he won't be able to find out. Thus, you'll have to wait some longer time, but I'll try to collect more information. 
Please keep reading!
Your opinions?
To be continued...
This week, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

Silence 
is all we need 
is all we hate 
is all we gain 
is all we give. 
Safeguard the silence! 
And destroy it. 
\emph{W.G.}

Sometimes, 
life's an abyss; 
Sometimes, 
life's a mountain; 
At every time, 
one should know 
that things will change --- 
for the better 
or the worse. 
\emph{W.G.}
