Hi! A long time, yes; and loads of new things!

This will most probably be the last one of those posts in this project. A new era of my life is to begin, and O. has become a friend; no more. The final decision is yet to come, but you'll see what I'm telling you if you just go ahead. 

\textbf{At last}
\textbf{[u]Bidding Farewell[/u]}
Yes, this was the time of farewell --- it really was. He'd found out that in a time of overload, when he was busy all around the clock, he didn't think of O. anymore. 
And sometimes, they could talk as friends again. 
Now, this time was nearly gone, at least, the load had become lighter; and this very day, this Wednesday, had shown him how much he had changed. 
This Friday, he'd close the door that could guide him back to his memories; but not in an eradicating manner, but in a way of changing his attitude towards her. A betrayal of his own, yet buried feelings......
So, what had happened?
There would soon be a day quite like tha last one when he was together with O. quite long, and was still loving her. Now, he was offered an interesting possibility to take part in a project, which would mean that he would not be there that day. And his contemplation had guided him to the idea to take part in that project, though this was one of the first moments when he started thinking about O. again. Exactly this was the thing that gave him that shock: He realized how long O. had been gone for him. When he looked at her now, she was just a girl; a girl with potential, yes, but nothing more. 
On Monday, she'd received a bad mark, and he felt he should comfort her; he couldn't, and he didn't. 
And this very Wednesday, he saw her reflection in a glass when she was arriving from behind; first, she didn't notice him, and he pretended not to do so either. 
He knew she wouldn't talk to him right now, for she had become quite silent in front of him since some time. 
He greeted her, walked next to her, and the two of them began talking. 
It was just a time of probably ten or fifteen seconds, but she even laid her hand on his shoulder, now comforting him. This was friendship. 
However, he felt that she thought different about this friendship, for it didn't seem to make her think that they should talk some more. When reaching the door, she opened it, for she had been faster than he had been; He waited for her to go through, when she was stopped by somebody else. She was talking to that person, and he stood there for some seconds --- and was gone. 
He left her in a similar way she had once left him, when he didn't comfort her at that bus stop after somebody had run into her. 
The feeling of guilt wouldn't take long, and he knew he had succeeded. However, O. didn't notice him in any way when passing next to him some hours later, but now, other people were present. He wasn't sure if she had followed him that morning after having finished that communication, but he thought he could remember her just having arrived shortly after him in that room. As she had not been that closely behind him, she must have gone fast, as if she suddenly liked talking to him; when they were alone. 
This illusion told him that there was still some danger buried in his thoughts, and he realized he must extinguish the small fire that was still burning somewhere. 
One could still relight a fire by collecting new wood after that, and if the liquid that had been used to extinguish it had been dried, the place would already be prepared for a new flame to rise. Then, this flame could rise to even greater, longer power. 
And the main stream of air that had been lighting it had already been taken away, for he had turned most of his love into desire which could be destroyed more easily; Now, O. was more like G. once more. 
And P. seemed to have found out some of his feelings, at least she assumed something, for she didn't seem to like talking to O., really. On the other hand, she'd written down something about O. --- well, indirectly about her, as a teacher had used her nickname without knowing about that. Nobody really noticed, it seemed, but he knew, and she probably knew, too. And that sentence was something special: "Dead, dead, dead..... As dead as.....", followed by her nickname and some other things. P. had written down only that part with O's nickname in it, probably to publish that when they'd leave university. And that nickname was the name of a race that had extinct long before.......
P. had once even comforted him, touching his shoulder and stroking softly, irritating the others around; he would not really react in any way but only show a smile, and leave it there. P. would stay P., and he would stay himself, and both would be friends --- no more. 
Some people were telling him to give in to a relationship with L.-B., but he knew he could resist, and the more L.-B. tried to light the fire, the more she'd extinguish its flames. Too much air can kill a flame, and keep it from relighting --- sometimes, forever, and even before it had been lighted. 
His best friend was still after R., and seemed to have become a friend of her --- well, not so close a friend, but at least he was talking to her, while she seemed not to realise a thing. he could make her laugh, while his best friend seemed not to dare to do so. 
He wondered whether this fire could be lighted, and if so, if it would not die because there was too much oxygen, so that the flame would eat the wood without satisfaction, leaving an empty place behind. 
He wondered what was going on, and what was to happen. 
B. had this time approached him, not the other way round; another girl with a black aura seemed to be in a conflict. This girl seemed to be in love with somebody, while somebody else was certainly loving her --- and she knew that, and tolerated him. That could make one wonder whether she was after somebody else......
She was a real good friend of his best friend, and this one had asked him whether he liked her --- in a special way. 
He had denied that. He liked her, yes --- but nothing more. 
Since that time, she'd talked to him less, and he was wondering whether this was to say something, but he was pretty sure it wasn't. 
And another shock had struck him on Monday --- he had found old records, concerning G. --- or O. Records from a program for divination --- several programs for divination. And in the time he was still in love with G., they had told him about O., and once he'd even asked about her --- to find out about how to impress G. 
At that time, he was still inexperienced in that interpretation, but now, he could see that these results had been true --- they had hinted at O. 
He had been blind, as simple as that, as he hadn't understood a thing. 
\textbf{I} hadn't understood a thing. 
But it was over, and the future was uncertain --- well, probably, at least. 
And now, just a small update to show you what was going on: This very Thursday, he had only shortly been to university, but there was something he wouldn't forget that quickly: A sign he'd seen out of a car; A number representing O. and G. \emph{(in fact, this was the time the clock showed in that car)}, and then a plate showing "AWAY". This was something that finished this era completely, and he knew that this was the time of goodbye. When he saw O. this afternoon just passing by, he simply said "Bye!". 
And she replied in the same manner, smiling. 
He'd decided to finish his remebrance and kill his memory just that Wednesday evening, and he'd done so. O. was gone, and a simple girl was left right now.
Even those other friends of his he heard talking about her could not change his opinion: Though they didn't seem to like her in any special way, they accepted her kind of humour. 
And that was the most special thing about her, her way to show compassion; but he had seemed to have overestimated most things about that girl. And when he took a look at a picture from her now, his mind was not as full as before, and nearly all of that racing thoughts were gone. And that Thursday, he'd eaten things he'd never eaten before; the new era was just lying ahead, but he would take some parts of O.'s character he'd also integrated in his own with him. Finally, we all are a patchwork of other characters. 
So, this is the end of my presentation for now; I've just mastered the first era of my life, and learned what it is that we call love. Things that can be said so simply with one word suddenly are as complex as a book, and even then, you can just take a glimpse of it. Loving and to be loved is something you must learn --- those lines can only help you to understand what is going on with yourselves, in a similar way they helped me. Humanity can never understand itself completely, as this would mark its downfall. 
For now, I'm done --- a new era is to begin, and a new project will start as soon as some event has marked its beginning. For now, I'll take part in this project off from school and visit the girl that was present while the first denial took place --- the girl that was in a stable relationship for a very long time, and I hope this will stay a symbol for stability, having experienced such instable thoughts. She was the one that could understand many things by looking at someone, and probably, she had once had a closer look at me, for she knew a lot about my character --- only that she wasn't up-to-date. 
You'll have to wait some days, weeks, months, or years for the next era to begin --- I dare not say it will be happier or better or anything like, but it will certainly be different. 
So --- one last thing: Whatever you do --- Be on a lookout, but don't forget to look out for your own line of thoughts! 
To be continued...
In another era, at another time, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

Life is a game --- 
there are levels, 
and at all times 
the game can be over. 
But most times, 
there is no savegame 
you can return to. 
\emph{W.G.}

The innocent contemplater struck 
by the lightning of love; 
The guilty murderer given 
the gift of passion; 
And the innocent murderer, 
the guilty contemplater, 
standing in between, 
watching in boring, 
joyful awe; 
this is life. 
Choose your role! 
\emph{W.G.}
