\chapter{The First Arrival}
\label{cha:first-arrival}
Crack. 
This was the only noise he'd heard for hours: The cracking of dead twigs beneath his shoes. And it was only for Simetra he went on walking, for something had took hold of her, a kind of nervous happiness. 
He had spent the time thinking: The black figure that had destroyed the wood only for it to be built up again; How could such a system have developed? And why? 
It was a kind of steady state, based on steady change --- it was \emph{life}. The ups and downs of life had found their symbolic expression right here: Though the woods seemed dead, they were alive --- half-alive, at least. And the processes of destruction and construction fit so perfectly as if they were made to be presented to somebody else to watch them. 
However, it was all a system of steady-state, in the end. It didn't make any sense, destroying and rebuilding constantly. He'd sometimes seen the inhabitants of 'his' village fight each other, crushing their houses, only to rebuilt them shortly after --- this had been senseless, too, and he couldn't understand the motivation for those fights. 
Nevertheless, this left him to realize one thing: There was a lack of sense in life. 
There certainly was. 
But still, he felt that there had to be some motivation he couldn't understand in those actions. 
A sudden burst of sunlight, the first since hours, and a shriek of Simetra told him that he was close to a clearing; he didn't know what was waiting for him, but he had to be very cautious, of course --- these peculiar black and blue figures could have killed him, if it wasn't for Simetra's warning. 
He was staring concentratedly towards the area where less trees were trying to suffocate everything else --- the clearing seemed to be about one hundred metres in front of him. 
Slowly, and prepared to face nearly everything, he advanced, trying to make no sound though this was pretty hard to achieve with all those dry, dead twigs beneath your shoes. And the silence around him seemed absolute. 
Soon, he had reached the place where the clearing had to begin; He could hide behind two trees and overlook the area, where no dead forest was growing. And it was green. 
So green, in fact, that he was blind for some seconds until he had readapted to seeing a patch of nature so vivid. But this place was small, and he realized that it had probably just been left out by chance, as the black figure that destroyed the forest seemed to advance quite randomly. However, there it was. 
And he took a further look at it; But it still took him some time to notice the most special thing he'd ever seen: It (sat? stood?) in the middle of the clearing, on some big stones that had been arranged in a way that pleased your eyes, as if somebody had really done so on purpose. 
And that --- creature --- was as green as the grass around those stones, and it still took him some time to make her out clearly, for she was a female --- a fairy. He could remember the things he'd read about fairies: Once upon a time, they must've been all around, and the book only said that they brought happiness to the people. 
In some inexplicable way he was attracted by her --- she was sleeping, and her head was lying on one of these stones, her hands put underneath to protect the bright, shining skin from the rough surface. She was emanating light, and her hair seemed to glow in a yellow colour, and now, he could even make out a glimpse of her shiny, translucent wings that were folded on her back. 
She was pretty, if you can say that about a fairy, and he still stood there, wondering how she might have come into this dead forest. It must have been her magic that had conserved this patch of green, or some other magic that had conserved both. 
His hand moved to shove away another twig so he could see her better, and the light green of her dress began to move as she became awake. 
Quickly, the thin body moved and particles of white, glowing dust were emitted from her as her bare feet touched the ground. Looking around nervously, the small fairy couldn't make him out immediately. He decided to take another step, and the green fairy shrieked before she rose into the air displaying an abnormous speed. Simetra sat off quickly to follow her, but she was far too slow to do so and soon had to return to him for the fairy was gone, leaving behind only a trace of that white, glowing dust that dropped on him, giving this boy a warm feeling as it touched his skin and stopped glowing. He had quickly run to the stone in the middle of the clearing, but he could not see her anymore. 
He was amazed, and puzzled for a minute. Fairies had been inventions of that old books --- they had been part of stories that had been written for entertainment. They could certainly not be real? Well, they were as real as that black and blue figures that 'worked' on the wood. 
Astonished, he felt over the stone that seemed to be still warm --- it was smooth, and more of that dust was lying on these rocks. He sat down, and felt quite comfortable, for the stone that was supposed to be hard wasn't. 
A splashing sound woke him up immediately: A small fountain had emerged from the middle of the stones, and it looked as if it had been there forever, but he was sure it had just developed. 
The water was very clear, and it seemed to shine with a light that resembled the light of that dust --- then, he realized that the dust that was lying on the stones was still shiny, while the particles that had touched his skin weren't. 
He recalled the prickling sensation he'd felt when they had dropped on him, and he realized that they must be important. Taking out a pouch of leather, he collected them, using a piece of cloth so as not to touch the glowing particles. Even if there was no magic about them, they would serve as a light in the dark. 
Simetra came down again and dropped on one of the stones, suspiciously analyzing the water and sneezing as she'd breezed in some of the dust. 
He'd just closed the pouch as he was shocked by a noise that must be part of his imagination, but wasn't. A --- familiar --- voice said: "You may drink, it's not poisonous." 
Simetra was talking. 
If he wasn't subject to a sudden and inexplicable illness, this dust must be full of magic, indeed. 
And he decided to do what Simetra had told him, and he gladly swallowed the fresh water --- it was sweet and vivid, remembering him of the fairy that had made this spring come alive. The flask he had with him was filled quickly, and after Simetra had drunk, the spring went dry. 
All of a sudden, the tiny rests of the dust vanished, and the stones seemed to begin to move. The clearing seemed to go away. 
Simetra rose high with a shriek and came down again quickly, but he was already standing in the middle of the dead forest again that had filled up the space the green grass had filled before immediately. 
Simetra told him that the clearing was indeed --- moving away, shrinking against the horizon. He was still afraid to hear her talking, but he was getting used to it, as he had always imagined her talking to him --- only that she really \emph{did} so now. Irritating. 
But she was right --- as she told him the direction in that the clearing was moving, he knew he had to follow her. It was the only place he'd ever seen since he'd left the village which wasn't dead, and which was full of fascinating magic. 
He had to see it again. 
He had to see her again. 
And he had to find out what was going on here, even if it took him hours to reach the clearing again. Or days. 
What else could he do? There was no water around, and he'd need more; And the only place where he knew water was to be found was the clearing. 
He took a step, and another one, absorbed in his thoughts and barely noticing Simetra, who was sitting on his shoulder quietly now. 
He was striving to \emph{arrive}. 
To be continued...
This week, by Wilkie Goldentongue...
%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../Nature_of_Being.tex"
%%% End:
