\chapter{Coming to a First Conclusion}
\label{cha:coming-first-concl}
Since two hours, rain had been falling down.

He was all wet, and the grass he was walking on didn't make things better at all. He had realized that the rain only affected the clearing, for the dead forest around it would stay dry; but still, he could not leave the clearing. Not that he longed to do so, but it was kind of peculiar that you moved and the grass followed you. Though the spot where his feet touched the ground was now quite muddy, for it followed him, too, he knew he was moving for the trees of the dead forest in front of him vanished there to appear behind the clearing again.

He had steadily followed the arrow he'd found on the nut, but now, he was getting tired. Turning around and coming to a halt, he saw the stones that would invite him to take a rest; And though there was the image of Simetra in his mind, and though he knew he had to go on, he couldn't resist. No sleep had come over him for long hours, but this time, as soon as his head touched the stones, he fell asleep, ignoring the rain and the roaring thunder around him\dots

With the cruelty of a smashing hammer, a loud, crashing sound awoke him. 
He jumped, and turned to see where the sound had come from; For a second, he thought that the \enquote{roadbuilder} was close and that he could not escape him anymore;
Then, he noticed a wooden sign that seemed to \emph{grow} just in front of him.
He checked the nut with the arrow; Yes, this sign had grown in the direction he had been advancing towards, and quite easily, he could even make out the muddy spot again.

Letters began to form themselves on the still growing sign, and he was eager to find out what he would be told, but for now, he could only stay here and wait. 
He sat down on the small rocks again, and realized once more how smooth and soft they were, as if not stones, but perfect pillows; Then, he heard the sound of a tiny fountain, and he turned around to see the spring again. His thirst became apparent to him now, and he drank with satisfaction.

If he wasn't missing Simetra and the fairy, and if he didn't have a mission, he would have loved this place; but thus, he could only admire it. 
An admiration full of sadness and sorrow.

But there was nothing he could do except sitting, drinking and waiting, hoping that this sign would sort things out. 
The letters began to become visible, and he stood up to take a closer look at them. Most peculiarly, he could read them without any problems; but, giving it a second thought, why wouldn't a magic sign know how to address him in his own language?

Slowly, he began to decipher the first words, and things got easier the further he got; the sign was still growing, and a lot of text was waiting for him:
\begin{quote}
Thou hast gone far,\\
though far from far enough;\\
Your origin is still untraced,\\
your destiny unknown to human soul.\\
The twigs and branches of life seem dead;\\
and death brings life to darkness' fellows.\\
Meaningful is the choice you are to make;\\
for neither love nor death will be to blame\\
for failure of your kindred soul.\\
The trees out there could be your guide;\\
the nuts of dust could tell you wisely\\
where to go;\\
Your instinct can never be proved to be right,\\
and your logic can be, neither.\\
Lighted magic seems alive,\\
but vivid is the darkness of death.\\
The easiest way could be right,\\
but none may tell you if that's true.\\
You do know this silent speaker,\\
though you don't know you do;\\
Thou shalt not search for answers,\\
nor reason, nor emotion;\\
Life is a search for the way\\
to search without searching.\\
Swing to the left, swing to the right\\
to reach the centre;\\
but do not stay where you are.\\
You must move to stay,\\
and stay to die.\\
Thou longst for a magic creature\\
and a fellow, but shortly lost soul;\\
both are close, but far apart;\\
He who tries to leave will stay.\\
He who wants to find shall not search.\\
Yet do not stay, for change lies ahead.\\
A decision must be quick and wise,\\
for it can be made only once.\\
The late creatures you long to hold are waiting\\
in a world not yours;\\
Their magic can not save them,\\
but yours combined with theirs can.\\
Time is gone,\\
and can never come back,\\
unless the magic of the \emph{ONE}\\
turns its wheels again.\\
This singular being is me,\\
but I'm caught and bound to hide;\\
you are to find me,\\
as this is your mission.\\
I have been close to you for all your life,\\
but you have not been allowed to know.\\
I am with you now,\\
but you can not see me yet.\\
Your magic is still not known to you,\\
and I can not teach you.\\
I have told you who can;\\
be wise and go on quickly\\
without movement.\\
But don't you stay here;\\
get out!
\end{quote}
Puzzled was the wrong word to describe the way his thought were racing through his young mind, crashing into each other to combine to an unknown mess. 
What did it mean? Was his sister talking to him?

He would have to figure this out later; he could take the sign with him. But --- \emph{WHERE?} 
What did these magic words mean? He'd rarely seen such a difficult tongue before, and even the most complicated books he'd read were easy in comparison with this here. 
As fast as he could, he scanned the lines once more, hoping for an answer to come to his mind; Then, he realized that he should not search for an answer, but wait for it. 
He should not move, but he should not stay, either.

What had he done the last hours? He had moved --- and stayed. But how could he do the opposite? 
He had to \emph{be} moved. What could move him? \textbf{Who} could move him? There was nobody here, and nothing inanimate could move on its own, unless\dots
It was magic! That was the solution. But how could he make this magic of his come alive, if he didn't even know that he had any?
And how could he know that this sign was real?

He had a closer look at it; Magic had made it grow, and growth was a movement. But it had stayed here\dots
Suddenly, a burst of laughter reached his ears from far, far away. 
From the place where he had been coming from. 
And a loud, smashing, steady sound was coming closer. He had to get out, the sign was right. But how?

A shudder ran down his spine, and he was sweating more than ever. This was wrong: He was pushing for an answer again, as he was being forced to decide. He had to resist this urge to decide\dots
If the sign had been made grow by the magic of his sister, then this was part of him; part of his magic.
He took the sign and turned it around in his hands. Then, he closed his eyes, trying to become less nervous. When he opened them again, he was far from being calm, but he knew what he had to do. 
His magic would make him move.

The smashing sound must now be so close that it was only 100 metres away, but he felt no fear anymore. This decision was final. 
The first and last conclusion that would decide whether he was allowed to live on. 
He held the sign over the muddy spot, still waiting for a second. Was he right? He had to be right, and if he wasn't, it was too late; He was not to search an answer, and this one seemed senseless; He could never have searched for it. 
It must have come to him, as the sign had predicted.

He planted the sign in the muddy spot and sat down on it. He sat down on the sign. Nothing happened; what was wrong? 
The smashing sound was coming closer\dots

Yes! He would not only need his, but their magic, too!
Where could he get their magic in a second? He could not open his bag that quickly, and he would risk to destroy the nuts. He searched for an answer again; As soon as he realized this, another burst of laughter was to be heard, \textbf{VERY} close this time. 
Closing his eyes and concentrating, he suddenly heard something else: The spring! Quickly, he ran to it, took some water in his hands and watered the post, then finally sitting down on it again. 
Before he even touched it, a mass of \enquote{roadbuilders} approached the clearing, this was the sound he'd heard! They would smash him in a second\dots
And a big, dangerous, black figure seemed to hover among them, and it laughed again, grinning with an evil face\dots
