\chapter{Night of Existence}
\label{cha:night-existence}
The last rays of the sun had long been gone when he exited the house he lived in; his eyes searched the sky, and soon they found the singular star he loved, and his heart rejoiced. This was the moment of each day that was to himself, and he appreciated it. 
A big bird crossed the sky, her tail just touching the little star, and he knew that everything was alright - as far as that is possible. 
"Simetra, come here," he said in a low voice that could only be heard by that gigantic bird. It was the only creature that would never betray him, and the partnership that connected the two unequal beings wouldn't end until one of them died. All these thoughts in his mind, he raised one arm for the bird to sit on; then, his eyes searched the moon, and it was still there, hanging high above in the sky, and shining brightly on the grey, majestic feathers of the bird that had safely found the right place on his arm. 
The bird followed his friend's eyes and stared at the moon, and suddenly, she rised up again and started to fly towards it; the wonderful picture of the big creature in front of the moon gave the impression of clarity, stability and the wonderful dream of a fairytale. 
This was the Night of Existence. 
The night when he had been born, and the same night when his parents had bought this bird; and the very same night when they both had died. 
Slowly, tears ran down his cheeks, but he didn't try to stop them. Simetra knew better than return to him now and explored the sky once more, as she felt she'd better leave him alone for some minutes. Twenty years had gone by since that day, and now, the two of them were the last survivors. 
The next minutes would pass in silence. Then, Simetra would return, crossing the sky in the front of his eyes, giving him the power to hope once more, and the energy to stay alive. 
With a movement of his left hand, he made the tears go away; but the pain would stay, though it would now subside for some time. 
He took a deep breath, and his arm was shaking when he rised it once more; his broken voice called his last friend for another time, and she came. Finally, when she had sat down once more, their eyes met. Simetra felt the strong emotions and the powerful soul that was there inside him, and he felt the power of the bird; they would never leave each other alone. 
Two minutes had gone by when Simetra rised once more, and he took a walk around, thinking of the years that had passed. 
They had been happy, as happy as they could have been when you had to live on your own amongst alien people; he didn't have any friends, and only some of those strange beings around him had taken care of him. They seemed to fear that bird, the single creature that was - and had always been - his friend. 
The only creature that had saved him that night, and the only living being that knew what had happened. There must have been an attack, and the young Simetra had been found sitting on top of him who was hidden beneath a piece of cloth. Thus, the bird had saved his life, endangering her own. 
His eyes followed the wonderful lines his only friend painted at the sky; then, he realized that this night was not only a night of the past. 
The strange people that had taken care of him had only promised to do so for twenty years. 
This time had passed right now. 
He wondered whether this would be a chance or the moment which would lead to his death; His companion would protect him, but she couldn't do a thing against fate. 
Nobody could. 
And nobody could know about his or her destiny in advance. 
If he was doomed to die, he would; if he wasn't, he wouldn't, and no power could change that. 
Fate could decide whether somebody was invincible. It had decided his parents weren't. 
Nobody could go back and change that. 
Tomorrow, he'd have to leave this part of the country, and he'd do so with more sorrow than happiness, as even though these people hadn't liked the boy who had attracted so much aggression he had grown familiar with them and this land. 
He decided to take a last glance at those houses around here; the next day, they would provide him with some food and send him away. He'd already organized a horse to be able to reach another city. 
Another city - he'd never been anywhere else, and all around this place there was deep wood. This meant that he'd not be able to ride on his horse, but he'd figured out that this wood must end somewhere. However, nobody in this city had ever left it and came back to tell the others about it; the only pieces of information he could get were the ancient books of those who had travelled out there, and the things he'd learned by watching Simetra, who seemed to be awaiting that day eagerly, as she felt the growing tension of his. 
The cold of the night was becoming apparent to the bird, and she felt that it must make his friend shiver, but he noticed nothing of it, as the real cold was inside. When Simetra sat down next to him for another time, he felt the warmth of hope once more, and suddenly realized how cold it was. After some seconds of contemplation, he decided that the two of them should go home to sleep, as they'd have to leave early tomorrow. 
However, he knew he couldn't sleep, and it was not until Simetra had reassured him by sitting close to his bed that he closed his eyes, sleeping the exhausting sleep of an orphan of fate. 
Soon, Simetra would also close one of her eyes and join in to a half-sleep; however, she would always be alert if any danger would arrive. 
But this night, the only danger were the nightmare-like memories that chased him through his dreams, and Simetra could do nothing about it, though she longed to chase away any danger out there. 
To be continued...
This week, by Wilkie Goldentongue...

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../Nature_of_Being.tex"
%%% End:
