\chapter{Voyage in Solitude}
\label{cha:voyage-solitude}
The first rays of the sun had just touched his still closed eyes when one of the villagers was on his way to the house he resided in, bringing some food, the last gift he would be given by these people. Simetra noticed the person, but she knew that she'd better keep silent until he was gone; A tamed animal was something unnatural to them, and an animal that took care of a human being and showed emotions was something that could only be achieved by using evil powers. 
Thus, the villager seemed afraid when opening the door carefully, but when there was nobody to be seen downstairs, he sighed, entered quickly and silent, dropped the food on the table and was gone even more quickly than he'd arrived. 
The food was the last sign he'd left, and it would also be the last significant symbol of that village for the two friends. No letter, no word was left, and one may wonder whether the villagers gave a party because the two demons were gone; We won't ever know, as we'll accompany those two fellows without returning to that place which we won't ever see again the way it is now, with it's high-climbing trees and the small huts, the fire and the belief in evil spirits; all those details will be lost for us, and among these the superstitous villagers, which couldn't do a thing against their belief. 
Right now, Simetra touched his nose carefully, and he woke up slowly, as he felt the presence of his friend and the feeling of safety and peace the bird brought with her. No danger would come near him right now, but he knew he had to leave. All his bags had been packed days ago, and it would have taken him no more that ten minutes to get ready; but he had to take a look around once more, keeping these pictures of the beloved house in mind. He felt that none of the villagers would ever dare to touch it or live in it, and he realized that it was another friend of his who would wait for his return if he ever decided to come back. 
Half an hour later, he'd walked through most of the now empty rooms, remembering all the tiny little memories that were connected to them; Now, he stood in front of the room he'd never opened again. 
The room where his parents had died. 
He knew he had to open this door today, as he coul probably find some signs that would explain what had happened and who was responsible for it. 
But for a quarter of an hour, he just stood there, staring at the door and the old, rusty handle which had not been used for twenty years. Furthermore, all windows had been shut tightly, as the villagers had feared the dead spirits to hunt them at night; thus, he had never taken a look inside this room, and even the keyhole was shut tightly. He had received a key with the food, a key to that room, as the villagers knew he wouldn't leave without having taken a look inside it. 
Slowly, he took the key and put it into the keyhole. 
It fit. 
A minute later, he was turning it, and the old lock still worked with a 'click'. Now, he could not go back anymore. 
It took seconds until his right hand touched the cold, rough handle. Slowly, he pushed it down, and the door showed only weak resistance. 
For the first time since tweny years, rays of sunlight touched the floor of the room which had been the place where a brutal crime had taken place. Two brutal crimes, to be exactly. The only thing the villagers had ever done was to take the corpses away to bury them somewhere in the deep woods, far away from their houses; then, they had sealed the room tight. 
The first thing he saw was the blood, the blood of his own parents on the floor. Of course, it was just a stain of blood, as bacteria and other creatures had cleaned most of it away; but time could never eradicate the horrible strength of the symbolic link between this blood and him. 
He sighed, then he took one step into the room, closing the door behind him. Simetra had to stay outside; this would be a voyage into his past, and it would be a voyage in solitude. 
Up to now, he had not noticed that there was still light in this room; he searched for the source and found a golden medal, just lying next to one of the red stains. It was sending out a warm, yellow light, and he couldn't remember having seen this light before he'd opened the room through the cracks of the door; it must have started to emanate this light just at the moment when he'd opened the door. Still, he felt very nervous when he realized that he had not wondered why there was light in here when he'd opened the door. 
He decided to think about this later, and he picked up the medal. The same moment his fingers touched the (warm?) metal, a surprisingly strong feeling took hold of him; This was something he'd never experienced before. He [i]remembered[/i] something he'd never seen, and he couldn't help but watch what was going on without interfering into this magical process. 
Light flooded through the room, but not the cold, white light of a bulb, but the warm rays of the sun; the windows that had been shut tightly were open, and it was summer. The buzz of all those insects in the woods became present as he realized he wasn't alone. 
A woman was standing in front of him, and he didn't waste any time trying to find out who she was; he [i]knew[/i] his mother though he'd only seen her as a baby. The vibrating, emotional connection that linked the two beings made their eyes glow; but both of them knew this wasn't real. The urge to step forward and embrace her became his dearest wish, but he couldn't do so, as this was a holography. He wondered where this word had suddenly come from, but he understood that it was simply there, and he understood without any explanation. 
Then, his mother started talking, destroying the painful and yet wonderful silence that could not yet last forever. 
[quote]"I can see in your eyes that you know who I am, and that you've realized that I am dead", 
[/quote]
was the way she started. He was startled, but he didn't flinch, as he heard the voice of the creature that gave birth to him. 
[quote]"You must listen carefully now; please don't ask any questions, I cannot answer them. What has happened, is done, and cannot be changedn neither now nor in the future, even if it was completely wrong. On the other hand, this is probably the only way to make our vision of the future come true. You must know that powers are working, evil powers of unknown strength; I imagine you must look quite self-confident now, but know you cannot face up to them. There is one person who can; this girl is your sister."
[/quote]
A sister? Now, he indeed began to tremble. He had a family, even if it was only small; but he was not alone, though he'd never really been. Simetra was still there, and she would accompany him for the rest of his life. 
[quote]"I feel you must be astonished now. I would give anything to be able to take a look at your face, but it is impossible for me to come back. My life wasn't taken for nothing; you have survived, and your sister is well-hidden. She doesn't even know what she is supposed to do, nor has she realized who she is. It is your task, my son, to find her and to give her all the protection you can offer. Don't ask me where you should start to search for her; I cannot tell you, for anyone could find this record and listen to it. Trust yourself; your heart will guide you, and your companion will help you to accomplish your task. I must leave now; I can hear they are coming, and you shall not see how your own parents are killed. We will meet again, please know that; but don't look forward to it, times will have changed then."
[/quote]
Loud footsteps could be heard, and as quickly as the vision had appeared, the room was empty again; and this time, it was completely dark. He knew he'd seen everything; there was nothing more to do. The medal hanging around his neck as if it was a normal necklace, he exited the room. After he'd closed the door, he breathed again, suddenly realizing he hadn't done so for a minute. Still, his eyes were fixed and he could hear the words of his mother; He checked the medal, but it was cold now. It would not be opened yet; he had to think about everything, and Simetra would be with him then. 
The weight of a feather dropped on his shoulder, and he didn't need to turn his head to know she was there. 
Nothing had to be said right now; He took the things he'd packed long ago, and left the village, not looking back once more. 
The time of being subdued was gone. Now, he had a task, and he was to do something important: He had to find his sister, the only relative that was left now. 
To be continued...
This week, by Wilkie Goldentongue...
%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../Nature_of_Being.tex"
%%% End:
