\chapter{Cold and Starry}
\label{cha:cold-starry}
A light breeze was running through countless leafs over a forest that was full of silence. Everything was grey in the cold and starry night, and the sun had long been gone, only to be replaced by a full moon whose light didn't enlighten anything except a small patch of green. Slowly, the grass began to move as the wind went through it, and a tiny figure that had been lying on the stones in the middle of that clearing began to rise. The creature shook his head and searched for his backpack, which was leaning against one of the stones nearby. A peculiar, magic light was around him which emanated from the dust that was floating in the air, but nothing alive was to be seen around him. 
He was alone, and for the first time in his life he didn't know where Simetra had gone and whether she would ever return to him. 
He began to move towards the forest that enclosed the perfectly round clearing; What had happened in the last hours? A terrible headache was the misty cloud that covered his memories, and he could only wander around and wait for that memory to return to him. Suddenly, he stopped dead. Wasn't that a sound, as if majestic wings had moved the air nearby? He looked around, and then high into the sky, and finally, he shrieked to call Simetra; but there was no reaction. The wood was dead, and the air above seemed to be the same. 
He wondered how long he had slept; Now, he was very hungry. As there was nothing he could do but worry, he sat down and opened his backpack, searching for something to eat. But before he could do so, he saw the nuts, and everything came back to him in a second. He had seen the fairy in the clearing; The nuts had grown, and finally, he had flown over the sea. The wings; his hands searched for them, but they were gone, and he was wearing his shirt again. The crash - there had been a crash. The sound of the crushing trees and his smashed bones was as vivid as if it had just happened, and reverberated in his whole body. He must be dead, nobody could survive such a crash. 
Somebody must have taken care of him. 
No, this couldn't be; The fairy would certainly not have healed him? But Simetra could not have done, that was for sure. Where had she gone? 
He imitated her shriek again, and the sound echoed through his mind, but everything else was silent. 
As deadly silent as it had ever been. But he had reached the clearing, he was still there; The shiny nuts were still in his backpack, and they seemed to ask for his questions. He took a look around - this certainly [i]was[/i] a hopeless situation, and he would need some help. He counted the nuts once more, finding 11 of them - they were all there. When his hand touched one of the nuts, a question was rising in his mind, but it wasn't the correct one; He was asking why the fairy had helped him, and that was not of any real importance right now. But it was too late, and the nut told him: 
[quote]Search your memory, the answer is there 
asking things you know for long is not fair. 
[/quote]
He was close to tears. Not only had he lost one nut, but he was also responsible for this loss, and he had even been punished for it by the nut's words. Of course, the dust that was around him was a kind of magic shield the fairy had set up as she had been here; Nobody could come near, at least not if he or her was no real magician. This was what he had read, at least. And he had just played with the magic the fairy had left... 
He felt as if he was a stupid little boy, and his stomach told him he was when it grunted loudly because he was still very hungry. He could use some bits of the nut, at least, though there was still most of the last nut left. 
Seconds later, he felt refreshed and wasn't hungry anymore. The rests of this new nut had wandered to those of the old one, and he knew that they wouldn't ever lose a bit of their refreshing powers. 
This time, he concentrated. What did he need to know? And once more, he was caught in a conflict: Should he ask for the place where he could find Simetra, his oldest friend, the place where the fairy had gone, or the way he should proceed? He wondered whether Simetra had followed the fairy. But he wasn't sure what he'd be told if he simply asked for the place they had gone to. Well, he was also wondering what he'd be told if he asked how he should proceed, but what else could he ask? And wasn't all that questioning about wondering what the answer would be? 
He took another walk around the stones. He'd need an answer. The third option was the correct one. Yes, of course: The right way to proceed must be the way to find the fairy [i]and[/i] Simetra, and thus, he could answer all those questions if he just decided to ask this one. 
He breathed in once more and felt the refreshing effect of the magic air around him; But he couldn't help but see the image of the fairy lying on the stone again, and he knew he would have to concentrate very hard. He sat down on the magically warmed stone and focussed his mind on the question how he should proceed. It seemed to work; now, he'd have to take the nut without remembering the way he'd come to own it. He opened his backpack, and his hand reached inside, carefully selecting another nut. 
It seemed to work; the voice raised in his mind again, and it said: 
[quote]You ask how to proceed, 
and to be told what to do. 
Do not search for an answer, 
it is inside; 
your mind has told you whom to follow, 
just look inside: These nuts are hollow. 
[/quote]
For a second, he stayed in this stunned state of concentration; Then, he began to wonder what this was supposed to mean. He took the two small stones and cracked the nut carefully, looking at the contents. Nothing seemed different with this nut. But then, he had a look at the inside of shell that had enclosed this nutritious ingredients: This was no normal nut. Of course, he had know this before, but now, he could make out a sign inside the shell: An arrow. The other half displayed the same sign, and soon, he was analyzing the other nuts: He found the symbol of two wings and of a clearing with a kind of shield around it. Well, exactly the things he'd figured out earlier... 
But what was the arrow supposed to mean? 
One of the two pieces of the nut he was holding currently fell to the ground. When he wanted to pick it up again, he realized that it was [i]moving[/i]. It was turning into a specific direction. He laid the other piece next to this one, and it reacted the same way, pointing into the very same direction. But in which way had his mind wold him whom to follow? 
Well, he'd probably find out when making his way in the direction he was supposed to follow. Still, he was wondering how he would escape the figures that were destroying and rebuilding that forest. He would think about that later on. 
He had to leave the warm stones, the wonderful, magic clearing, and he had to do so with sorrow. He didn't really know where he was going, at least not consciously. But he had to find Simetra again; and the fairy, of course. 
As soon as he'd crossed the border to the forest, another wonder seemed to take place: The clearing [i]followed[/i] him. This could probably mean that he was supposed to follow the fairy, but at least, it meant that he was treading the correct path in a clear and cloudless, cold and starry night. 
To be continued...
This week, by Wilkie Goldentongue...
%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../Nature_of_Being.tex"
%%% End:
