\chapter{A Withering Soul?}
\label{cha:withering-soul}
\subsection*{Originally published: \DTMDate{2006-01-23}}
\begin{quote}
Hi, it's Wilkie again!

I hope you're still understanding my innermost feelings, taking part in my life in a way none has ever done before:
\end{quote}

It was Monday again; A day he'd seen her for quite a long time. But this Monday was different: In the morning, he'd \emph{exactly} known the way he was feeling, and could have written a completely different text. However, throughout the day, this was changed.
Everything was completely different and much more complex now. 
We'll begin by describing the condition he found himself in this morning: He knew that he could organize his thoughts and that he'd have to focus on forgetting her, at least consciously, to be able to live a balanced life again. And that seemed possible.

The first lecture was the one when he sat next to her. 
They didn't talk a lot, but she explained why she couldn't react to his attempt of contact and for a conclusion, she seemed quite open again. Maybe, this was a result of his now quite low expectations; but there was an improvement.

On the other hand, he could notice that she wasn't in love with him. 
And that gave him a shock, as he could now realize it clearly. 
She liked talking to him, but she enjoyed talking to her girlfriend more. 
This girlfriend of her was quite nice to him as well; He was pretty sure she already had a boyfriend, and he knew for sure she would just stay a friend; but maybe, this friendship would be something important. 
Thus, he maintained it, and he enjoyed it all the same.

His decision to try to shut off his feelings or at least weaken them by putting the emotions into a corner of his mind seemed to be still fixed. 
Another girl was flirting with him in another lecture that day; but she wasn't important, she was flirtatious with everybody, that was her nature. 
His opinion was changed when fate delivered him the message, that the two of them --- O. and he --- would be together in a group for an excursion in the upcoming week. Well, the group was large, and there were her and his best friends included in that one; but he didn't care, it was a sign. Fearing that she would try to change groups to be able to go on another excursion that would be easier to be reached, he began to think.

The theory, that an hope is only fulfilled when it has died, though interest still remains, was now proved. 
As a consequence, he should keep his plan to forget about her; but that seemed impossible now. 
The day before, he'd found a song; He'd try to use that to apply that plan, as it could easily influence his mind in a condition of trance. 
He knew how to achieve that; He'd started to take an interest in all that stuff long ago, and still seemed to suck in everything that seemed to be somehow inexplicable, keeping it in his memory, even if it was logically impossible.

Thus, he'd learned techniques of hypnosis, telepathy and many other things; also divination and astrology were to be found among his subjects of interest. 
Today, he'd only need the hypnosis part, and perhaps, also the state of trance one had to be in when he wanted to have telepathic contact, but he managed to do that quite well. 
It even seemed to work in daily life; he somehow seemed to guess things before people told him. On the other hand, this could also be a consequence of his farsighted thinking. 
Now, he just thought he would probably enter her car next week, as he didn't own one himself; Thus, he would be able to join th excursion without having to buy a ticket. Her best friend would be there, too; But his best friend was able to use his own means of transportation.

But now, we'll have a look at the lyrics of this quite modern song: 
\begin{verse}
I think I did it again\\
I made you believe we're more than just friends\\
{[\ldots]}\\
It might seem like a crush\\
But it doesn't mean that I'm serious\\
'Cause to lose all my senses\\
That is just so typically me\\
{[\ldots]}\\[1\baselineskip]

\textbf{chorus:}\\
Oops!...I did it again\\
I played with your heart, got lost in the game\\
{[\ldots]}\\
Oops!...You think I'm in love\\
That I'm sent from above\\
I'm not that innocent\\[1\baselineskip]

You see my problem is this\\
I'm dreaming away\\
Wishing that heroes, they truly exist\\
I cry, watching the days\\
Can't you see I'm a fool in so many ways\\
But to lose all my senses\\
That is just so typically me\\
{[\ldots]}\\[1\baselineskip]

\textbf{repeat chorus}\\
{[\ldots]}\\[1\baselineskip]

"All aboard"\\
"{[\ldots]}, before you go, there's something I want you to have"\\
"Oh, it's beautiful, but wait a minute, isn't this...?"\\
"Yeah, yes it is"\\
"But I thought the old lady dropped it into the ocean in the end"\\
"Well {[\ldots]}, I went down and got it for you"\\
"Oh, you shouldn't have"\\[1\baselineskip]

Oops!...I did it again to your heart\\
Got lost in this game, {[\ldots]}\\
Oops!...You think that I'm sent from above\\
I'm not that innocent\\
--- by {[\ldots]} (I guess, you'll all know nevertheless)
\end{verse}
Could she really be thinking this?
He would have to believe; It was his only chance. 
He did some high-speed divination (you may also call it fortune-telling) to prove he was right; It just told him enough to know he should go on. 
And he did.

Slowly, all the memories were seen in a negative way, as she was just playing with him. 
Maybe she was. 
Maybe she'd never done anything else. 
He needed another person to project the feelings on he'd felt for her, as he couldn't lock these away for long; He tried to separate these on all the friends he had, which was something he had been preparing for long.

Probably, P. and O.'s best friend got the biggest parts; next, there were his best friends and P.'s best friends. Now, O. was just some friend. 
His soul had been levelled.

He was feeling cold, though it was warm inside; He just felt as if he was standing in the cold wind that blew outside, cooling things down till \SI{-5}{\celsius}. 
He was shuddering; He'd have to repeat that several times for some hours. 
It was a method that worked; He felt like a Hobby-Psychologist experimenting on himself, something everybody is doing all the time. 
But he was doing that consciously, for a change.

And he didn't mind it going wrong, as there was nothing to lose; If one's feelings and hopes are not fulfilled, which never is the case, one can equally die. 
Does that mean that all of us should commit suicide?

No.
There's one hope left. 
The hope for --- the expectation of --- hope itself to return, thus rendering this return impossible. 
We all know that.
But we ignore it, as we'd die without that single hope.

Only one giving up all hope can persist; I think, there was one sentence we were talking about a complete lecture in German, and my German friends told me they've also dealt with it; I shall paste it here: 
\begin{quote}
Eine jede Hoffnung ist ohne Sinn. Kein Mensch verfalle auf die Idee, auf die Erfuellung seiner Traeume zu sinnen. Vielmehr soll er den Irrsinn des Hoffens begreifen. Hat er ihn begriffen, darf er hoffen. Wenn er dann noch traeumen kann, hat sein Leben Sinn.\\
--- Robert Schneider
\end{quote}
And finally, a third quote, as three is an important number: 
\begin{quote}
Flowers of true friendship never fade.\\
--- from a small fortune cookie program
\end{quote}
This one gave me hope. Even if everything went wrong, the power of friendship would probably save me; But I was not allowed to hope for it, as I'd already noticed myself. 
I hope you understood that one; Tomorrow, you'll probably hear a lot about other persons, as the story with O. won't continue till next week, somewhere around next Monday or Tuesday; We'll see, all of us have to wait without hope.

So, now one may ask: What was he doing to forget her, or at least shove the feelings away in some distant part of his heart?
We already know he was doing some kind of hypnosis, something comparable to the intoxicating way a rhythm can influence your thinking. 
His head was now aching, as he had listened to the song we quoted above for about an hour, but the first effects were there to be noticed; he didn't have to think of her that often anymore. 
All his memories were rewritten, that is, they were interpreted in another way, so as to change his perspective on her. 
She wasn't flawless anymore.

Some part of him still believed this, but that part wasn't in control anymore, and it would only return if there was some radical change. 
He was shaking and trembling both with pain and fear; and he was feeling cold and empty, as if life was passing out of him. 
Something inside him cracked; something died; a flame was disturbed, and it was hidden so nobody could see it's light anymore. 
Another candle was lighted inside him; Its light was different, but quite equally strong, it would be able to shine brightly. The old candle was a memory that would be locked away with the others, till the day of return came; but that was something he didn't dare to think about, as his hope for such change was now extinguished, though he would be prepared for it. 
Exasperated, he took a deep, shaky breath. 
Finally, he was done for the first time.

Other times were to come, when he would repeat this procedure, when spasms would go through his body again in a revolt against the pain he was enduring for the sake of his future; He thought of the way schizophrenic people had been treated with a high dosis of insulin, that didn't kill them, but left them in a state of continuous spasms for long minutes. 
This was comparable to it.

There's nothing more to add, if you know about that procedure; However, he did that \emph{on purpose}. 
It was like curing some mental sickness. 
Maybe, love is a mental sickness.

He seemed free to feel again, and he was happy about it. 
What he did, in fact, was just a shorter method of locking feelings away, something most psychiatrists need years to succeed with. 
He had prepared that for long, as his complete life seemed to be some kind of preparation for it; The methods he'd used were not common, but successful. 
It would most probably only take him hours, or, in fact, two days. 
He would be finished tomorrow; He was quite sure about that.

Nobody knows what is to come, and thus, we'll have to wait till the next post arrives. 

\begin{verse}
Control yourself,\\
to control the future.\\
--- W.G.
\end{verse}

\begin{verse}
A child was watching the rain. \\
It was a happy sight. \\
Innocence gave him the freedom\\
to stand there\\
and watch in awe. \\
An adult would have thought\\
something. \\
A child didn't;\\
It just felt. \\
It didn't have no hopes, \\
as it didn't wish for nothing, \\
thus receiving everything. \\
So my advise is this: \\
Drop your hopes!\\
Regain your innocence!\\
Be free once more, to feel without restraint!\\
Just watch in awe, \\
when the raindrops touch your hand and evaporate. \\
Stop thinking, when you start to feel!\\
--- W.G.
\end{verse}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_First_Era.tex"
%%% End:
