\chapter{The Chamber of Secrets has been opened}
\label{cha:chamber-secrets-has-opened}
\subsection*{Originally published: \DTMDate{2006-01-27}}
\begin{quote}
Hi; that's me again, and everything has changed!

That day gave me a hard time; I'll now probably take a break. You can read through this, take your time; I don't think that the next post will arrive tomorrow, and you'll understand why when you finished reading this. 
But don't be afraid: Thousands of posts are lying ahead, as I guess I'll continue this here for some months\ldots

You'll be astonished: The Chamber of Secrets has been opened!
\end{quote}

Friday; normally, this would have been a day without new experiences. But this time, everything was different, and all the things that had happened lost importance, as conditions had changed. 
Completely. 
Most cruelly.

The day began quite normally, as every day would begin: The bus was late. 
When he entered university, he met Y., who took another bus, but was late, too. 
Both entered the auditorium late, but the lecture hadn't begun yet. 
That would all be regarded as something normal; even the fact, that he now took his seat somewhere else as somebody had already blocked his place. 
The girl to his left was somehow puzzled; everybody seemed to be tranquillized in some way, but he'd already noticed that yesterday. If life was just an illusion of his or of somebody (or something) else, that would explain everything: Either, this person / thing was really drowsy --- or simply going nuts. 
But that was not really probable.

Probable was, indeed, that his aura had been changing, and thus the influence he appeared to have on his environment, as we are all capable of changing some parts of our futures. 
He was doing so, when he applied the method to lock away his feelings about O.

And fate seemed to notice that silly game he was trying to play, as it would put that attempt to a stop --- today. 
A cold shiver got hold of me when I wrote that lines; If I were right --- then, we would all be controlled in some way. 
Well, we were. 
Most probably.

We'll now go over to the next puzzling event: The marks all of them had to receive were to be given earlier. 
In fact, just after that lecture.

Students were all running to and fro, not knowing what was to happen, searching for an auditory with the professor where they could take seats. 
When they had found it, all seats were in use, and only O. was standing, finally talking to the professor to be allowed to get herself a seat.

When she'd got it some seconds later, she carried it --- or rather slided it over the floor by pushing on the edge --- to the seat the professor was going to use, and exchanged it, explaining that the chair she'd \enquote{stolen} from the hallway was too heavy for her to carry it into the room, though it was more comfortable. When she finally took the lighter chair of the professor, she was seated quite near to him. 
He noticed, that when papers would be passed round, she always had a look if he'd received one, and if not, offered him one; before, she'd asked the boy next to him if she could receive one, too, when the staple reached that boy, but our protagonist was unable to react, as he was sorting the chaotic staple for the sake of his fellow students. 
Finally, everything was over and they all went down to take a break; their lectures were finished for today.

He would learn, later that day, that G.'s marks were better than O.'s; but he knew, that G.'s method to learn something could be somehow compared to the quite peculiar method L.-B. was using. He was the only one who could explain something to L.-B. in a way that she understood it immediately.

But we want to have a look at the things that had happened between the time when he received his marks and the first lecture this morning, as he'd met one of O.'s friends then. 
She was the one who had a car, the one he should ask, and O. was nearby with her best friend when he did so. Well, she agreed, now having just three people in her car: O., O.'s best friend and him. Probably, there would be one more, but it could also be possible that this was finished.

Finished\ldots
an interesting word, when we have a look at the things that are to come!

Now, most of them had the possibility to go home, as they had cars or motorcycles or something like. 
O. and he weren't, and for some reason, about eight people stayed, among them O., her best friend and her friend with the car. 
The three girls were chatting with each other. There was just one other boy located in the room, and the only other person of importance was the girl without friends he'd met some week ago at the bus stop. 
O.'s friend with the car --- we'll give her a name, as she may be of importance. Her outer colour was somehow brownish / blueish, while her inner colour was really colourful and shining. 
We'll call her B.-B., as we've now mostly had a look at the outer part of the aura and named people after that, though O.'s outer colour was greyish / white. 
Well, B.-B. was talking about some of her experiences; he was just listening, laughing or smiling sometimes, waiting for O. to speak. 
The most interesting thing he learned was the fact, that she was trying to phone her boyfriend, but he didn't answer, as the number didn't work. It didn't seem to be correct, as she'd already checked it on the internet.

On the internet\ldots
His attempt to contact her\ldots

She'd told him that her computer was somehow defect, and he'd believed her; and he was pretty sure she hadn't looked up that number at university. 
This fact now occurred to him, while he was writing this lines, typing in a steadily increasing speed as his anger soon was stronger than ever. 
But it wouldn't become too strong, as she'd already said some other things before. When she explained that her boyfriend didn't seem to care about answering (he was on a trip, on some holiday; at some place where she didn't like to go, as she told them later), B.-B. said that she wouldn't accept something like that and stop such a relationship, and he was now eager to hear her answer. What she said would induce the development of a wound in his soul.
And a knife would stick in there, so no blood would be able to leave it; but the pain was something he'd have to endure, nevertheless. 
For some more minutes. 
She said that she understood him preferring to be together with his friends, drinking alcohol. 
And she was serious about that.

B.-B. said she wouldn't understand something like this, and some minutes later, the pain was so powerful he had to go to the library to do something else. 
Some students he knew were developing rumors in some sort of childish play, and some twenty minutes later, he would have to go for the bus. When he just was about to exit the university, O. arrived, alone, smiling at him; she was going to be taken home in G.'s car, as she had to be home fast in order to do some call; probably, she would have to call her boyfriend, again. 
But she wouldn't afford it to call him on his mobile, as that seemed to be too expensive to her.

She'd already explained something else today: As she said she wouldn't go on a holiday to the place where her friend currently was, the person of our interest felt offended; some months ago, she'd have liked to go there, and he'd liked it, too. 
And he still wished to go there. 
She didn't.

That was one of the first things he heard that didn't connect the two of them anymore, and she added happily that she'd rather do something else, something he didn't really like. 
Her best friend seemed offended, too.

But now, he was talking to her, telling her he'd now take the bus to go home. 
She told him he could also join her and G. in the car to fetch the bus more securely, and probably, some earlier bus; he agreed, though the knife still stuck in the wound. 

She even offered him that G. could take him home, though that would be quite a detour. 
Thus, he told her that it would be a real long way, but before, that hadn't impressed her; in addition to that, she was in a hurry, as we already know, and would exit the car before he would arrive home. 
But he didn't believe what was to come, inevitably.

The first girl had exited the car, and he was alone with G. and O., when O. said to G. she could simply drop him at the place where he could wait for the bus, and he didn't say anything against it; but with this sentence ringing through his head, he knew she wasn't loving him, in no way. 
And that was the power that turned the handle of the knife.

A pain shot through his body, and he was stupefied; now, he was just able to apply his profiling system, and he did so, in a way the two of them didn't seem to notice. 
It was quiet in the car, before he exited it, and he just called \enquote{Goodbye, and nice weekend!}, when he left. He didn't hear their answer, but he saw them hurrying up even more, as the car sped along him. 
It seemed as if it was happy to be able to go even faster, after having spat him out quickly.

Maybe, the persons in it were. 

Now, he was disillusioned. 
Completely. 

When he had a look at the time the next bus would arrive, he was shocked: He would have to wait for no less than --- 50 minutes. 
But he would be thinking all the time, opening the adamant chamber again, the chamber of secrets, to destroy everything inside. 
He now had the power to do it. 
It was finished.

His soul was free again; still, some parts of his love remained, and he would be able to love her again, probably; but not so quickly. 
The knife had hurt his soul, and now he was able to take it out again, as the wound was closing; the ulcer, which once had been a mustard seed, had been destroyed by now. 
It was getting colder all around him, as though the sun was shining, it was just about minus four degrees Celsius.

But he wasn't freezing: The fire of his soul had been lighted again, and the power of his self-conscience was developing; maybe for the first time. 
Maybe, she'd done him some good, as everybody does, no matter if it's bad or good. 
It's always something good in the end, as we learn to avoid the bad and to search for the good. 
Mostly.

He stood there, freezing though feeling warm; then, he closed his eyes, waiting for some darkness he could see on the back of his lids. 
But he just saw a reflection of himself; Maybe, this was the sign he'd found his own soul, his innermost character. 
He felt like that, at least.

Having reached this inner stability, he was capable of having a look at the place where he had once sat together with G. and O., while G. was sitting next to him; this was the place where he'd once been alone with G.

Now, it was covered with snow, and he knew that the sun couldn't melt that sheet of ice for the rest of his life; this experience would be covered forever, most probably. 
He remembered something the other girl had said in the car some minutes ago; she said she'd once finished her relationship to her former boyfriend with an SMS. 
She would never do such a thing again, she explained.

G. answered, that she also didn't like it if she'd have to say such a thing directly, standing in front of him; O. seemed to prefer that way, but she was nearly silent. 
He noticed that these girls seemed to be playing with their boyfriends, doing some kind of trade; This became obvious, when the other girl said that she wanted to leave her current boyfriend, as he didn't really take an interest in her life; But she wouldn't tell him now, as she didn't like such situations.

And that childish manner of them was something he'd never seen or believed with O. 
Now, this became realistic. 
All these girls were children. 
Maybe, everyone was. 
A child. 
Somehow. 
He suddenly realized that he wanted to be a child, sometimes, too; But he knew that he really wished for a girl thatwas acting in an adult manner, understanding him, and he'd always thought O. to be that girl.
Now, he realized, that this wasn't so sure as it always seemed to be.

He finally entered the bus, when it arrived; Then, he was on his way home, together with some other girls he knew. Was the world just consisting of girls?
It seemed to be like that, as the only persons he met when he wasn't together with his best friend were girls. 
And somehow, they seemed to be more adult that most of the boys; but still, they were childish. 
He passed by the homes of G. and O., and saw their cars; but he didn't see them, though some part of him still searched for their faces. 
It was finished, probably forever.

The chamber of secrets had been opened, but not to replace the enemy and former beloved in some kind of radical substitution with somebody new, as had happened with G. and O.; this time, he was on himself. 
And that was even harder, but he was prepared.

He would be prepared to endure anything, as he'd already been through the most straining hardships of life; something most geniuses had endured in their youth; It would be possible for him to realize a great future. 
Probably.

By now, the swirling, blubbering and fluent thoughts that had been boiling in his stomach were nearly all banned into that text; he was happy again, experiencing some new sort of happiness. 
Both of them had looked beautiful today; but now, it was finished. He wouldn't tell them. In that desperate attempt to contact O., he had told her about this texts; It would be interesting to see her reaction when reading them. Now, he's done everything he can do, and it's her turn, if she decides that there's some future to it. 
But this post still isn't finished.

He arrived home. When he wanted to turn on his computer, to write it, there was a power outage; The energy was back seconds later, as he switched the fuse on again; but as it always was the case, the radio of his mother in the kitchen was switched on and searched for the radio stations randomly.

He entered the kitchen, as he was home alone, to program his mothers favourite station to its original position again, when he heard the last words of a song: \enquote{Life goes on, I'll be strong again}, or something quite equal to it.
A shudder took hold of him, as he realized the chance that this sentence was exactly begun and finished in the moment he'd entered the room --- and exactly after the power was up again --- and exactly when that station was tuned in randomly --- was near to zero. 
Fate had interferred --- something was there, controlling our lives from the outside. 
Or somebody. 
A planning entity?

The idea wasn't new to him; he'd always thought that fate was just the expression of thought in reality, of some particles of conscience that were flowing, unseen by the living creatures, but sensed by them; they were giving them their consciousness. 
That was the idea he believed in.

And it was in the book \enquote{His Dark Materials} where he found the explanation, though it just told about it metaphorically. 
There was an emptiness inside him, but he knew it would woon be filled again; thoughts would live forever, and consciousness would never die; only bodies could. 
And these particles of thoughts would always search for partnership; there was a lot he could tell. 
\begin{quote}
\enquote{Tell them stories. They need the truth. You must tell them true stories, and everything will 
be well, just tell them stories.}
--- Philip Pullman
\end{quote}
Well, he would continue, as would his life. 
He would still be breathing when O. was in the north, far away, to continue her studies in the hometown of her granny; but that was just a silly, childish plan, as nobody should plan --- plans never happen to come true. 
Try it for yourself.

After such experiences, I feel empty, and I'm in need of time to recover. 
But there's one thing I want to add: As he turned on the TV while eating, he saw some news about exactly the same town we've just talked about, and then, he switched channels and happened to find some series, where one of the main actors shared his name: He just saw that by chance, as the introduction was sent at exactly the same time he'd switched to that channel. 
Was it another sign?
He saw the title of the series: \enquote{Live for Love}.

As he thought that to be another sign, he had a look at it, though he would normally have switched to something else by now. 
The main actor was fianced with a girl that had blonde hair, like O. Somehow, she looked quite similar, though she was a completely different person.......
Was it time for another CUTOFF?

No. That was gone, too. She was now part of his past. Maybe this was the best foundation for a new relationship with her, at least, that's what his theory told him; we'll have to wait and see. 
He didn't know if he hoped for something like, either.

This one has exhausted me; as I've already told you, I feel empty. New sensations are to come, stay tuned, though it may be that I'll take a break, but saying this also induces the thought that there'll be a lot of new sensations arriving this weekend, though I don't believe it.

Please stay with me, and tell your friends about it --- I can already see this forum is growing. 
And maybe, I'll help one of your admins, who proposed me via PM to include this into an RSS-Feed, to do so; but there's still some formatting missing, so you could read the texts without entering the forum, then. 
We'll have to wait, but you can look forward to it, if you want. 
You can be sure another post is to come, but I'm not sure when it will be finished, and if it will contain much more information apart from poetry, as this one's about \SI{150}{\percent} length of the \enquote{standard} I've tried to apply till now; but life's not predictable, and you shouldn't try. 
Hope that you are still out there\ldots

\begin{verse}
The shell has been cracked\\
with the sharp edge\\
of ignorance's knife;\\
now, the inside is not protected anymore,\\
and it has been hurt. \\
But this is the only way to gain freedom\\
and to achieve a final peace. \\
--- W.G.
\end{verse}

\begin{verse}
He was still longing for her grip\\
her embrace\\
the touch of her fingers on his shoulder,\\
though everything seemed to be gone; \\
but nothing would ever be lost\\
as everything was saved\\
in the eternal, gigantic brain\\
called consciousness. \\
--- W.G.
\end{verse}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_First_Era.tex"
%%% End:
