\chapter{First Steps}
\label{cha:first-steps}
A light breeze cooled his neck when Simetra dropped on his shoulder again. There was nothing she could report; everything had become silent after they had passed the ancient gate that guarded the village, While passing through that gate, he had felt some kind of separation and insecurity, as if leaving a safe haven, even though the village never was friendly to him.
However, the environment he was passing through was bereft of any live animals, and the trees to each side had grown so high that the sky was not to be seen. 
Simetra had been up there several times, and she had just returned, but there was nothing she could do. The end of the forest could not be made out, and even for her, this was a new sight, for she had never been so far away from the village that she almost couldn't see it anymore. 

The path he was treading upon was completely covered up with branches and leaves so he could hardly go on, but he was determined to do so. At least three hours must have passed by now, but the surroundings hadn't changed since the time they started, while his mind told him that the scenery was even darker and more dangerous. Simetra was unnaturally nervous, and the silence that was only interrupted by breaking twigs below his feet seemed to hamper his breathing, for it was a weight much heavier than his backpack could ever be.

Simetra rose again, and broke through the roof the trees had constructed above them. For him, the lone silence became a load even heavier.

About five minutes later, he began wondering where Simetra had gone, but he knew she would return; Probably, she was flying farther away to find out about a way out of this graveyard of nature. Realizing that walking on wouldn't help for he didn't see the ground anymore, as it was now covered up completely, he sat down and ate a bread and an apple. Then, he noticed what was so special about this forest: There was no water, and the bottle he had with him would only last for a few days. This forest must have been dead for ages, and one could wonder how it could still be there, for it seemed so thick as if it was still growing --- but it wasn't alive. 

It was deserted, in the literal meaning. 

And water seemed as rare as it was in a desert. He'd read about deserts, in the ancient books, but they were full of sand, and this one was full of trees --- however, the description seemed to fit perfectly. 
A cry of a bird disturbed his thoughts --- Simetra returned. He answered with an equal cry, and she knew where to find him. After she had crashed through the treetops, he offered her some bread, but she nervously moved her beak, pointing behind him. There was nothing he could see, but he realized that somebody --- or something --- must be coming. Simetra had warned him. 
Quickly, he hid behind a big, black tree, after he'd stored the food in his backpack again. Simetra sat on his shoulder, and the two of them stood there, behind the tree, watching the dead place in a million of dead places, waiting for it to reveal one of its secrets.

He watched to the left, for this was the direction Simetra had pointed out --- the leaves began to move.

Everything was silent, and not even a breeze could be felt, but nevertheless, the leaves moved.

And some trees seemed to fall down. \emph{Silently.}

This movement originated from something he couldn't make out clearly yet --- but it was coming closer. He decided to take a step back and choose another tree, now climbing on a branch so he could not be seen from below.  And he was right to do so, for something gigantic was coming. Gigantic in matters of effect, not concerning the real size.

The movement came closer, and some trees nearby fell down to reveal the sight on a small, black, quickly moving figure that threw trees around and cleared a kind of path. Still, there was absolute silence, and he knew that if Simetra hadn't warned him, he would probably have been killed by that small figure down there, for it seemed to lack eyes and was simply going straightforward, destroying the forest in front of him, her, it or whatever it was. As quickly as the figure had appeared, it was gone, and he wanted to climb down to have a look at this new road, but Simetra stopped him.

He knew she wouldn't do so if this wasn't necessary, and thus, he decided to wait. This was a peculiar and dangerous forest, and for he hadn't seen such areas of destruction before, he wondered whether he simply had not come along such a small figure or whether something else would happen. 
He'd soon find out.

After this group of \enquote{road builders} had gone, a ghastly noise shook the earth. The silence that had been there before was now replaced by a noise he could hardly endure, and it felt as if thousands of termites were eating on a piece of wood. 
And this was quite close to what really happened: Blue figures of equal size arrived, eating the trees that had fallen down in a monstrous speed. They left behind a black, somehow moving liquid, that smelled as if\dots{}
No, he couldn't compare this nasty smell to anything he'd ever smelled before. He was glad to see those figures go away, for this meant that he could take his fingers out of his ears again, since the noise must become less brutal.

But another, equally nasty noise would still be there, and the stinking mass was still moving. This liquid was the thing that made the noises, and soon, he saw why: Little trees began to grow in the middle of this mass, and he couldn't help but watch for some minutes until the area of destruction was filled up with trees and branches again.

The black mass was gone, accompanied by the fouly smell and the loud noise. Now, he climbed down, and Simetra didn't stop him. No borders could be made out --- The new patch of forest fit in perfectly. He wondered in which way this destruction and reconstruction was efficient, but of course, this was the explanation why the dead forest was still alive: Those creatures rebuilt it steadily. 
And though he knew they were dangerous, he was happy that they were there, for it meant he wasn't the only living being here --- with Simetra, of course.

And Simetra would now happily point out another direction to him, and he knew that he should advance in that one, for she seemed happy, as if there was a patch of green far, far away\dots{}
