\chapter{Crossing the Great Water}
\label{cha:crossing-great-water}
Absolute silence.

Still, Simetra was with him, and from time to time, she beat her wings and rose up high in the air to try to make out anything that was different from that monotonous forest. And each time, she had returned telling him that nothing was changing, but that things looked the same in every direction. Finally, she just shook her head imitating the gesture humans used to tell someone else that something was wrong or not working out correctly.

Indeed, she had adopted some human traits when that pieces of dust had touched her, and she seemed to have become an even more important part of his life. 
But slowly, both of them felt that a wind was rising: First, it seemed as if the wood was breathing, but then, they could make out a direction, and they were advancing exactly that way. Though the leaves were moving now, silence was still all around.

He decided to walk more quickly, and an hour or so later, Simetra told him that there was a sea in that direction. A grey, nearly black, dead liquid filled this sea, and Simetra added that she could not make out the end of it for it stretched to the horizon --- as far as she could see, almost like an ocean. 

He decided to take a rest right here, for it would probably take him another hour or so to reach this new obstacle. At least, something was happening --- the monotonous forest would end somewhere. 
But where had the clearing gone? 
Had it crossed the sea? Did it change direction along the way? Or had the fairy simply taken the magic away, and tried to escape by flying over that ocean? 
He'd never seen an ocean. He just knew that it was a big, gigantic amount of water a human being could not cross so easily. In fact, he'd only read that this was possible, but he'd never found out about a way to do it. 
And probably, this ocean wasn't even filled with water. But he doubted one could walk on such a grey liquid, and Simetra told him that storms and strong winds were triggering off high waves that made it even hard for her to fly over it, for the wind would become even stronger.

But he simply had to do it. 
He had to find out what was happening here. 
For now, he sat down and unpacked another piece of bread. 
When he wanted to get his flask out of his backpack, the leather pouch that contained the dust fell on the ground. Simetra told him for he hadn't noticed; but some particles of this strange, magic dust had already escaped the pouch and touched the dead earth.

And a small, green plant began to grow. He quickly grabbed the pouch so he would not lose any more of these magic particles, this memory of the fairy; And then, nuts had grown on the plant, eagerly awaiting the moment they would be taken off. 
He took one of them, and as soon as his fingers touched it, a voice in his mind told him:
\begin{quote}
Use the dust of fairies wisely ---\\
it can save your life, and help you to continue your voyage.
\end{quote}
He dropped this nut in his lap, and touched another one; another voice emerged from nowhere:
\begin{quote}
Don't ask for more ---\\
this is all that is to be said for now.
\end{quote}
He laid this nut to the other one in his lap, and those two became darker --- the others seemed to be still green, and glowed a bit,
but this could just be an invention of his mind for everything else around here seemed to be without colour.

However, he decided to touch the other nuts with a piece of cloth before he put them in his bag, for he wanted to take these nutritious counselours with him without using up their energy.
It seemed to work, for their glow remained and they stayed green. The two he'd taken off --- He felt they had to be cracked, for he'd need to find out whether they were really edible.
He took the two stones that were lying below the tree (\emph{he couldn't recall having seen them before}) and cracked the first one carefully.
The shell could be opened quite easily, and the small and light stones found their place in his backpack together with the other, already \enquote{used} nut.

Simetra hopped on his leg and analysed the ingredients of the just cracked nut with her beak; Finally, she tasted a small piece of it and seemed satisfied. Though she could speak, he didn't need to listen to her saying that everything was fine (though she said so); And so, he finally also took a bite.
The small and tiny bit of this nut suddenly seemed to grow in his mouth and filled it completely, but leaving enough room to chew comfortably. It was a wonderful, refreshing taste and he didn't become thirsty ---
in fact, his thirst vanished, accompanied by his hunger. 

He was satisfied and satiated, and so was Simetra. The remaining pieces of the nut found their place in another small pouch, but he wouldn't need these in the next hours. 
Now, he had to make his way to the sea, and he felt strong enough to face everything that would come. 
Soon, the wind became stronger and very cold, but he was indifferent to that change, and so was Simetra: The ingredients of the nut seemed to protect them against some of those obstacles. Half an hour later, he reached the ocean. 
And it really was the way Simetra had described: A grey, dead mass of liquid, smelling a bit like the black mass that had been the strange dung that made this dead wood grow. He took a branch from the ground and touched the water with it, and as he drew it back, the part of the branch that had touched the liquid was gone.

It seemed to have been cut off perfectly --- as if the water had done so. Certainly, this was no water, or at least, not only water; and it wasn't only dead, but could annihilate. 
He remembered what the nut had 'said': The dust could save his life, and it could help him to go on. But did this mean that he was protected against the effects of that liquid? He doubted this to be true, but he had to find out. His fingernails were quite long, as he'd never had to think about anybody showing interest in him in that village he'd come from --- and sometimes, long fingernails were useful. One of that 'sometimes' was now. He was lucky that the waves didn't come as close as he'd expected, because they seemed to stop just one metre before they'd reach the forest, as if there was some secret contract of fear between those two landscapes. Thus, he could give it a try. Slowly, his finger approached the surface, and as soon as his nail touched the liquid, a shot of pain raced through his finger, his hand, his body. In a reaction of reflex, he drew his hand back and fell on the ground behind him. Some twigs cracked, and he quickly had a look at his finger: Nothing seemed to be wrong, though. Even the nail wasn't hurt; but he could still recall this killing pain, and he knew that this was the wrong way to cross the ocean.

He stood up and took a step back, sat down again and opened his bag another time. Now, he took his time to count the nuts: There were eleven of them left. 
But he had to take one of them now. He waited for another moment: The \enquote{dust of fairies} would save him. Yes! This was the solution. Not the nut alone could help him to cross that sea, but the dust itself must be used. But he didn't know where and how to apply it\dots

Simetra rose into the air, and tried to make her way against that storm. The power the nut had given her seemed to help, for she seemed to be able to advance. Quickly, she returned to the ground to tell him about her success\dots
When he saw Simetra coming down, he realized he'd found the solution. He'd have to fly! And when she touched the ground next to him and said that she could probably make it now over the ocean, he took a piece of cloth and carefully grabbed some of those wonderful particles. He realized he'd have to take his shirt off. Simetra was watching curiously as he put the dust back into the pouch and dropped his shirt into the backpack after having taken it off; then, he took the piece of cloth again, grabbed some particles of the dust and carefully let them trickle on his back, thinking about lifting himself into the air, and being reminded of the fairy. 
It worked.

Simetra shrieked, as two translucent wings were growing on his back. 
A warm feeling went through him, and he closed the pouch carefully so as not to lose one of these particles. He knew he'd found the right solution, and Simetra realized what he was up to before even one word had been spoken. 

Before he could wonder how those wings were working, they unfolded themselves and he rose high in the air; and there was another voice, that asked him where he wanted to go, but his mind was still filled by that image of the clearing, as it had been since he'd lost it --- and her.

Thus, he shot forward, and Simetra could barely follow him. The wind around him and the feeling of that killing sea below was thrilling him --- and he imagined that Simetra must feel like this all the time. He wondered how long the journey would take, but he enjoyed it; slowly, the sight of the forest behind was disappearing, and he wondered where they were going, if they were really going somewhere\dots

An hour later, there was nothing but that water all below, and it went up to the horizon. The wind was gone, however, and he imagined what would happen if this sea was infinite, and if he was to fly like this for the rest of his life. Simetra had already found a place on his back some time before, as she was tired to fly at such a speed. No clouds were to be seen, and nothing seemed to be alive around here except the two of them.

Suddenly, the semblance of a piece of land appeared in front of them; first, it just looked like an island, then, it grew steadily until he could see --- that it was a landscape full of dead, grey trees. Had they finally just flew in a circle? Simetra knew what he must be thinking, and she told him they weren't; they had not changed the direction at any time, and she knew that for sure. She was a bird, and her orientation could not be doubted, but nevertheless, the landscape looked so similar that this was hard to believe.

Simetra left his back again, and he slowly began to descend; when he was close to the top of the trees, he suddenly felt extremely tired as if all energy had been drained from him. In the last moments above the tops of the trees, he thought he could make out a patch of green some hundred metres away, but he wasn't sure, for he simply crashed through the treetops fractions of a second later. The last thing he heard was a big and loud \enquote{Thump!} when his body was smashed against one of the trees, and then everything went dark. 
