y\chapter{Thought Communication}
\label{cha:thought-communication}
The night went by silently and without further incidents. Through the slightly transparent sphere of feathers, Simetra saw the sun rising atop the crowns of the trees, marking the beginning of a new day. The forest felt significantly more dangerous with the additional knowledge she had gained last night, and she felt it was emanating an aura of death even though it looked bizarrely natural.

The fairy, Aurora, woke up first. After a short moment of confusion before she remembered the strange situation they were in, she stretched herself, slowly stood up, and unfolded her wings, taking care to be silent such as not to wake Apollo. After rubbing her eyes, she faced Simetra, greeting her watchful eye with a smile. Simetra herself also took this as a trigger to wake up completely, blinking both her eyes and stretching out her wings, moving her claws and shifting her weight from one to the other, until she was finally fully awake. \enquote{Good morning}, she whispered, and the fairy did not respond with words, but reacted by moving her index finger to her mouth, pointing at Apollo with the other hand. Calmly, she took her left hand and approached Simetra, finally touching the back of her head. Simetra let it happen --- they were beyond any aggression and initial fear. Then, Simetra could hear a voice whispering in her head: \enquote{Good morning, Simetra}.

Communication by thought? With a surprised look in her eyes, Simetra focused on Aurora, trying to respond. All she could muster was a surprised \enquote{How?}, but apparently that went through, since Aurora responded: \enquote{We have been linked by our magic and by touch, so we can communicate without speech. Let me try to remove my hand, the link should remain.}

And so she did, and while the voice was slightly more silent, all it needed was a bit more focus by Simetra: \enquote{Can you still hear me?}

\enquote{I can. I think it will take me some time to get used to this, it still needs quite some focus on my end, but the more we talk, the easier and more natural this seems to become}, Simetra responded.

\enquote{Just to clarify}, continued Aurora, \enquote{I can not listen in on your thoughts, nor can you listen in to what I am thinking. Our voices only reach each other when we address one another. Physical distance still plays a role, especially if other magic interferes, but we can talk like this without fear of being listened to, and as soon as you are used to it, it will be really effortless.}

\enquote{This is really useful}, Simetra responded. \enquote{I have so many questions I want to ask, but it would be best if my friend would be there to join us, since I am sure he is equally puzzled about this strangely absurd chain of events. So while it pains me to wait longer, it's probably best if I tell you a bit about the two of us first. I guess this forest is large enough to keep us up here for quite some time, right?}

\enquote{Indeed, it is. While it is hard to pinpoint our location just by looking at this endless ocean of trees, we fairies have an independent sense of location, and I can tell you for sure it will be many hours before the landscape changes.}

\enquote{This is quite reassuring. Well, then I will try my best to describe our story\dots I am not sure where to start --- what is my first memory? I remember Apollo has told me that I have come into his family in the same night he was born. This is now 18 years ago, and we have lived in the same village ever since. You've met us close to this village, we have left there not long before meeting you.

  The village has not been too friendly to us. In the first eight years, Apollo's parents have been there to protect us and raise him, until ten years ago, a tragic calamity has hit us. Both of them were killed, exactly eight years after his birth. I could not do anything apart from hiding him under a blanket, and I don't know whether this really protected him or it was a stroke of luck he was not found by the attackers. The villagers have taken care of us since then, for ten years, apparently following an agreement made in advance by his parents, until we had to leave when Apollo turned 18 years old.}

\enquote{Who did attack you?}

\enquote{At that time, I still lacked my current sense of self-awareness, and lived by instinct and emotion alone. The attackers looked like humans, but I could feel a powerful and evil aura when they approached, and I could feel the sudden haste when Apollo's parents seemed to prepare for something. They must have realized what was about to happen, and they left a message for him, and had a forceful discussion --- or rather, a fight --- with the villagers. It was a day full of hurry and panic, and the emotions burnt themselves deep into my soul. In the end, they calmed down, and awaited the arrival of the attackers, seemingly accepting their fate, or unable to change it. It was over so fast, that I hardly realized what was going on, and only with the human self-awareness I gained the last days, I finally realize they were indeed preparing for this, planning for Apollo to be kept safe in the next ten years.}

Simetra stopped. She looked down, closed her eyes, and needed some time to calmly breathe in and out. All the happenings on that day were still vivid in her memory, and she was still adapting to her new human features, which changed the way she could interpret and understand all those past memories. More humanity did not ease her life in this regard, it only increased the level of tragedy contained in these memories by giving some actions more context and meaning.

\enquote{I am sorry to have made you remember this}, Aurora said full of compassion. \enquote{While it will not help against the deeply rooted pain, there is a legend passed down among the fairies, and it is what guided me here --- it is about both of you, I believe. But we should wait until Apollo is up before I continue.}

Aurora decided the best way to calm down and regain their energies would be to have a bit of breakfast. She opened a pouch on her belt, and extracted two juicy looking, light green fruits. They were small and spherical, similar to grapes. She popped one into her mouth, and started chewing, offering the other one to Simetra, who gladly accepted. As expected, these fruits also bore magic inside them --- while chewing, they started to fill the mouth completely, and not only did a strong, fruity taste spread itself, but they were also nourishing and quenched the thirst at the same time. A single fruit was sufficient to saturate them, since they just could keep chewing for a few minutes and the fruit did not vanish, until they finally instinctively gulped the remaining pieces down to empty their mouths.

\enquote{These fruits are from my hometown}, Aurora explained. \enquote{Places in which magic naturally dwells have become rare these days, and so are the places we fairies can call our homes. But it is best if I continue with my story when Apollo is with us, I think he should wake up any moment now, given the tasty smell of these fruits.} Aurora smiled, and indeed, as Simetra glanced towards her friend, she saw his nose twitching a bit, and seconds later, he was slowly waking up, blinking his eyes and yawning heartily. Interestingly, he was not confused by the strange place he woke up in, but immediately turned around and greeted his companions.

\enquote{Good morning}, he started off, noticing the remaining colourful stains from the fruits on Aurora's hands. \enquote{I see you are both already awake and having breakfast, mind if I join in?}
With this casual starter, Aurora produced another one of the grapes, and passed it to him. Not surprised at all, Apollo started to chew and enjoy the taste. Simetra could not resist the urge to try out the thought communication technique with him, and without further ado, she concentrated on Apollo and thought: \enquote{They are quite tasty, aren't they?}

Apollo coughed, and finally looked a bit irritated as he turned towards her. \enquote{How\dots?}, he stammered, and looking at Simetra, he thought: \enquote{How long have I been asleep? What has happened to Simetra?}

\enquote{Actually, not that much longer than we have slept, I must say}, Simetra responded via silent thoughts. Slightly shocked, Apollo thought: \enquote{Can you read\dots?} \enquote{No, of course not, but you are quite fast picking up this technique and responding to me. I can only hear your thoughts because you focused on me and have actually been close to blurting out what you thought just now.}
Apollo calmed down. \enquote{This is rather\dots unusual, but somehow convenient}, he continued, also addressing Aurora. \enquote{It's astonishing how fast you've got the hang of this, but I should have expected this after all that happened}, Aurora responded to both of them in her thoughts --- it was as if a silent conference had been established between them. A large, owl-like bird, carrying human traits and magic in it, a slender, beautiful fairy with translucent wings, fair skin, yellow undulating hair and giving off a bright, greenish glow, and finally Apollo, an 18 year old human being brimming with strong self confidence, all assembled on a wooden sign racing through the skies, communicating in silence. Finally, it was time to discuss the pressing questions and find out where they were headed, both physically and concerning their future path.
