\chapter{Simetra's Memories}
\label{cha:simetras-memories}
Apollo was silently digging in the soup. Astonishingly, it seemed the soup had become warm of its own accord --- either the plates were imbued with magic, or the chalice had actually warmed the soup while it was poured out. He did not give it much thought and even though he appreciated the astonishingly fresh flavour of the vegetables which were part of the soup, it only caused a slight smile to play around his lips. But his head was elsewhere, trying to digest the story. All he remembered from the past was that Simetra was with him since the day he was born and that she protected him; but actually, he had never learned much about his parents. While he spent the first happy years of his life with them and their parental warmth and love was still present in his heart and mind, he actually never learned about any of their jobs, tasks, dreams or experiences in life. All he knew about them was that they were his parents, and cared for him. 

Apollo shortly stopped moving the spoon to his mouth and stared into the air in front of him, slightly shocked. Only now, he realized that he never actually tried to ask them about their background, their history. Could he be blamed for that? Thinking further, he started to wonder: If he was supposed to match up with the person in the legend, shouldn't he know about his sister? Tracing back his memories, he realized that while there were emotions left from before he'd reached the age of eight years and while he surely remembered his parents and the tragic night, his mind was mostly blank concerning the years before. He'd never wondered about that since he had been with Simetra, and humans don't recall many memories from the very first years of their lives when they still don't have a well-defined sense of self just yet. But was this the only reason?

He shook his head hard to escape the frozen state he was in and blinked his eyes. Only then, after refocusing, he realized that he was not staring into thin air anymore; the fairy's face had entered his line of sight. Aurora must have realized he was frozen up and stared at him calmly, with a slight, friendly smile on her lips, not saying anything. He blushed as she was quite close, and he realized only now that she was actually pretty: her face was tiny, with slightly puffed out cheeks, and her skin was pale apart from a few freckles around her snub nose. Her green eyes sparkled at him, betraying the young age her body seemed to have by emanating an intelligence and wisdom of many years. They matched the light green colour of her slightly transparent dress. Apart from the pointed ears and the translucent wings on her back she looked like a human in her teens, maybe a few years younger than him. Her blonde, wavy hair was slightly tousled as if dishevelled by an unseen wind, and it took Apollo some effort to compose himself again and focus back on eating. Aurora had given him a bit more space after she saw that he blushed, and a somewhat playful smirk remained on her face afterwards.

\fancybreaker{}

It was hard for Simetra to deal with the memories which had suddenly started to rush into her mind. As if a dam broke loose, her mind went back in time while eating --- the legend had brought back her memories from the first years with Apollo, when she herself was still a young bird, unaware of what the happenings in her surroundings meant. But she was aware now, and the memories all came back, almost making her faint from this sudden pressure. She was glad the soup was placed in front of her, since it allowed her to follow her instinctual, mechanical motions to eat. This kept her from fainting, at least. But inside, thoughts were swirling, memories taking new shapes, as if a seal had come undone all of a sudden. She could not remember speech from that time, but there was a scene quite like the one in the legend buried in her memories which now suddenly got meaning. The girl which must be Apollo's sister was there, and she remembered they all lived in a different place, flooded with luxury. The one day clearly matching the day from the legend was when they had moved, and when the girl had left them. At the time, she did not interpret human interaction, but Simetra still felt the loss and tragedy in the hearts and souls of the persons around her --- and she also carried the memory of that painful event in her heart. Only now, it all got meaning. With this new understanding, a pang of deep pain from the past shot up inside her.

She had to slowly sort out these thoughts, and reorganize this memory to rebuild a coherent line of events. The turmoil in her brain gave her a headache, but after sorting this out, she knew she would have to tell this story to Aurora, unless Apollo did it. But maybe his memories had been sealed until now, too?

\fancybreaker{}

Aurora calmly ate the soup she had provided to all of them. Carefully, she watched Apollo and Simetra. They were reacting in quite different ways; while Apollo seemed calm first, he suddenly froze up, as if time had stood still for him. Curiously, Aurora bent over, staring into his eyes, which seemed to focus into thin air. He must have been so absorbed in his thoughts that he did not even notice her. She took the chance to muster his face, and she found he had dark blue eyes, with small specks of brown, as if his irises could not decide which colour to settle on. His face was slightly stubby, probably from the last days of travelling, and it bore sincere, determined features, even though his eyes were quite absent-minded at the moment. She curiously tried to stare deep in his eyes, into her own reflection, as if to draw out his thoughts and history. Then, he suddenly refocused and blushed, and she drew her face back. While he was the protagonist here, he was still a human man, and easy to irritate. She smiled in face of this youthful demeanour. 

She watched Simetra next, while continuing to eat silently. The bird seemed to endure a strange pain, mechanically eating all the while, as if to calm herself down. She must be remembering something, digesting the things which had happened before she became aware of herself. If she were humanly shaped, she'd probably be sweating, but as she was a bird, all Aurora could make out were her eyes moving restlessly from one place to another, betraying her inner turmoil even though she was calmly eating the soup.

Clearly, both of them were in a very different situation, probably for the first time in their lives. Simetra seemed to remember something, while Apollo was incapable of thinking straight. His feelings might have sealed away his past, but as in the legend told among the fairies, the familiar would be the trigger to draw them out. 

\fancybreaker{}

Slowly, all three of them were satiated, but they were still lost in their individual thoughts. Simetra's eyes lost a bit of their restlessness as she seemed to calm down, and Apollo was silent and composed, but had a questioning look on his face.

\enquote{It seems you have a lot of questions on your mind}, started Aurora, looking Apollo straight in the eyes. He seemed to flinch a bit, but then nodded, averting his eyes ever so slightly. \enquote{What is the earliest memory you can grasp?}

Apollo focused again, looking at Aurora. \enquote{My memories are mostly blank before the time my parents died}, he said. \enquote{While I can still remember their warmth from before that, and feel their love, everything else seems completely clouded.}

Simetra turned her head, looking at Apollo in astonishment. \enquote{The legend made me remember the painful day when your sister vanished}, she began with a trembling voice. Apollo turned his head, focusing on his companion. \enquote{The legend matches my memories so much it is frightening. Only now I manage to interpret the images kept in my mind from before I gained my sense of humanity.}

Apollo touched her feathers, trying to calm her down. However, at the same time, he glanced at her with sparkling, interested eyes. They had spent their lives together, but these memories were apparently locked away from him, probably sealed by a lock of painful loss. He feared what would come, but he had to proceed, and he would have to ask Simetra to tell the tale.

Endlessly long minutes passed by, while Apollo kept stroking Simetra's feathers, trying to calm her down. He did not need to say anything, for Simetra knew what he was going to ask. After she had recollected her memories and brought them in order, she slowly calmed down again. To ease the stressful situation, Aurora slowly put away the plates. As she lifted them, they shrank back to their former small size. At the same time, they seemed to clean themselves. Next, she took the spoons, which also had been magically cleansed, and put them back into the bag at her belt. She left the table in place, putting her elbows on the wooden desk and resting her head in her hands. Without specific pressure, but rather with a calm and collected gate, she looked at Simetra until she was finally ready.

\fancybreaker{}

We have lived in a big estate when you were born, Apollo. Your parents bought me on the same day you were born, and I have since watched over you as a companion, a familiar. We were a happy family: Your parents, you and me. At the time, I was not aware of human speech, but from the images which came back into my mind, I can assume your parents had some ruling power in the region we lived in. They had servants, which they treated like friends, and regular feasts were held which many of the people in that region visited. It seems your parents did not segregate their people by status or rank, and it was a very peaceful atmosphere without any visible oppression or crime.

One year after you were born, your mother was pregnant again, and your sister joined our little family. There was a big celebration, and the peaceful times continued after. Our estate was a big manor house, with a large garden, and I remember all to well how we played there and in the nearby forest. Once your sister was able to walk, even though she was too young to leave the house alone, she would sometimes sneak away and join us, playing hide and seek and other games close to the mansion. Still, most of the time your sister had to stay at home. I did not fully grasp the reason, but her skin was very white, as if made from porcelain, and would at times become red when she stayed outside for too long. She must have had some kind of strong sensitivity to the sunlight, and it seemed to cause her pain to stay outside for too long, especially in summer. However, these were happy days, and sometimes, other children from the nearby town would join us, and they played with us as fellow children, as equal friends. These were joyful days, and there is a lot of warmth from these times filling my memory. I remember these emotions well, even though I can not recall the words I heard at that time, and can not even recall your sister's name.

Your parents were very busy with their ruling duties, but they still spent all of their remaining time with both of you. It was a youth without flaws, as if taken from a fairy tale, or a beautiful dream. As in the legend, it might have been to good to be true, or at least, it seemed to be too peaceful to stay this way forever.

Now that I am slowly grasping humanity, I feel like there ought not be light without shadows. And sure enough, from time to time, I could see some of the villagers becoming lethargic. Drowned by the peaceful times, an escapist drive to leave the stable environment and roam the nearby lands started to dwell in the youngsters. Those who joined us in our hide and seek games started to recite stories of adventure from long ago, of warriors from a forgotten time fighting against powerful foes. At first playful, I could slowly make out a fire burning within their eyes, as they did not only recite these stories in awe, but also started to dream about themselves becoming such heroes. They pointed at pictures in the books they brought, every time more eagerly pointing at heroes and beasts of ancient times. 

At the same time, your parents became ever more busy. I could not follow what was going on in detail, but it seems there was a conflict with a neighbouring country, and it took them quite some effort over several years to convince them to enter a peace treaty. It seems this conflict had been sparked by a personal attack: The inhabitants of that neighbouring country did look different, with slightly darker toned skin, since it was a country with endlessly long summers and sunshine and desert-like regions. I remember that wen I saw first pictures of these inhabitants, some villagers made comments about them being of different origin, even blaming them as enemies of humanity due to their looks alone. Apparently, there was some incident which sparked this conflict, and it took a long effort to spread more tolerance among the people in our land. It is astonishing how much I can infer from the pictures, gestures and facial expressions alone, now that my vivid memories are all revived.

Still, your parents seemed to have succeeded at that, after years of effort. Trade relations had been established, and our neighbours started to come as regular visitors into our country. However, it seemed like some of the hostility had entered the minds of our people. Some of the heroic stories told by the children had been twisted, they now talked about dark-skinned foes, who were killed by bright, shining heroes, sometimes even saving princesses held captive by those lords of darkness. While I could not understand speech, I could take all this from the images drawn in books and being embedded in the emotions the children exuded. As you may imagine by now, the fact that your sister had very white skin and rarely left the manor made some people worship her as the ideal human being. Your sister, in response to some of the children looking at her with glorification shimmering in their eyes, stayed at home even more, only increasing this effect. 

It must have been this small twist, which continued to seep into the minds of the people which was the trigger. Along with the escapism bred by the peacefulness, it led to the following events. They unfolded only a few years later. As the legend made me recall, it was on your seventh birthday, marked by a large festive event. All around the estate, people had been busily preparing for the day, and when the day finally arrived, your parents managed to take time off from their duties to spend time with their family. A large tent had been put up next to the estate, in the garden right behind it, and a stage with musicians had been built inside. Large desks with a free buffet lined the tent and everyone was free to come and join the festivities. The family was seated close to the stage and many people arrived to greet and congratulate us. For me and I believe also for you, the necessary formalities were mostly boring and exhausting, but there was still a calm and controlled atmosphere. Guards were there of course, too, but they were sparse, and actually seemed in a festive mood, too. Nobody expected any malicious actions to take place.

Hence, what happened then caught us all by surprise. A loud, roaring sound backed by great power could be heard from afar. All those present in the garden were irritated by the noise and their heads shot up, searching for the source. Apparently, the sound was coming from quite some distance away, but not from the ground; it came from up above. None of the people present had ever heard such a powerful roar, but they all had an ominous feeling and were reminded of the stories from long ago: This was like the sound of a dragon, a creature which according to history once roamed the skies, but had not been seen for ages. How did a dragon find it's way here on this day? Were these creatures even still roaming this world? 

It did not take long for chaos to unfold. After an eerie silence, a few moments later a single person mumbled the word \enquote{dragon}, which all of them were thinking but did not dare to pronounce. The panic began right after. A dragon, in this day and age, a creature which could bring calamity to whole countries? Cries of fear filled the tent, tables were overturned, and even the tent itself began to tilt as people pushed with all their might to escape from the area. Amidst all that terror, energetic youngsters in shiny armour suddenly appeared. They invaded the stage, which the musicians had already fled, and as they drew their swords and held up their shields high into the air, they let loose a battle cry which apparently was supposed to calm the people down. This failed miserably, as another roar from the ancient dragon could be heard just a moment later, much closer by. A gust of wind made the tent waver, and suddenly, a golden light could be seen through the white fabric of the tent, which grew in size by the second.

Your sister and your parents were already being evacuated and on their way to safety, but you still stood there, frozen in place. I kept you company and tried to alert you by shrieking, but you seemed to be completely spaced out. As the light grew brighter and while the soldiers were busy evacuating everybody, several hooded figures appeared behind the buffet tables. They started to chant in unison, and a protective barrier seemed to emerge right on top of us. The youngster warriors assembled themselves right in the middle of it, and it only took a few seconds until the fire breath of the dragon arrived. The fabric of the tent lighted up like paper and vanished in an instant and the breath pushed against the barrier with forceful might. The young warriors lifted up their shields and went into a protective stance, while you and I were still frozen in place. The heat propagated through the barrier and got almost unbearable. It was as if time stood still; the cries of the people pushing to escape the tent had quieted down, as the tent was slowly emptying, and only the gushing of the fiery dragon breath could be heard, along with the continuous chants from the hooded figures.

As the soldiers serving your parents realized you were still frozen in place, two of them came rushing towards you. At the same time, a slightly crackling sound could be heard from above, as the barrier was slowly giving way with a groaning noise. As it finally shattered with a sound similar to a mirror exploding into thousands of pieces, a soldier pushed you to the ground and put himself above you, lifting up his shield. I quickly took protection behind the shield, too, as the second soldier also lifted his shield and braced himself for impact.

The devastating fire hit the shields both of the soldiers and the youngsters at full force. It seemed the shields of the youngsters were covered in some kind of protective resin or imbued with magic as they seemed to be fully ignorant of the fire. However, they could barely withstand the force of the breath pushing against them. I could hear loud cries from the hooded figures at the same time, and they fell to the ground, burning to a crisp. Their magic was broken, and they could not offer any resistance against the powerful attack anymore.

The soldiers protecting you were powerful enough to endure the force, but their shields could not take the heat and began to melt. Slowly, but surely, they were exposed to the fire themselves. Their armour shielded us, but a painful moan could be heard from the trained soldiers as the temperature rose. When the fiery breath finally came to an end, both soldiers were lying on top of us, and the stench of burnt flesh was unbearable. They would never move again.

Finally, the pain from light burns brought you to your senses, and you extracted yourself from below the two bodies. While we were running towards the manor house to search protection, I turned my head around and saw the youngster warriors mostly unfazed. While it seemed their strength was exhausted from withstanding the powerful breath, they appeared to be without physical injuries. As they saw the remnants of their hooded friends, though, terror entered their eyes. The dragon was circling above, apparently watching the situation below. With the tent and magicians removed, it seemed like it did not regard the small humans below as a potential danger anymore. As a predator, it must have been sensing the fear in the hearts of the young warriors down below, too, and the beast seemed to calm down slightly.

It was this exact moment when a small explosion could be heard from the forest and smoke started to rise. The dragon was alert and turned to look in the direction of the noise, expecting a long-distance attack to come. You also stopped to run and turned; While your focus was in this direction, I turned around to face the manor house, trying to nudge you to continue fleeing. It was only due to this change of viewpoint that I saw a small, almost invisible sphere flying towards the dragon from the manor. As it approached, it quickly unfolded into transparent wire, which formed a net. The dragon was too slow to react and was caught up in the net immediately. It seems the net was magically enhanced, as it slowly enclosed the dragon, who was twisting inside more and more, until it finally could not move its wings anymore, and started to tumble towards the ground, letting out a powerful and angry roar.

But such an intelligent and proud beast of the past would not give up so easily. With sharp claws it attempted to break the net, while at the same time recharging its breath to attack with another gust of fire. The hard scales of the dragon were unaffected by the cutting magic the net must have applied when it wrapped itself around tighter and tighter, but at the same time, the claws were ineffective against the net. The dragon kept falling down until it finally opened its jaw wide to prepare for another attack. Tumbling down, it was not really possible for the powerful hunter to aim at a specific target, so while it would likely hit the forest most of the time, all the unprotected humans who had attended the feast and were now on the run were at risk.

You were watching in shock, stupefied and helpless, and unable to escape to safety. I tried to nudge you, pointing towards our house, but you didn't respond. At the same time, most of the young warriors seemed to have heartened up and they started to run towards the place where the dragon would likely hit the ground. Also, the flow of people on the roads leading through the village started to change. A procession of people, carrying a palanquin in the centre of the crowd, slowly started to approach the scene. They were surrounded by more young warriors, mostly children. Even though they were clad in armour, I could recognize some of them who played with us during the happy days before. Among them, there were also some carrying bows and more hooded figures who started to chant. Soon, they were enclosed in a protective shield which moved along with them. It was a strange sight, and a mysterious atmosphere. The soothing noise of the chanting child magicians was soon broken by the battle cries of the archers, who started to attack the dragon.

Finally, you seemed to realize the impending danger right as the dragon was almost ready to unleash its breath. There was no time to flee to the manor house anymore, but there was a pair of large boulders nearby, originally placed there as decoration next to the path leading to the house. Thinking that these should withstand the fire attack, we hid ourselves behind the closest one, and peeked around the boulder to continue watching the scene as it was unfolding. Not a second too late, as the dragon's breath started to scorch the earth not too far from our hiding place. Only as it got closer uncontrollably and singed a nearby bush, the full power became apparent. But it was not only the wood and bushed which were burning, as the stench of burnt flesh began to fill the air. Not all people and animals who had fled were so lucky to find a safe hiding place and it seemed like the air was converted to a burning inferno.

It was almost unbearable, but as the fiery breath seemed to catch more distance, we courageously spied around the corner of the boulder. I could feel you were slightly shivering as we could see the dragon's breath hitting the procession of people carrying the palanquin. Luckily, the gush of fire continued to move and the shield was able to hold it off long enough. Mostly unfazed, the protected people kept walking and the archers tried to attack the falling, tumbling dragon with arrows which seemed to be imbued with magic. I remember they were glowing in a bright blue and I had the impression they were flowing towards the dragon like a stream of water, travelling as if carried by invisible waves instead of flying in a straight path, but still hitting their target well. These seemed to be effective against the fiery beast, as it started to scream as the stream of arrows reached the scales. It seems the arrows were slowly\dots seeping in, maybe this is the right way to put it. They carefully made their way through the tiny joints between the scales as if following a natural flow and then got stuck in the dragon's body.

As the dragon tried to unleash its breath again, it seemed the fire was forming much slower. The magic imbued in the arrows must have been sealing the dragon's power and, surely enough, more and more arrows rained down upon the majestic beast until it finally squealed, interrupting its magic attack. The net, which seemed to be shrinking ever so slowly, finally caught the dragon so tightly that it was unable to even move a muscle. In these few moments, the fight was essentially over, and the young warriors who had been disheartened before now finally reached the dragon. With a battle cry of their own, they drew their swords. A painful slaughter began.

Still feeling unsafe, the two of us struggled to slowly exit the safety of the boulder. At the same time, the procession had come to a halt and they set down the palanquin at their centre. Those who had carried the palanquin seemed to start to fiddle with the drapery which was hiding whatever or whoever was within, and they were actually slowly lifting the protective curtains. A white figure with ideal proportions, made from the most exquisite marble available in the country, was slowly unveiled. She looked so much like her that both of us gasped in shock.

\fancybreaker{}

\enquote{Diana}, Apollo interrupted in a loud, sobbing voice. \enquote{Her name was Diana!}

Aurora and Simetra, who had been absorbed in the visuals the recited tale created in their minds, were abruptly brought back to reality. They turned to face Apollo, who was holding his head in his hands with an expression of shock, silently shivering all over and crying with empty, rigidly staring eyes, slightly bloodshot from intense emotion. But before Aurora could even open her mouth to address him a sudden rumble went through their wooden means of transportation as it came to an immediate halt. In the blink of an eye, the three of them started to fall down from midair, at breakneck speed.
