\chapter{Separated}
\label{cha:separated}
Apollo had lost control. As his memories came flooding back at him, his instinctual magic had broken down and the magic of flight he subconsciously controlled even when they had been sleeping evaporated into thin air. There was a throbbing pain in his head as the emotions from the past came gushing out of the locked area they had been dwelling within until now. He did not even realize what was going on around him, nor did he notice right away that he was falling. Emotions locked away for a decade came back to him with excruciating pain.

Diana was all his mind would focus on. Memories of his sister, his childhood, came back all of a sudden. Her fair skin, her porcelain-like beauty, her sensitivity to sunlight; all of those details he'd heard in the story he could now confirm with his memory. But there was so much more: her smile, her laugh, her scent, the regal aura she exuded at all times. It all came back, together with the pain of loss and infinite sorrow. He knew the continuation of the story, but could still not accept it.

\froufrou{}

\enquote{Simetra, quick!}

Aurora regained her senses first, and on instinct started to unfold and flap her translucent wings. It took Simetra a bit longer, as it seemed she needed time to switch back from her storytelling to the realization that she was still a bird, as she had been her whole life. As Aurora dashed down and held on to the sign they had just recently been riding on, Simetra quickly realized her proposal must be to try and slow down their fall. Simetra followed her example, and wrapped her claws around the signpost, fluttering wildly to try to help keep the wooden sign from falling. Meanwhile, Apollo, in a streak of incredible luck, was still seated on their old means of transport, as if nothing had happened. Only then, Simetra realized the feathery shield around their means of transportation was still there. It must have kept the wooden boards in balance, and prevented Apollo from falling off.

As Aurora and Simetra struggled to slow down the falling sign with Apollo on top, Aurora managed to take a glance at their surroundings. The sun was shining up above and if not for the deadly forest below it would have been a wonderful day. The sunlight was refracted in her translucent wings and the colours of the rainbow could be seen on the wooden planks right in front of her, playfully moving about. As Apollo was still beside himself, Simetra took in the beautiful sight, and as if fuelled by the colours, she doubled her efforts to keep them floating over the trees. Aurora quickly moved her head around, as if searching for a way out after their long flight through the endless sea of trees, her blonde her swaying from side to side.

Seconds as long as an eternity went by, and Simetra was close to passing out from the effort. Finally, Aurora reached out her left hand, in a fast, but very controlled movement. She squinted, and grabbed onto something. To an observer, it seemed as if she was trying to take hold of thin air, but her movements were so careful as if she was trying to softly touch the web of a spider, neither breaking it nor getting caught in it. Aurora seemed slightly surprised and taken aback for a moment, but quickly calmed herself and continued. More seconds went by, and while Simetra was trusting her deeply after the short while they travelled together, she was slowly reaching her limits and began to doubt her own perception: the air started to shimmer close to Aurora's hand, just like it would on a hot summer day near a dark surface. As if a mirage was developing, it seemed the air was opening up, revealing an image of something different, far away. Like watching a faraway scene through a lens, or observing something through the reflection in a calm lake, a slightly transparent and blurry image of a grassy, dark area shimmered in the air. Simetra could only capture a glimpse of it, though, as if a tiny rift had opened in the air and was still unstable.

\enquote{Hold on, we have to overexert ourselves in one last effort!}, Aurora spoke through their link via thoughts. With her last energy, Simetra fluttered as strong as she could, operating by will alone. Aurora let go of the floating sign with her right hand after pulling it up slightly and quickly moved her feet below it to at try to keep it atop the trees. With her second hand free, she reached out into the rift and with coordinated, experienced movements widened it. Simetra watched as time slowed down to a crawl in her mind. She closed her eyes to refocus her last energy on keeping their means of travel in the air. Ever so slowly the rift was widening, but Simetra was unable to continue observing. Her complete mind was focused on moving her wings, up and down, up and down, in a steady rhythm.

\froufrou{}

While Aurora realized time was running out, she had to take a gamble: they could not risk to land here, and recreating a safe place such as the clearing she had used before would not be possible in the limited time they had available. She could not control wood to let it fly, as this was not a natural effect, and the sign was in any case imbued with a strong magic she would not dare to touch. However, she knew they had to take it along, and Apollo would not regain his senses fast enough to stabilize the situation. The only way which came to her mind was to escape via a ley line to a place known to her. This was a risky venture, since she was the only one among them who had experience travelling through strands of highly condensed magic, and it would take her quite some time to prepare their escape route. Time which they did not really have, but there was also no alternative in sight.

She decided to trust in her own power combined with Simetra's strength, and began to search, expanding her perception such that she would see the tiniest movement of magic. The sunlight and prismatic colours which would be projected through her wings would guide her in the search for a flow of magic in the nearby area. She forced herself to stay calm, and the experience of many years helped her to succeed. The ley line was found, and she slowly tapped into it, feeling her way to a place she had visited before. She was shocked, as she learned their location and how close they actually were to the place from which she had begun her travels quite a while ago to meet those two companions: She was close to her hometown.

\froufrou{}

Simetra was on the brink of finally losing consciousness from exhaustion. Her muscles ached, and it felt as if her wings were broken off her body, and only pain remained. Mechanically, she kept beating those wings she could not feel anymore, without any thoughts, just a single, clear focus. Up and down, up and down, like a clockwork, always striving to keep the rhythm going. 

As she drifted towards nothingness, she felt a slight movement of air, pulling her to the side; or did she imagine it? Maybe she was just drifting into unconsciousness, falling deeper and deeper. Finally, everything went dark.

\froufrou{}

Apollo reconnected with reality as his environment changed. He felt like he was dragged away from the painful pangs in his head into a large, powerful stream tugging him along, without any way to fight back. As if somebody had thrown him into a torrential river, all he could do was struggle to stay afloat and follow the current. But what was this strange river he was floating in?

The painful memories got pushed aside. Apollo was struggling to stay alive, swimming. However, the liquid he was in was very much unlike water: while it was certainly fluid, it did not splash, nor was it of a consistent viscosity. The colour seemed somewhat yellowish, but whenever he tried to focus on it or name the colour, it seemed to change slightly, as if the colour could be anything from the colours of the rainbow. It seemed like the liquid did not have a fixed colour, nor was it transparent enough to see more than a few centimetres beneath the surface. When he did not focus, the yellowish tint came back. Looking upwards, he could make out a blue, but somehow blurry sky, as if out of focus. Forward and backward, the stream seemed to continue forever, and the horizon was out of focus again; it was similar for the waterline, which seemed somewhat earthy, but hard to get into focus. Somehow, all this did not look like reality to him. 

Only then, he realized that he could not see the others anymore. What did happen to Simetra and Aurora? How did he end up right here? He started to cry Simetra's and Aurora's names in an attempt to alert them, hoping one of them would suddenly pop out of the stream right behind him. But nothing happened, and his voice was deafened by the somewhat hissing, crackling noise of the liquid flowing all around him. 

Apollo panicked. While he had essentially lived alone for many years, without contact to other humans, he always knew there was a village nearby, and there was Simetra to keep him company. At times, he would have felt lonely, but he'd never been completely isolated from the world around him. However, Apollo now felt as if all other people had been swept away. Nobody, no other creature would respond. No single animal could be heard. The strange, rushing noise was slightly unsettling as he frantically moved his hands, trying to swim against the flow of the stream. The current was too strong to resist, though; trying to go back the way he came would never work.

Apollo tried to calm himself down, and collect his thoughts. As he succeeded, the stream around him became less wild, as if responding to his increased serenity. However, the current did not become less strong or slow down. As Apollo pulled himself together, he realized that he did not feel wet at all: still wearing all of his clothes, the liquid was not seeping in or drenching his clothing, which would otherwise have become so heavy already that he'd have a hard time staying afloat. He decided he needed to collect more information about this place and this liquid to find out what was going on. Swimming against the current would not work. Following the current might be dangerous, though, since he did not know why he arrived here at all and where the stream would take him. Maybe he could try to reach the waterside? But was there anything on the shore? Apollo squinted, trying to make out any structure on the shore. However, the imagery was very evasive, as if it was all a blur. Was this reality, or rather a dream? Reality couldn't look that way, could it? 

He slowly struggled to swim towards the waterside. While doing that, he had to follow the current so he would not get swept away. Luckily, the liquid was not cold, or he might have already frozen to death, as it took quite a while to slowly get closer to the shore. The activity was draining him of his energy, as if he was also fighting against himself; also, he had still not fully recovered from his emotional breakdown just a few minutes before. Furthermore, he was struggling alone, while up to now, Simetra had always kept him company.

\froufrou{}

Aurora carried the unconscious Simetra in her hands as she flew through the ley line. She had locked the wooden sign in place between her legs, as her wings prevented her from carrying it like a backpack. She was lucky that there would be no attack or other need to use her hands while floating in the ley line, as she was mostly defenceless this way. She had lost sight of Apollo quite a while ago, as he had fallen right into the magic torrent of the ley line just shortly after they had entered through the rift. In the end, this should not cause any major issues, as long as he followed the current; he should still end up at the exit at the end of the ley line. However, he would be floating in liquid, highly condensed mana for quite a while, and it was not well studied what would happen if a human being stayed inside condensed mana for too long, or even drank it. Aurora was worried, and scanning the surface of the torrent of mana below her carefully, although she was extremely tired from the recent events, both physically and mentally. Apollo was nowhere to be seen. Maybe he was further behind, travelling slower than they had been? Maybe he fought against the torrent? Aurora turned around, fighting against the flow of magic, which did not only move the liquid torrent below her but also the air above. Her progress was slow, but steady. If only Simetra had been awake; as a bird, she would have been able to scan the distance far better. Maybe she could emulate Simetra's brilliant eyesight with a bit of magic, making use of the fact that she was in contact with her, drawing out Simetra's natural abilities? 

Aurora concentrated. She closed her eyes, and focused on her fluttering wings, moving up and down in a steady rhythm. The eyesight of a bird; she envisioned a bird like Simetra in her mind, flapping its wings, following the very same rhythm. A bird of prey, looking towards the far away horizon, focusing into the distance. She became one with these visuals, and slowly opened her eyes again.

She could see Apollo, far away, further upstream. He seemed to be struggling against the current, finally gave up, and then after a while he seemed to try to reach the shoreline. How far away was he from her? Aurora tried to estimate the distance, but her temporarily changed eyesight did not include the necessary experience. Now that she knew which direction he was in, she relaxed slightly, and her eyesight went back to normal again. Surely enough, she could not make him out anymore, not even when squinting. This was bad; would she reach him in time? If he really managed to reach the shore, she was not sure what would happen to him. The ley line was a powerful force, and exiting it by escaping the torrent manually might throw him out at a random place, or could even hurt him. She tried to call out to him, but to no avail, it seemed; at least, she could not hear any response. The gushing noise of the liquid mana below increased, as her mind began to race, and the wind she had to fight against seemed to increase, too. She also tried to contact him via her thoughts, but the interference by the strong mana prevented her from getting through to him. Her only hope was that the increased turmoil of the mana flux would also get hold of him and transport Apollo along, towards her. Still, would she reach him in time?

\froufrou{}

Apollo was slowly getting closer to the shoreline. As he struggled, the current became faster and more turbulent, as if trying to push him back. The gurgling of the liquid increased, seemingly trying to devour him. He took that as a sign to continue escaping the grasp of this strange torrent, and mobilized all his strength. At full force he continued, and the shore came closer and closer. Finally, he could make out the earthy structure at the shore, lined by something like small, mossy stones. This was one strange river, and he knew he had to escape it somehow, as not only his heart began to throb heavily from the exhaustion as he was panting more and more heavily, but his head was throbbing, too. Somehow, this environment was pushing onto his mind, slowing down his very thoughts. He had to exit this stream as quickly as possible. He was sure that falling unconscious in this strange river would not end well.

Finally, he reached the waterline, and touched the mossy stones with his bare hands. Somehow, the moss felt as if it was burning his skin, and the current increased in strength even more, but this could not stop him. Fear was driving him, as his head was aching more than his muscles by now. It took him three attempts until he could finally get a steady grip on one of the mossy stones, and with an inhumane effort, the pulled himself out of the liquid. Quickly, he rolled towards the earthy surface behind the stones, escaping the burning sensation the moss imprinted on his bare skin. As he lay there panting heavily, flat on his back with the pain in his head slowly subsiding, he could see Aurora approaching from up above. She was still far away, but slowly getting closer. She seemed to be carrying Simetra in her hands, and even had the wooden sign with her; Apollo rejoiced. Aurora was wildly moving the head, trying to signal something to him with one hand, and he could see her mouth moving, but the gurgling liquid drowned out all other sounds.

Apollo jumped to his feet, starting to run towards his companions. As he did so, the ground beneath him gave way, and he was sliding farther away from the stream. The pull was so strong that he could not resist; he tried to hold onto something, onto the earth around him, but it seemed to have become too slippery to even grant his fingers any resistance. As he cried out to Aurora one last time, he could barely make out her face, which was full of worry and sadness. Fractions of a second later, the image of Aurora holding Simetra in her arms burned in his mind, he fell into darkness again. As void spread out around him, he could see one item falling towards him: his backpack! Aurora must have thrown it in the last second, and he managed to catch it while tumbling in the nothingness. A worry crept into his mind: Did that mean they could not follow him anymore? Was he supposed to stay inside this strange, forceful stream?

Apollo was at a loss, as the world around him slowly brightened again. All of a sudden, he could see the sky, and a strangely shaped crack in the air which he must have fallen through right now. A second later, his back crashed against something wooden, and he could hear leaves rustling as small twigs scratched his skin. He had tried to turn mid-air, but he was too slow, so he at least covered his eyes. He hit a thicker branch a few moments later, and the air was pushed out of his lungs. Finally, he hit the ground hard, and was left unconscious.
