\chapter{Preparing the Search}
\label{cha:preparing-the-search}
Aurora and her family had finally reached the village. The elder, suddenly emanating a vivid aura of fresh energy, had started to fly faster than all of them halfway along the journey. He had already vanished into his dwelling inside the large tree in the middle of their village, likely researching the strange occurrence in the ancient archives. Aurora and her mother finally dropped off at their doorstep, and with her last energy, Aurora dropped on the bench right in front of their residence located high up on branches of the very same central tree the elder was living in.

Her mother went inside to fetch her something energizing to drink and eat so she would be able to recover a bit while her father was organizing the search party on the clearing below. She had to join them soon to provide a mental picture of Apollo to all those who would help in the search. While emotions and simple statements could be transferred by thought communication easily over prolonged distances, more detailed images or memories could best be shared when being close to the others. But Aurora still felt too exhausted to get up, and the noise of her mother coming back from inside their residence actually startled her a bit, since she was almost falling asleep. But now was not the time to give in to her mental exhaustion.

Her mother gave her a small wooden mug, filled with special, refreshing nectar which should help her to calm down, refocus and refresh her mental energy. Aurora slowly sipped from the sweet, yellowish liquid, and felt her swirling emotions come to a peaceful rest. While she was slowly drinking the nectar, her mother held out a wooden bowl with a puree made from energizing herbs, which would help her to regain her strength by absorbing the energy nature had stored inside the leaves of the herbs and the vegetables which were part of the meal. Aurora slowly dug in, savouring the taste and thanking nature for providing her with new strength. As fairies were living in-sync with nature, they could re-energize themselves this way, but of course they were also giving back something to the nature surrounding them. When in need, though, they could rely on this support from their partner.

\fancybreaker{}

While Aurora was recovering, her mother went to their guest house to which their housekeeper had brought Simetra. She placed her hand on the wooden door, shortly closed her eyes, and in a natural motion, the door shrank back into the wooden wall. It was the usual way in which fairies opened the doors to their buildings: the doors were just a natural extension of the wooden walls, and any normal attacker would not be able to enter their homes. The windows were protected with sturdy gratings, which both prevented accidents and also offered additional protection even if the windows were kept open over night to let the forest air enter. However, the guest house also had a manual opening mechanism which could be worked from the inside, but Simetra had not yet been told on how it could be activated.

Aurora's mother slowly entered the small cabin, and the light inside naturally increased its brightness. She found Simetra fast asleep, but could see that she had already drunk some water and had somewhat calmed down in this unusual situation, so she must have been awake just a while ago. She silently sat down on a wooden chair next to the bed, watching the large owl lying on top of the bed sheets, breathing slowly. Barely audible, she began humming an ancient tune, a melody both like a lullaby and sounding as natural as the whispering of the leaves in a forest. Slowly and magically, the bed began rocking to and fro, careful not to wake up the sleeping owl. Aurora's mother turned her head and focused on the closed window. A short moment later, it opened by itself, leaving in the fresh air of the night and the shine of the moon. As she continued to sing with a seemingly infinite serenity, a barely visible glittering light entered through the window and approached the sleeping Simetra. The song Aurora's mother was humming was entering Simetra's dreams, and the magic energy channelled in from the forest outside would refresh her much faster than sleeping normally.

Of course, this did cost her mother some of her own stamina to keep the balance, but she knew from the tale her daughter had told that Simetra had to join the search, and it was the fastest way to refresh her as most of the other techniques the fairies had available would not work on outsiders. As she calmly kept humming, eyes closed, Simetra relaxed even more in her sleep and absorbed the energy streaming into her.

\fancybreaker{}

While her sleep had been dreamless at first, Simetra suddenly found herself standing on a huge meadow. She looked down, and saw human feet, toes which would move when she ordered them to in her thoughts, human hands she could open and close, and human clothing. Somehow, this felt normal to her in this dream, and she started to run, in no particular direction at all, her blonde hair swinging back and forth from the warm wind. She suddenly stopped and then laid down flat on her back, staring at a blue, cloudless sky and a bright, dazzling sun. As if she was collecting energy from the sunlight, she felt more and more energy streaming into her, recharging her with tremendous speed. She closed her eyes, and enjoyed the warm, energetic feeling. 

The refreshing energy streaming into her body, with her eyes closed, she could focus her thoughts more clearly. Why did this human form feel so natural to her in this dream? Was this a consequence of her having learned speech just recently, or was there more to it? She slowly moved her hands across the green grass, enjoying the tickling sensations on her fingers and palms, wondering even more why this felt so natural and somehow nostalgic. Something was nagging her in her memories, but the more she tried to focus, the farther away that volatile information seemed to float.

Simetra focused on her breathing, in, out, in, out, deep and long breaths. She calmed down even more, trying to free her brain from the countless thoughts and questions popping up in her mind all the time. Right now, she needed to recharge her energies, and nothing else could be more important, as she'd need to be refreshed and focused to rescue Apollo.

\fancybreaker{}

Aurora had fully emptied the mug of precious nectar. She forced herself to stay calm and to empty her mind, falling back on the bench, closing her eyes. So much had happened in the past days, much more than would usually happen in weeks or even months of her life. It was hard to tune out the urgent nagging of her emotions, but she had to stay calm and let the nectar revitalize her from within.

She must have dozed off for a few minutes, as she woke up to a commotion on the clearing below, refreshed as if after a night's sleep. Jumping up, she tuned her mind to the voices below. It was extremely unusual to hear a noisy commotion in the homeland of the fairies, when they usually communicated without spoken words. She could make out the elder, who was insisting that he wanted to speak to her, and her father trying to calm him down. Apparently, the search party had been mostly assembled, and he wanted to wait for her to finish resting.

Quick as a breeze, Aurora jumped down from the tree, slowing down before she reached the clearing. The commotion died down, and the elder immediately approached her. \enquote{Does he have a special eye colour?} he asked right away. Aurora had to close her eyes to remember, and she replied with a clear picture of Apollo's dark blue eyes with specks of brown, which was quite unusual indeed. The elder gasped noisily. \enquote{While I have yet to decipher most of the old records,} he continued, \enquote{this does exactly match with the description. History must be repeating itself, and I am convinced we must help him with all our might. I will stay in the village and continue translating the old records, please hurry to save him.} \enquote{Did the records mention a companion, such as Simetra?}, Aurora interjected. With an expression of regret, the elder wrinkled his brows and clenched his fists tightly. \enquote{I'm sorry, I can not say any more at the moment. The old texts are not written in our common tongue, in fact, they even use a different from of writing, so I need to translate them slowly. I only found the records so quickly since one of the first elders had left short notes which have been translated, but most of the stories which were considered unlikely to be true were not touched since ages.} The elder sighed, Aurora nodded, and then he left to continue working on the old records.

There was a determined, but also somewhat eerie silence in the clearing after the clamour before. All eyes were focused on Aurora. \enquote{We should check on his companion first. While Simetra must be exhausted, it might be wise to take her along, both to increase our chance of success, and since she would likely never forgive us if we did not take her with us,} she finally decided. While her father was nodding, she flew up high into the tree and approached the resting place for guests. She could hear her mother singing within and could not resist but listen, eyes closed. After a few seconds, she contacted her mother in her mind, explaining that they wanted to take Simetra along. She responded, and a few moments later, the singing stopped. Aurora slowly opened the door, the lights were turned up by magic, and Simetra slowly awoke. As she glanced around through half-opened eyes, she noticed Aurora's mother first, jolting awake. \enquote{Shhh, don't be alerted,} she said in a friendly tone. Simetra must have realized that this was the same voice she subconsciously heard before, as she visibly calmed down. She finally positioned herself upright, saw Aurora, and collected her thoughts.

\enquote{What's the last thing you remember?} Aurora asked. \enquote{You transported us. The river, Apollo,\dots We did not reach him?} Simetra replied briefly and with a question mark at the end, slowly becoming more nervous as she felt so refreshed that she must have slept quite a while. \emph{\enquote{Was Apollo still missing?}} her eyes seemed to communicate. Aurora sensed her anxiety, and quickly explained that they managed to make it to her hometown, that a search party was formed in the meantime, and that her stamina was recovered more quickly than usual by the fairies' magic. Aurora was surprised that Simetra actually remembered more than she should have, as she was unconscious right when they entered the ley line. She must have memories from that moment when Aurora used her natural eye sight to magically look for Apollo, which connected her to Simetra even though she was unconscious for a moment. Simetra's mind must have filled in some of the gaps, and it seems she accepted this for the moment.

Aurora could have projected all this into her thoughts, but this would have exhausted both of them much more than this exchange of words, as transmitting thoughts to another who was not close family or even the same race took more toll on the mind than regular communication. They might need all the stamina they had in the upcoming search.

Simetra unfolded her wings and stretched them wide, realizing they had to get going. \enquote{Everyone is assembled in the clearing below,} Aurora explained. It took Simetra a second to realize again that the house they were in was high up and not on the ground. She bowed deeply and thankfully towards Aurora's mother, not questioning who she was, why she helped her or what was the source of their magic, as there would certainly be more time later to talk about all that happened in great detail. Finally, she took flight just as Aurora exited the guest house, gliding down to the clearing, where a new commotion had erupted just as they were arriving. Aurora approached her father with a questioning look, and he started to relay her by thoughts that a scout had returned with news. Aurora quickly interrupted him by lifting her hand up, as Simetra slowly perched on her shoulder. Her father realized that words would be better to convey this to both of them, and after a glance at the scout whom he must have instructed with his thoughts, the young boy who must have been checking out the area around them and already came back to report began to explain.

\fancybreaker{}

\enquote{I made my way along the ley line, and had to stop after a few minutes of flight,} he started to explain. \enquote{As I was exiting our forest and approached the mana collection fields, there was a sudden barrier. It is hard to describe with words --- it was like a rift in the world, going right through everything. I tried to approach it, and actually it did not block me like a wall, but my power of flight just stopped working. I could not even stretch out my hand across it, as if an external will was keeping me from doing so. It felt like the actual fabric of the world was missing in this gap, it was unnatural and frightening.}

As he was still panting from the fast flight, he took a few seconds more to recover, and then projected a picture of the rift into their minds. With enough concentration, he could also send it to Simetra. Shock became apparent on all their faces, as the emotions the scout boy must have felt were transmitted along with the unnatural image. There really was a strange, insurmountable layer of \emph{nothing} right there, in the middle of the forest, thin, but still somehow very apparent. \enquote{I tried to pass around it by flying for one minute in each direction, but it might be spherical, as there was some noticeable curvature,} the scout continued. \enquote{I tested throwing leaves or a stick through the rift, and it also slowed down when approaching it, then slowly falling down afterwards.}

Aurora's father called in three other scouts quickly, and sent them out in three other directions. \enquote{If it is spherical, we might gain some information by finding out where or what is the centre of this strange sphere,} he explained. \enquote{In any case, it seems we cannot leave the regular way to search for Apollo. I wonder how the ley line reacts to this disruption, and whether the elder will find something about this unnatural occurrence in the old records.}

\enquote{I also tested whether magic could pass through,} the scout added. \enquote{Even just sending wind through the rift failed. Magically moving water seemed to create a similar effect as with the stick before, it was slowed down, and then fell, as if all magic was removed when approaching the rift. While it seemed like a barrier first, I got the impression that the fabric of nature is completely missing in this small gap. I wonder why I could even see through the rift and watch the mana collection forest on the other side. Trying to look as far as I could, I could not make out any disturbance in the forest there, though. It was completely silent, as if it was frozen, but as we know, these unnatural mana collection fields always look like this.}

Everyone was quiet, lost in thought. Simetra broke through the silence first. \enquote{May I join the elder, and try to interpret the old records? I have the feeling I could be of help there. After all, the only other thing we could do is wait for the other scouts to return.} Aurora's father pondered this request. Usually, the old records were never shared nor even shown to anybody, but this situation was so abnormal that he tended to agree. He contacted the elder and asked for his confirmation. The elder's reply, transported by thought, betrayed quite some stress, followed by hope when he finally decided to accept Simetra's help. \enquote{You may join him,} Aurora's father said, and the surprise was clear to see on the faces of the assembled search party. Aurora, surprised herself, explained to Simetra that this was an unusual honour. Simetra nodded and quickly flew towards the large tree. Aurora's mother, who must have joined them while they were talking, followed her, magically opening the door to the elder's residence and guiding her inside.

As the silence returned, Aurora clenched her fists tightly, collecting her thoughts. Suddenly, she started to speak. \enquote{Maybe we could also send a scout\dots upwards? If the rift is really a sphere, it must also block the path there, and it might be possible to find out the direction of the centre from the curvature.} \enquote{That's my daughter for you,} her father said. \enquote{Let's do just that while we wait for the other scouts to return. It will be interesting to know how high this sphere is going, or whether there is some opening at the top.} On his cue, another scout left, flying upwards.

\fancybreaker{}

Simetra approached the elder, after Aurora's mother had shown her the way to his study. The elder lifted his hand, and slowly, the wooden wall became alive. A small twig grew from it, forming a rod for Simetra to sit on. She perched on it as soon as the elder dropped his hand down and the movement stopped. All the time, the elder kept focused on an old record lying in from of him, made from papyrus which was of a slightly ochreous colour and apperently had been stored for ages. The small study was lightened by one of those orbs Simetra had already encountered in the guest house, but in addition, there was a small orb with a warm light floating right above the old, wooden desk the elder was using. This was quite a comfy place to read, and even though all windows were shut tight, the eyes would never tire with this natural lighting. The elder kept focused on the record in front of him, with an old book which seemed to be a kind of hand-made dictionary as reference and a sheet of more modern paper next to him, which he wrote on from time to time with a pen which seemed to be made with a piece of coal in front. His gaze did not leave the papyrus, even as he had to turn over to begin writing on a new page of the paper. After he turned it over, he slowly moved his hand over the sheet, and the letters written with the coal pen changed to a metal-like varnish in deep black, which must have been more persistent. 

Simetra watched in awe for a few moments, before she finally focused on the actual writing on the sheets with notes and also the old record. The writing used for the notes was illegible to her, it must have been a special way of writing used by the elder or the fairies, as she had never seen it before. However, when she focused on the old record, the letters felt strangely familiar. Simetra was confused, and blinked nervously several times. How could she be able to read at all, when she was brought up as a bird? Why had her intuition even guided her here, to help the elder?

She closed her eyes. Focusing, she tried to push those thoughts aside. It did not matter why she could make sense  of those records, at least not right now, as they needed to save Apollo. Breathing in, she opened her eyes again, staring at the characters, starting from the sentence the elder's finger was currently tracing along. \enquote{\dots with unusual sparkling eyes, a dark shade of blue, but with specks of brown. A young, human boy, of unknown origin, his parents lost, arrived in our village on the sixth day of\dots} Simetra started to read aloud. The elder twitched when he heard the first words, and his finger started to tremble. Gasping, he shifted the full focus which had kept his eyes glued to the old record towards Simetra, looking at her with great, astonished eyes, gasping. \enquote{You can read the old tongue and writing fluently,} he finally was able to say, his deep and experienced voice still trembling. \enquote{How is that possible?}
