\chapter{The Downfall of O.}
\label{cha:downfall-of-o}
\subsection*{Originally published: \DTMdate{2006-09-13}}
\begin{quote}
Hi!

This time, we shall really go into it. Accompany me when regarding the most peculiar changes, and take your time to decide if anyone may be pleaded guilty or not.

Something turning my world: The downfall of O.
\end{quote}

It had just taken place on the fifth of September 2006. The change was profound, and he had realized that it was final on the next evening.

What had happened? Of course, as he was still in love for his system to block her out had not been completely successful, he tried to be close to her most of the time. She must have noticed, of course, and the moments they were talking shrinked to something close to nothing. This was her initiative again, for he had rarely started talking to her in the preceding months, leaving everything to her. This meant that her silence decided that he was not to talk to her.

Nevertheless, it was mostly him who broke the silence. Finally, he talked to her less than to a normal person around him, and the few words they exchanged in hours --- if any words were spoken at all --- were nothing compared to the sentences that could make their way between him and a friend.

But this was not the event that caused his further reaction; Maybe, it was just a sign that told him that something was to happen --- \emph{soon}. He was wondering whether this change was a result of her relationship with her boyfriend, and whether she had now decided that this one was final, but he gave up on this thought on that special evening, when he sat next to her (accidentally, as fate had placed him there).

He tried to communicate, and she reacted only with the necessary answers. When he said something that was not completely obvious (at least, not to her), she became ironic again.
The irony he had once admired and loved. 
But this time, she was ironic about him.

And this meant that she was laughing about him, and some others joined in. The only sensible reaction he could think of was joining in, and he did so. Still, that was just the first step towards the key events. Often, something we regard as major change is based on small things, and only the sum of them may render something impossible or hopeless.

This time, if not every time, it was exactly like that. Minutes later, when she had been gone for some time and then returned, he realized that concerning the parts of her character that were profound and not so easily controlled were still the same. The food that was placed in front of her and him remained quite untouched on both the dishes, for both didn't like it, while the people around them ate most of it. What had changed with her or him that made them so different now? She had left the table, and the part of her that had cared for his friendship was gone.

This was what he realized now, and at the same time, he felt that he would be able to see her now in the way the others did. And then, she didn't look as perfect as she'd done before, at least concerning her character.

The only critical point he could recall was some moment when he'd talked to her and probably insulted her appearance a bit, but he was just joining her thoughts, for she was always insulting herself. This could not have been the result for her sudden change concerning their friendly relationship, certainly not, for she had not even reacted at that time.

As I've told you, this was only the first step. The next was an insult in front of nearly all the other people he knew and liked. 
An open, not completely justified insult.

She had made a kind of proposal that would exactly fit his own idea, and when he thought he could easily integrate it to present it publicly and please her, she insulted him indirectly and without real justification.

Her eyes had changed then. The stars full of wisdom and understanding had been replaced by a glance of fury, accompanied by a look that seemed greedy and demanding. Was that the real O.?

She must've been more than a spectator of life, then. Though this insult had been officially adressed to everybody, it seemed to be made for him especially, as her eyes told him. Yes, he knew her, and probably, he knew her manners too well to misjudge her once more.

His blindness was now gone, accompanied by his once-so-strong love. Still, this wasn't final yet, for he tried to ignore all those things that had happened, giving her the second chance he'd never really had. 
The next evening, she grasped and dumped this one.

He found her talking to people that showed interest in her, but he had never ever thought them to be of her crowd, really, for he'd thought them to be part of her show of life. The expression in her face, her smile, and her eyes teached him to think differently: Though she didn't seem to love anyone of them, she was certainly showing them the same emotions she had showed him so long a time ago. This face could drive you nuts, and you would not be able to escape this magic easily. Now, he had penetrated the shield, and he would not be sucked in again.

The old O. was gone, and there was the new O., not being the person he had once loved. The person that had probably loved him a long time ago\ldots
But time was to pass, as it always did. And the next second, she and her new, betrayed friends were laughing with her about him. 
He felt that the childish smile and the laughing meant more than the others around her felt; It was not the innocent thing it seemed to be. She knew \emph{exactly} what she was doing, right from the very beginning.

He felt dumped, though he'd never been lifted up by her for real. His next thought was the idea what would have happened if he had really \emph{been} in a relationship with her; Would he have found out by now what she was doing? Was it just a temporary change, or was it final? Had she planned all of it? Was it her way to dump him without hurting herself nor him, for she didn't know he knew everything? 
Was she finally just getting rid of him the way of talking to him less and less, and finally hurting him to make him feel better without her?

He was wondering if she really knew what she was doing. Maybe, it was fate, or destiny once more. But he knew he could not make out the plan, and if he could have found out, it would have been different. 
He was shuddering, for he was alone once more, realizing he had learnt and kept some things from O., P. and all the others. P., by the way, hadn't changed thus profoundly. 
But his best friend had, too.

It was as if friendship meant nothing in these days anymore, and he wondered whether this was not only the downfall of O., but of character itself. He felt he was changing, too, but still, he hoped he could control it. His heart was weeping, but this was normal in such a world. 
A lonely, isolating world in which one could only trust oneself, and not even this was true. 
The only positive emotion was hope; The hope you could trust somebody while you knew you couldn't. But life was the way to escape this reality. 
How did he react to this new loneliness?

He felt more than dumped by O.; In fact, he felt dumped by the world and all its inhabitants. Thus, he tried to change all of it for the better --- He started working, getting his fingertips on quite everything out there. It was his way to deal with problems out there: He would try to change the world, securing his own existence. 
This meant he didn't have any spare time, but he felt that this was the right way as soon as the first people were impressed. Still, L.-B. was stealing time from him, getting on his nerves even worse, becoming more and more offensive. 
But he'd stand it.

When he got his nose into O.'s affairs (though only indirectly), she ignored what he did, and he decided to cooperate with other people around her, thus ignoring her ignorance. And he seemed successful, accepted by the now-changed world, punishing his best friend and O. by not telling them what he was really doing. In fact, this was not so big a change, but it made him feel better. 
Yesterday, the final sign proved him right: O. was outside the library, not very far away. Some small idea of destiny made her turn round to face him, and she was slowly raising one hand, as if to greet him; At the same time, she didn't smile and stopped when she was half-way through. Before he could even try to answer, she was gone. It was as if she was fighting a normal reaction, denying her own self\ldots
If he had done something wrong, he didn't really know about it. He had only once been inconsistent with his normal character, and he had lost some of his cynicism she had been admiring, but that was all about it. Her change seemed to sudden to be any kind of long-term reaction.

Thus, he agreed with the idea that not only he, but she had changed, too. And with her, this was a profound change. 
His decision was final: He'd close the story about O. in the way it had been going on up to now. He was not that important anymore, and he'd probably be better off this way. Still, there was this feeling about the search for the reason of her changing\ldots

But his best friend had changed, too. He knew the reason, at least part of it: His interest in a girl --- or, in fact, in one of two girls while he could not really decide which one he loved --- had changed him, for he tried to adjust his attitude. He lost himself to become part of the group of admirers. 
For me, this admiration had had its share of my life for some time to come. Though it's part of men's nature to admire, it may make you blind. You should never lose yourself and adapt to be like another creature.

He realized that he'd --- in a way --- done so by becoming like O.; His cynicism and simple reactions had become less as he was trying to become a more integral part of society. Maybe, that was the right way to go on, but who can tell?

Slowly, he realized, life was back to normal. Loneliness meant control, and control meant seclusion. Seclusion, finally, meant that you could be yourself below the profiling system. That was the point he was returning to, and he had learnt a lot.

No matter what destiny held in store for him: He'd face it. Even if that meant that there would be a time when O. would return, or at least her character would come back to him in her body or another person. Maybe, the things that make you be yourself are not fixed in place; Maybe, he was even in a happy relationship at the same time with another O. in another world. 
Maybe\ldots

\begin{verse}
The dissonance of time \\
is what we call destiny; \\
If it gets hold of you, \\
which it must, \\
it will seize control. \\
The only way to escape \\
is playing by the rules \\
until the game is over; \\
Then, you may be granted another try. \\
--- W.G.
\end{verse}

\begin{verse}
Who defines the multiduous character \\
of human beings? \\
Can thou control it? \\
Are there signs to forebode its development? \\
Is it really fixed to a single being, \\
or the sum of the multiduousness \\
of individual particles \\
in an eternal stream \\
of consciousness? \\
Do these particles \\
make up our soul? \\
And do the seemingly random movements \\
of these parts of matterless energy \\
define the path of our change? \\
--- W.G.
\end{verse}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../Wilkie_Goldentongue_-_My_Life_in_a_Nutshell_-_Second_Era.tex"
%%% End:
