\chapter{Months of Passage}
\label{cha:months-passage}
\subsection*{Originally published: \DTMdate{2008-03-18}}
\begin{quote}
Hello my friends, 

you have just witnessed some of the moments most valuable to me. They are now forlorn in the stream of time, only linked to my memory and these words. Letters forming a symbolic link to what has been\dots{}

However, we shall now rush on a bit, for the things that have happened in the next months have only drained me somewhat and changed my lifestyle a bit in the direction it was already drifting to. The following chapters will be part of a new section, somehow, forming the thing between the cut we just experienced and university. Filling, but doing even more\dots{}

Join me on the drowsy voyage: Months of passage.
\end{quote}

These months would start quickly, end even faster and without notice they would come to a sudden halt. Daily custom would develop, and drowsiness was to become a normal state of mind.

There were times when time was just trickling, soakening what had been active, turning work into a trotting activity. Things just seem so easy in the beginning, until one starts to adapt --- in a couple of days, the small details begin to grow and eat up the creative ideas that once flooded your mind.

Standing, listening and keeping up the conversation, though knowing that much work was to be done --- I was doing civil service. It meant, there was much to learn, many minutes to wait and listen, understand and adapt. Some changes took place, initiative was becoming more realistic, but at the same time grew simpler. Capped by outer rules, by the past and what had been. Change was faster than it owuld generally be inside the world of bureaucracy, but still somehow too slow for such a young fellow. Generations were parted by their subjective view on time, and one of the greatest problems in human life was the wish to live in the time of another generation. A destructible attempt\dots{}

However, there were many upsides to this time. I had come to know an older person that was working with me --- and she emanated a shimmer of the orange I had thought to be forlorn. And working with her day after day showed me the small little details that would have made the possible past I had been longing for an impossible dream.

It was gone, gone for good. But nevertheless, happy memories and dreams would stay and accompany me for the rest of my life --- reality was just one of the dreams there was, special only because it left us all with the equalities and inequalities democracy was asking for. The dream that was most free of all of them\dots{}

But we shall not think right now, though these months were full of thinking. Few minutes to write, but all the time, the whisper of thoughts was knocking on my mind like a breeze of that hot summer. It was a time in another world, completely submerged in the pool of social relationships and human development --- being with children, playing, understanding who you are, have been and might be. Amongst them were those that searched to display themselves, to impress and struggle just to destroy the equality in this world to make it match their other dreams, to make it lose its speciality, to make it more common and controllable --- and those who defended this world and made friends with it and the other creatures living there, not fighting but protecting them to help themselves. Caring for the "greater good", the silent word that is running through community and never classiefied as what it is --- struggling to make this world a special place --- that was their duty, our duty, and they accepted it before the others even realized.

The interesting thing was the time: How early each one chose his or her role, the place to stay and grow. Few would leave the route they had begun to follow, for fate takes the earliest part in human education and it was straightaway. What we felt, we made feel, what we learned, we would make learn --- mirrors we were, and it was our duty to take care of each other.

That was what I learned in these months --- and I learned to know more and more about people. How they could take things seriously or not, how influence of others grabbed their hearts, how satisfaction was dependent on opinions and actions that were not their own.

For me, a whole new life was introduced: Children were there to look after, work to be done, a schedule to stick to. And time was passing really fast after the first few days had gone by, and a wheel showing dates was turning so quickly I could not even read the numbers --- which meant, they were even closer to my mind because I needed them.

There were many people who could teach me things about human beings I had never heard of, and others that just did their work. Some talked, some thought and others just looked and listened. And I was there to analyze, to learn --- and adapt. And this adaption was the path to the drowsiness I had to learn to endure, a state of mind that would be hard to lose later on, but somehow, the knowledge that was offered was worth it. And it was a deep knowledge, something that went into the mind and would be useful later on. It was one of the things I had been missing for long --- the ability to \emph{see} people, proximity to other creatures faster than ever. Quickly adapting to understand and use the right words\dots{}

It was hours of talking, and sometimes, things were quite complicated. Always fumbling for a key in your pocket you would miss weeks after the last day you had been there --- closing and locking each door behind you, collecting money and joining bureaucratic structures, and finally phoning hundreds of people, talking to answering machines, wondering who would hear your voice in a foreign house.

Feeling the feeling of children calling your name, asking to help them to construct something imaginary that was reality to them. Who does not long to have the imagination of a child?

The most stunning memory I have is that of a small girl telling me about her mother and finally asking me were mine was. She certainly was thinking about it, though she was younger than four years old.

I was soon helpful to everybody there, cleaning the rooms, offering them to carry something heavy or repairing several things. And finally, time was always cutting close, reorganization was taking place and I was in the middle of all this. Nevertheless, most things stayed static --- and thus, one of the most important things about me I have learned was, that being in a static environment is a loss of flexibility, creativity and productivity for me. Some will see this as a logic consequence, but it isn't --- just think about the number of people working according to a regular schedule, and though they are always doing things a bit differently, this finally is static. A world of sleeping creativity\dots{}

Would it ever be woken? And more important: Should it be woken?

I am listening to recommended and loved music, creativity transported by saved data, conserved as books are, but completely different. Waiting for happiness\dots{}

The past had been full of ups and downs, but one thing had always been there --- learning. Analyzingly, observingly, distantly and sometimes closely achieving wisdom. It had been almost perfect, and I would not want to miss a single one of the ups --- and especially none of the downs --- there had been. I am still trying to touch the flame of wisdom, burning my hands --- liking the burns as signs of what had been. 
Please stay with me and watch this candle's hopefully eternal flame burn\dots{}

\begin{quote}
As steady as the rain, \\
we ask if we are sane --- \\
and before we find the answer, \\
we're just down the lane --- \\
the yard of graves is waiting, \\
no time left for newly dating. \\
Death dated us, we can't deny, \\
he makes an offer one can never defy. \\
What has been? Static asking, \\
coninuous working, gasping \\
when things are gone --- \\
you won't get it done, \\
don't ask how, \\
life is now. \\
--- W.G.
\end{quote}

\begin{quote}  
A laugh from down there, \\
two eyes looking up, four, more, \\
a happiness to barely bear, \\
slowly opening a forlorn door. \\
Childrens eyes, \\
truthful lies, \\
mirroring wisdom\\
without disguise. \\
Happy embrace, \\
smiley face, \\
and clearest warmth was there, \\
the only thing we want to bear. \\
--- W.G.
\end{quote}
