\frontmatter
\chapter{Foreword}
\label{cha:foreword}
\subsection*{Originally published: \DTMdate{2006-01-10}}
Hi, you lot out there!

My name is Wilkie Goldentongue, and as I'm not a real living person, you won't ever come to know me personally.

However, you'll be able to enjoy (or not enjoy, be that as you like it) the things I'll write here.
I won't even tell you if I'm a real user of this forum or have just found this happy place to drop my stories like a bird of prey always finds himself something to eat, thus securing the life for himself and his family.

As you may have noticed, I'm English, however, I can understand some pieces of German (enough to be able to use this thingy here, that is). 

But now, I've told you enough about myself. The story will speak for itself, it's mine. You may call it my autobiography (or a short history of my life, or my life in a nutshell,...), if you like to do so. 

Time is valuable, and we are to use it wisely. 

Read the following stories, enjoy them, add your own impressions and learn more about yourself, this world and me. Please feel free to retell these stories, as they are the only thing I'll ever tell you, so don't ever ask for more. As I see, your Admin has opened this thread under the condition \emph{only} to write texts, tell stories or write down real experiences. I've always searched for such a possibility to express myself, and as I'm unable to start something like that on my own, I'm glad to be allowed to use this forum. I'm looking forward to discussions in other threads, if you like these texts. I thank you to be allowed to join this small group of people. 
