\chapter{Adam, Eve \& The unambiguous Signs of Love}
\label{cha:adam-eve-unambiguous-signs-love}
\subsection*{Originally published: \DTMdate{2006-01-15}}
\begin{quote}
  Hi, this is another post by Wilkie Goldentongue!

  Sunday! A day, which at first seems to be long, perhaps too long to endure --- and then, in the end, it's one of the shortest days of the week. 
  But most happily, I was able to reserve enough time to finish the following text; and I was also able to include several pieces of poetry. 
  You are free to regard this as my masterpiece; Perhaps, it will take some time until I continue posting the next text; this one exhausted me, and I feel empty, thrown against a hard wall by the force of the storm of fate.
\end{quote}

Sunday was another day without any possibilty of seeing her, and thus, another day that would pass by thinking about all the things that had happened up to then; other torturing moments when he would understand some of the most cruel signs he didn't understand before.

It was at night, somewhere between winter and spring, approaching a summer of love. He couldn't sleep, as his thoughts were flowing around all the experiences he'd gained the weeks before; he still thought that she'd a boyfriend, as we're just cought between the two occasions we described before: After the first denial, and before he was betrayed by fate.

His thoughts going here and there, he rarely opened his eyes, as he was lying in the dark and in a comfortable bed. It was somewhere around three or four o'clock AM --- that's what he saw when he looked at his clock. All of a sudden, a thought about his relationship to her --- to O. --- entered his mind and brought back some memories. For that reason, he began asking himself why she seemed to like him that much though she seemed to be a partner in a fixed relationship. With these thoughts in mind, he opened his eyes, looking at the red letters of the projecting clock above him; as soon as these clocks were in favor, he wanted to own one, as he often couldn't sleep.

The clock was showing 3:43 AM.

There was something special about it; he was a person that noticed something like that directly, while it would take others some time to figure it out, especially fellow Englishmen, as the word was German. But he had German friends and also did quite well in the German lessons at school. To give you a chance to follow his way of thinking, we'll describe the position of the clock; it was located behind him. As it was quite a simple type of projecting clock, the time could only be shown in one direction, i.e., it was turned by \SI{180}{\degree}. For that reason, what he really saw was 3:43 turned by \SI{180}{\degree}. 
Have you already written down the number and turned the paper around? If you haven't, you can imagine that a \enquote{3} would be an \enquote{E}, while a \enquote{4} would represent an \enquote{h}.

Do you realize what he saw?
He saw the word \enquote{EhE}.
Though it was German, he understood at once. 
A sudden shudder ran down his spine, beginning at his neck and not stopping before it had reached his ankles and finally his toes, before the surprising feeling came back again to flood over his body once more. His senses concentrated; that was something that always happens when you're alone and shocked in some way, especially when it's dark. He saw everything clearly, and he heard his blood rushing through his veins, transporting enormous amounts of a substance called adrenalin. 
He ignored all that.

Just one thought was flowing through his mind: Was it really possible? Could he imagine it?
Yes, he could imagine to marry her.

This shocking fact was something he quickly decided to stow away with his emotions he'd hidden somewhere below consciousness. 
Because then, he realized another time that she was in a fixed relationship; while in reality, she wasn't, but he didn't know that. 
Finally, he analyzed the patterns a clock would be able to show, and he didn't find a lot of words that would be possible to read that easily; in fact, he found none. Then, he had a look at the time he lay awake; he never had a look at the clock again at exactly 3:43, only if he intented to.

And this was the shocking evidence that the chance of this being a random event was quite equal to zero; but he also decided to ignore this logical analysis. 
That was the story of one of the unambiguous signs of love; however, it's not the only one, but it will serve as example quite well.

We'll now have a look at another story: At a time, when he was far from realizing that even a friendship between heim and O. was developing, both were exiting the bus at the same time. He was walking to the left, while she was going right next to him, to the right. This was one of the moments he saved for eternity, as it would take him a long time to understand it completely; as one may remember, we had a look at his youth, a trauma that blocked his emotions completely; and she would change it, but he wasn't yet ready for it.

A man or a young boy was approaching the two persons of our interest; he'd chosen the left way to pass them, and as he was in a hurry, he was to come dangerously close to her. 
And of course, he crashed into her quite hard, so hard it must've hurt her; but he didn't even turn back to have a look. 
She asked our protagonist --- me --- whether I'd seen it. 
He hadn't really noticed what happened, but he knew that there was a crash and that it was some person that simply went on running --- but as he didn't want to offend her, he answered positively.

He was drowsy, as it was early morning, and thus, he was just remembering the way pickpockets were working, which seemed quite the same, and thus, he wasn't able to focus his thoughts on her, as he was still on the brink of sleeping. 
She gave him a shocked, painful look that was demanding for consoling words, for a hand to take her, for a shoulder she could drop her head onto; that was something he would firstly notice after she'd found herself a new boyfriend.

But then, it was too late. 
After having passed around the next corner, every child captured in his / her separate thoughts, she saw some friends and went right up to them, leaving him standing there alone; he noticed that something was wrong, but he couldn't understand.

Finally, he stood there without knowing whether to wait for her to come back or whether to go on; as there was a big chance of other people to approach him, asking him what he was doing here, and as he'd only known her for a short time, and as she seemed to be in the process of starting a longer discussion with her friends, he decided to go on walking, without turning back.

Thinking back to that moment, which is something he does quite often, always gives him a shudder and a shock of pain; Today, he's imagining what she must've thought at that time, and it seems as if he remembers that her voice was shaking a bit.

It's a fact that most men --- all men --- like women that search for protection; however, it seemed that this offer she made to him was too early, as he was traumatized. He'd be healed by the moment when the feeling of betrayal crashed into his soul. 
But that would proof to be exactly the moment his chance would have passed. 
It has passed, though hope is still in the process of dying away. 
I'm now just trying to pack away the pain again, or to go through it to make it disappear; but it won't ever leave me completely. 
We'll now have a look at the next scene, which is quite comparable to Adam \& Eve. 
For an introduction, and to change my mood to give me the strength to continue, I'll quote from a book we're currently studying at university, as it was inspired by John Milton's "Paradise Lost", one of the most important pieces of poetry we've got today. 
\begin{quote}
But think of Adam and Eve like an imaginary number, like the square root of minus one: you can never see any concrete proof that it exists, but if you include it in your equations, you can calculate all manner of things that couldn't be imagined without it.\\
--- Philip Pullman, His Dark Materials, Book 1 (Title: \enquote{Northern Lights})
\end{quote}
That's an author I happen to like, though we are bound to read that books for university, and being forced to read something at most times takes away the experience of discovering a book on one's own. 
\emph{(I think someone was talking about that book in another thread and asking me about it; but I'm currently not in the mood of talking to anybody, as I'm even exchanging letters [like "taht" instead of "that"] because these memories are making me highly nervous, but I guess you'll understand, so please don't ask me anything concerning myself, while you may ask me anything about this story of myself)}
He's right: Everything in the bible is symbolic, and live is to be regarded as something that consists of symbols and signs, too. He also wrote something in chapter thirty-three, which was entitled \enquote{Marzipan}; In that chapter, he described a scene I'd experienced, too; but as I didn't know this book at that time, I didn't realize. But as \enquote{His Dark Materials} was inspired by \enquote{Paradise Lost} --- one of the main reasons why we're studying it --- and as \enquote{Paradise Lost} is dealing with the book \enquote{Genesis} which is to be found in the bible --- I should have noticed, and indeed, I had: 
They were doing an excursion at school, and quite happily for him, at a time when he was still in love with G. --- or at least thought so --- G. and O. were there, too, together with him. 
We'll now have a look at one moment he'd never forget; in one situation, she was asking him for a sweet, and as he had brought loads of them --- she knew that --- he was unpacking his backpack to get one for her. She offered to hold it, as the ground was dirty; she needed both her hands to perform that action. He finally got several of the sweets, and suddenly, mor people wanted to have one; another law of nature. As she didn't have a hand to unfold the paper, he did it; and after that, he just told him to put it into her mouth.

After one second of thinking, he did so, having the feeling of being remembered of something of vital importance. 
He remembered the story of Adam \& Eve. 
And all the stories of those films that show two people falling in love with each other. 
There was always somebody putting something in the others mouth. 
Philip Pullman had chosen \enquote{Marzipan} for that.

He'd chosen a simple sweet; there's no need for us to have a look at the taste, but he still remembers it. 
After he wore his backpack once again, he gave her the rest of the sweets, and she put them in her pocket. 
Some hours later, she asked him whether he wanted one of them; and though he could have unfolded it himself, she did it. 
And she put it into his mouth.

And he still thought she had a boyfriend, even the very moment her fingers touched his lips. 
Times have changed; Today, all this is nearly a year ago. About eight or nine month after it, he'd brought the very same sweets to another excursion, and he saved them till they had to go home, just to present them to her. 
She took them, put them in her pocket, and some time later, she ate half --- and gave him the other half, one after one, but not unfolded, just dropping them into his hand. 
What had he waited for?

At that time, she already had a boyfriend; and if she was like me, she would stick with him and be completely loyal. 
She did, though she sometimes hated him and called him an idiot or something like that --- at least, when I was there. 
Or maybe, this was only what I hoped, as I never heard her speaking when I wasn't near her. 
Nevertheless, she didn't stop talking to me, though she really ignored me this week. 
I'm wondering whether she did that on purpose --- or whether something had happened.

The attempt to contact her still hasn't shown anything, and I'm looking forward to tomorrow, when there'll be the highest chances of talking to her. 
Concerning that story here: That long post will mark a turning point. I'm getting nearer to the present, to the time just on the brink of the end of the second time of depression --- at least, I hope so. And as that is so, I'll start identifying me with the protagonist; we'll switch over to "I" more and more than continue using "he". You may try to interpret that, if you like to do so. 
I shall include some memories at all times, as I can't forget them, but I'll go on to the present, which will hopefully develop itself so as to conclude in a thing you may call a "happy ending". 
I'm not sure it will, though.

But we'll try everything, and the single hope that's left includes the belief, that fate loves justice --- and that God loves love. 
We'll see what happens. 
Please stay tuned\dots{}

\begin{quote}
I will go down with this ship\\
and I won't put my hands up and surrender\\
there will be no white flag above my door,\\
I'm in love and always will be\dots{}\\
--- refrain from a nearly modern English song: Dido --- "White Flag")
\end{quote}

\begin{quote}
The bliss is not to fall in love;\\
it's to be loved, too.\\
--- W.G.
\end{quote}

\begin{quote}
Love is a game of two persons that nobody wants to win.\\
--- W.G.
\end{quote}

\begin{quote}
Life's compound is love and joy;\\
so finally, you're only a toy\\
when joining in this stream;\\
sorrow is real, bliss a dream.\\
--- W.G.
\end{quote}

\begin{quote}
I feel fear --- and sorrow.\\
Something new is closing in, right into my borough.\\
It's full of bliss and I don't wanna miss\\
The moment it's presented to me.\\
I think, I'll love the she. \\
--- W.G.
\end{quote}

\begin{quote}
  When a woman marries again, it is because she detested her first husband.\\
  When a man marries again, it is because he adored his first wife.\\
  Women try their luck; men risk theirs.
--- Oscar Wilde: \enquote{The picture of Dorian Gray}
\end{quote}

\begin{quote}
Many receive advice, only the wise profit by it.\\
--- from a small fortune cookie program
\end{quote}

\begin{quote}
Love is a wall:\\
Climb it, and you'll starve on it;\\
break it, and the stones will kill you;\\
but you have to drag on either way. \\
--- W.G.
\end{quote}

\begin{quote}
A lie can be a knife\\
cutting your world into pieces;\\
but it can also be the glue\\
to hold it together.\\
--- W.G.
\end{quote}

\begin{quote}
Standstill is waiting for death --- going on is walking into his arms.\\
--- W.G.
\end{quote}

\begin{quote}
A sigh can be a brutal lie.\\
--- W.G.
\end{quote}
