\chapter{Second Denial --- And First Doubts}
\label{cha:second-denial-first-doubts}
\subsection*{Originally published: \DTMdate{2006-01-16}}
\begin{quote}
This is Wilkie Goldentongue again!

It's Monday, an interesting day. However, it's also a day when you run short of time; thus, this text will be one of the shortest up to now. But I hope, you'll enjoy it nonetheless. 
\end{quote}

It's Monday, the day I should've seen her for the most time; at least, there were the most chances. Well, I saw her; but not really, as she continued to ignore me, i.e., she talked to me just about 40 words, and no more; and she didn't talk by own motivation, as I had to ask her.

However, she laughed, but it was different now; something or somebody has changed, which induced me to recall quite a famous English song; I guess, there's no need to quote the name of the band, as nearly everybody knows them, though they're not in fashion anymore:
\begin{quote}
No more carefree laughter\\
silence ever after\\
{[\ldots]}\\
Here is where the story ends;\\
this is goodbye.\\
Knowing me, knowing you,\\
there is nothing we can do; \\
Knowing me, knowing you, \\
we just have to face it this time we're through;\\
breaking up is never easy I know,\\
but I have to go;\\
Knowing me, knowing you,\\
It's the best I can do. \\
{[\ldots]}\\
Memories, good days, bad days;\\
they'll be with me always. \\
{[\ldots]}\\
Now there's only emptiness,\\
nothing to say.\\
{[\ldots]}
\end{quote}
I tried just to quote the parts of it that express my feelings, however, I'm not quite so clear about them. I think, nobody can ever be. There has never been a real relationship, not even part of it; just a friendship.

But my feelings have always been different, until the moment she decided to ignore me; I don't know who changed; I just know there has been some change, and I've felt it most strongly today. This texts gave me the power not to think of her all the time, as they took over parts of my memory; they're most valuable to me, and if she ever happens to read them, I'll see if everything was just a dream. 
Maybe, I'll be able to find out tomorrow, or even today; she knows about my attempts to contact her, I've just told her about it in quite a subtle way; if she answers, this will be the first step towards communication.
We'll see, hopefully.
You have to wait, and I am eagerly looking forward to it, too.

These are my first doubts; I don't think my love is really subsiding, but it has been shook quite hardly, though powerful emotions can't be destructed that easily, if they prove capable of being destructible at all; but what's necessarily happening when a strong feeling is insulted or hurt in some way, the opposite feeling is always gaining in strength, as balance is the basis of human existence, though nobody seems to feel like that.

Part of me began to hate her for the pain she'd given to me without even knowing --- or caring --- about it. 
The other part still loved her, and perhaps will prove to be even stronger than before, as hate is the beginning of all love. 
However, I was enjoying myself with other people, now sometimes being capable of forgetting about her, at least consciously; I'm not sure if I'll ever forget her beautiful, intelligent brownish-blue eyes for the rest of my life.
Or the moment right before the first denial, when a vast bunch of photons was reflected between our pairs of eyes: My right eye looking into her left, her left just fixing on my right one, our two images mirroring in each others sparkling instruments to catch in the world around us; that's a moment I'll never forget, the moment I thought we were meant to be; when the small particles of light were just hopping to and fro, connecting our minds, our souls and our hearts; how could I dare not to notice, and even deny that Godly intervention?

I won't ever understand; however, the second denial is really simple to be explained: 
There was a small, young girl, sitting next to me in the bus and getting on my nerves; she always told everybody about everything she'd heard, as the search for attention was her sense of life; her parents had broken up some time ago, and this was her way of dealing with it.

Thus, I always answered with the two letters \enquote{No} when she asked me whether I was in love with somebody she knew. 
Both G. and O. were among these people, and another person we're yet to stumble over --- Y. (Yellow) --- was included there, too. 
A fourth --- or fifth --- person is yet to follow: P. (Pink), a person quite peculiar and interesting, but I don't think there'll ever be anything more than a friendship connecting me to both of them, and --- be that as it may --- I'm happy with it.

This was the second denial --- maybe, the story would come to an end when there was a third --- I guess you all remember Petrus denying his allegiance to Jesus for exactly \textbf{three} times. 
Maybe, we're all surrounded by such signs, but only few, the saddest and most complex, and on the other hand, the most mad and lonely people are capable of noticing these, thus destroying their own lives with a terrible understanding --- maybe, the GUT, the so-called \enquote{Grand Unified Theory} is completely nonsense; most interestingly, life is completely different and dominated by inexplicable signs. 
I notice them, and I'm suffering from this knowledge; but in addition to that, I'm also trying to help all the others to cope with their lives, trying to take some positive turning points by rendering out things to them they'd never have thought of.

As I already announced, this post was to be quite short; don't you worry, the next one will hopefully tell you more, and thus, you've got more time to think about it and give me your opinion. 
Stay tuned\ldots

\begin{quote}
  If a feeling is denied, it'll always strike back by denying itself\\
  --- or by becoming even stronger.\\
  --- W.G.
\end{quote}

\begin{quote}
  Sometimes, there'll be a refreshing rain, giving you a cold shower; and suddenly, everything starts to fall apart.\\
  --- W.G.
\end{quote}
