\chapter{Day of Surprise}
\label{cha:day-surprise}
\subsection*{Originally published: \DTMDate{2006-01-24}}
\begin{quote}
Hello, anybody who's still out there!

This time, nearly everything went different; but as that's always the case, we should have expected it. So, we'll call this the \enquote{Day of Surprise}. 
\end{quote}

It was Tuesday. Tueday, the 24th. And 24 was his favourite number. Thus, this day would normally be one of the worst, as it always was the case that our expectations prove to be completely wrong and in fact just the opposite of reality.

That was also the reason why Friday, the 13th always was a nice day for him. 
But as he expected this theory to be applicable, the day was quite good, nevertheless. 
The first two lectures had been cancelled, and thus, he was able to fetch a bus some hours later. 
He met a girl there which talked to him.

She simply approached him and said \enquote{Hello!}, using quite a friendly tune. 
He answered, though he didn't even know her name. The only thing he knew was that he'd seen her in the bus several times, but he hadn't really talked to her. 
Up to this moment, that is.

And now, she was talking to him, not the other way round. 
She was younger, and still going to school. Thus, she told him about her current situation there and about her friends, which she doubted to be real friends. 
And finally...

finally, she told him that she had no boyfriend, before she asked him whether he had a girlfriend. 
Both agreed they would be waiting for \enquote{Mr. / Mrs. Right}. Additionally, she was asking him \enquote{whether there was anybody in sight}. 
Well, he was shocked, but he kept that to himself. 
He would never start a relationship with her, he was sure of that; she was too young, and she was too weak to look into his eyes while she spoke for longer than a couple of seconds, whereas O. had been\ldots CUTOFF!

The memory was sent away, into the locked room to join the others there. 
This crowd was getting bigger and bigger, and maybe, we all have such a kind of room inside; Possibly, the reason for our death is just that this room is full. 
Today, the doctors tell you that about \SI{30}{\percent} of all diseases are caused by psychiological problems; the word they use is 'psychosomatic'. 
Well, my opinions is, that nearly all diseases are caused by such reasons. 
But we have stopped at the moment when he exited the bus.

At least, that was the thing that had happened next, after he'd said \enquote{Goodbye!} to that girl. 
Another girl from his university exited right behind him, and followed him to the university, not saying a word while walking.

When he passed the parking lot, O. and her best friend were standing there, though he couldn't make out her car. Looking in his direction, the two of them simultaneously raised their hands to wave at him; he did the same, maybe even before they'd noticed him.

He could see her smile from the position he was located in, and he couldn't help but watch her for several minutes while he was passing by, just turning his head to have a look at her. 
The two of them seemed to be waiting. 
He was finally reaching the university, and entered it, thus losing sight of her. 
He went to the library to sit down and enter the world wide web.

For a moment, he thought of her, and all emotions were jumping back at him; but then, his mind activated the recorded version of the song he'd nearly learned by heart now, and the power of these feelings was weakened. 
However, he was still under control of these emotions, as he'd underestimated them; whenever he tried to do a next session, he finished up with a terrible headache; But he was succeeding, slowly, but steadily making progress. 
Then, O. entered the library, about half an hour later.

Her best friend was with her, and the two of them greeted everybody who was present and asked for another girl they were searching for. 
Then, they went away.

He was alone with his feelings again. 
One of his friends was with him, but he was of no help; his best friend was sitting about 5 metres away, enjoying a lecture that wasn't cancelled. 
He couldn't have helped, either.

Some minutes later, O., her best friend and the other girl they'd searched for arrived at the library again and sat down to do some work. 
Somewhere in between, P. had arrived and his friend had gone away.

He was talking to her and another girl that sat nearby, while O. and her group of friends were working. 
Still, he wasn't capable of controlling his thoughts, as he dared to believe that this was the first result of his attempt to forget about her. 
And about an hour later, he would meet G., just to exchange a smile and talk to her boyfriend. 
He knew he should ask G. or O. if he could join them in one of their cars when they did the excursion next week, but he didn't dare to talk to anybody who was in some way connected to the emotions he wished to lock away.

He'd have to go on with the methods he was applying now, and he did so when he was on his way home, in the bus again, and alone, though another girl should have been with him; Maybe, her lecture was cancelled and she was able to fetch some earlier bus.

The consequence of the next session was a terrible headache, but he had learned better to endure such things, as they would pass. 
As another thought about her crossed his mind, he had the image of a synapse that was disconnected and died because the memory was forgot; of course, this was just part of the vision to encourage the process he was going through, as all the memories would be stored somewhere hidden; Nothing would be lost. 
Nevertheless, he could still remember the scent of her perfume when he was in the library, smelling the sweet fragrance though he was nearly two metres away. 
This sensation would also be put into the closed room among others he'd yet to discover again, e.g. the feeling of the hair on her leg when they sat in the bus in summer, next to each other; or the touch of her hand on his shoulder --- CUTOFF!

Again, this was stowed away. 
As a result, he was becoming more talkative; A heart without strong feelings keeping it bound will always open itself to everybody. 
The next vision was approaching him: She was sitting next to him in the bus, and somebody asked him for his weight. He simply answered that he hadn't stood on scales for quite a long time. She had a look at him, quite into his eyes; Something inside him knew he was fat, and she wasn't; He wasn't attractive, but she was\ldots

She told the boy who'd asked --- the same boy who would ask the question that would lead to the First Denial --- that such a question wasn't easy for \textbf{'us'}, meaning him and her, smiling at the same time as she told him her weight. Today, and even at that moment, he wasn't really sure if he understood it correctly that she was just as light as 58 kg. But as her size was about as his size, that meant that she was too light and should grow fat up to 59 or 60 kilograms\ldots

He knew she would laugh at this, if she knew about it. But something had told him at that time that she really meant that it was a problem for both of them\ldots

However, this was the next CUTOFF; something else to put in the adamant box. 
His head was spinning, as he remembered the way she could be sarcastic or ironic in a way that you really believed she was \emph{meaning} it; one of the reasons she wasn't everybodies friend. 
Another vision was rising: The time long before he'd really come to know her, when she stood there together with another guy, presenting the two of them her new mobile. The guy had the same she had, and he didn't have such a new phone.

She said: \emph{\enquote{Yeah, only members of that elite-lecture can have such a thing.}}
At that time, he really believed that she'd meant it. 
CUTOFF --- again.

ANother time: The boy who asked the question that led to the First Denial had once asked her in the bus if he could take seat next to her, and she'd looked at him, smiled a decent smile --- and said 'No.'.
Our protagonist still believed this for some seconds, though he should've known better, and was as startled as the boy, who was beginning to go away, when she called him and explained that she didn't mean it. Then, I had told her that I believed her, too, at least for some seconds, and G. had a funny, questioning look at me. 
That sarcasm was something he'd miss, for sure\ldots
CUTOFF --- another memory in the adamant chamber with the closed door.

Back to the present. 
The day should be finished by now, he believed that. 
And for that reason, it wasn't. 
His mother and his granny had met a girl he'd talked to in the bus for some time, and as she'd known some things about him, his mother believed he was in love with her. 
Well, he wasn't. 

He never would, he was sure. 
But that was some sign --- sort of --- again. 
Probably.

Was it an offer of help from good old fate?\\
\emph{\enquote{Have a look around --- she's not the only one?}}\\
    or rather\\
\emph{\enquote{Cast a look around --- illusion is everywhere?}}\\
He didn't know, but he decided not to figure out, as he was still working, trying to stow his memories of O. away. 
He would be finished tomorrow; He was quite sure about that, again. 
We'll see --- or read --- if he will succeed till then. 

\begin{quote}
His soul had been bound by emotion;\\
now, he was free again,\\
longing for another,\\
binding feeling. \\
Men is no creature,\\
to endure freedom;\\
we're all searching,\\
for captivity. \\
--- W.G.
\end{quote}

\begin{quote}
The usage of irony\\
is the heart of all misunderstanding. \\
Not to use irony\\
is the heart of all misunderstanding. \\
To understand is impossible. \\
--- W.G.
\end{quote}
