\chapter{Decay or new Growth?}
\label{cha:decay-or-new-growth}
\subsection*{Originally published: \DTMDate{2006-01-25}}
\begin{quote}
Hello, are you still there?

Another day; more signs had come, and he'd seen her several times, but his method was becoming successful now. One question is yet to be answered by you: Decay or new growth?
\end{quote}

Wednesday --- the middle of the week, the centre of the life; The harshest day of them all.

But that was okay for him, as he'd learned to endure, and he had to do that, if he wished his method to succeed. Now, he had to prevent to become hilarious about the small effects he noticed; He'd seen her today for two or three times, and once, he was even able to wish her a \enquote{Nice Lecture} \textbf{in return}. But that also fit into the image of a good friendship, and was the relationship he now agreed on with himself; his love had been locked somewhere, and now, there was just friendship remaining; Well, quite so, as the process wasn't finished yet. He still fond himself tracking her with his eyes; on the other hand, he still found himself smiling more when talking to G. than he used to smile.

He did that today, but only something about ten words, no more.

For now, we'll have a look at some important signs he noticed today; you are free to interpret these on your own: 
The girl his parents had assumed he was in love with told him this morning, that she was sorry for having talked to his mother using such words. 
She wasn't in love with him, but he'd known that before; he noticed now, as people who are in love don't forget anything you'd said, at least nothing important to you. 
She had, and he was happy about it.

The next thing that happened was, that L.-B. was following him again and even offered to buy him something to eat --- he refused, and P. did best to help him by distracting him from her \emph{(which was not the original problem, as L.-B. distracted HIM; but if he SEEMED to be distracted by someone else, she might go away; However, she didn't)}.
He wasn't able to send her away; It was even a problem to refuse her offer, as she seemed to get angry, not respecting his wish, but trying to force him to accept it. 
He was happy when the next lecture began and he was able to leave her. 
Really happy. 
Hilarious.

In that lecture, something of interest happened: He made a loud noise while writing, and his fellow students mocked him: They began by laughing, before one of them said that he was always trying to get attention, e.g. by making loud noises, as he didn't receive any of that beloved attention.

Well, he said that ironically, and he knew he was paid attention --- he didn't make loud noises, normally. 
But in fact, attention is something very interesting: It can be paid in many different ways. And the attention he was longing for still was missing. 
The one thing he longed for now was to talk to O., as a normal friend; even if he'd nearly managed to put away his emotions of love, he still liked her as a friend, and not having talked to an important person in your life though you saw her quite often is always a big strain on you self-confidence and your soul.

But we'll try to ignore O. know, as he's trying to do that, too: The song is beginning to get on his nerves, and as it's connected to O., the time of success is coming near. 
He knew he'd always be able to go back to the \emph{backup copy} he'd locked somewhere; but as long as he knew that consciously, he'd always know something about it. He should also forget about that, but this would take a while.

Till then, we should have a look at another sign; a girl he hadn't really talked to for years was now talking to him, in the bus; She was okay, but somehow, he preferred to keep his distance, and she did so, too, as they were different in many ways.

While he was talking to her not that frequently, he had a look around. There was the small girl that had talked to him on Tuesday. She was sitting some metres apart and seemed not to notice him, maybe not recognizing his face \emph{(which was quite improbable)} or ignoring him on purpose --- or just captured by the sensations of her own thoughts. 
When the girl to which he kept his distance was gone, he tried to fetch her eyes or her attention in some way, staring at her for several seconds to induce some kind of reaction; it didn't come. 
Well, that was strange.

But we'll wait till the moment when she had to exit the bus; then, she would also have to pass quite near to him. Just before her feet would start moving in the direction of the door that had just opened, her standing in front of it, her eyes turned for the fraction of a second, meeting his; what he saw was at least that she'd recognized him, but she simply turned to go away. He was just wondering whether this really was the same girl \emph{(he was quite sure about it, but not THAT sure)}, when she waved at him, smiling, passing by the bus from the outside. He reacted by smiling, too, and by lifting his hand. 
She had been the same girl.

Most probably, he'd see her tomorrow again, in the bus; if that's the case, we'll find out about it then. 
Now, the powerful tension that happened to get hold of him when he listened to the song and tried to forget about O. was subsiding; his thoughts were now freeing again, but still focussed on these texts here. 
And they had been written for O. 
Just for her. 
CUTOFF!

Again, the power of his mind saved itself from remembering the things he'd locked away; But at that moment, he wasn't sure whether he'd done the right thing, and whether he'd prove capable of finishing this process comepletely on his own. 
He knew what L.-B. would be thinking, if she was capable of formulating such poetry:
\begin{quote}
If you change your mind, I'm the first in line \\
{[\dots{}]}\\
Take a chance on me \\
If you need me, let me know, gonna be around \\
If you've got no place to go, if you're feeling down \\
If you're all alone when the pretty birds have flown \\
{[\dots{}]}\\
Take a chance on me \\
Gonna do my very best and it ain't no lie \\
If you put me to the test, if you let me try \\[1\baselineskip]

{[\dots{}]}\\[1\baselineskip]

We can go dancing, we can go walking, as long as we're together \\
Listen to some music, maybe just talking, get to know you better \\
'Cos you know I've got \\
So much that I wanna do, when I dream I'm alone with you \\
It's magic \\
You want me to leave it there, afraid of a love affair \\
But I think you know \\
That I can't let go \\[1\baselineskip]

{[\dots{}]}\\[1\baselineskip]

Oh you can take your time {[\dots{}]}, I'm in no hurry, know I'm gonna get you \\
You don't wanna hurt me, {[\dots{}]} don't worry, I ain't gonna let you \\
Let me tell you now \\
My love is strong enough to last when things are rough \\
It's magic \\
You say that I waste my time but I can't get you off my mind \\
No I can't let go \\
'Cos I love you so \\
--- Hope you'll find out where these Lyrics are from; but if you're still reading, you should already know by now
\end{quote}
And he still wished O. would think like this. 
Another CUTOFF was inevitable. 
He wasn't sure anymore that he would be able to endure it, but he knew better than to stop --- 
\begin{quote}
\enquote{Get rich or die tryin'}
--- I guess you happen to know the person who developed this statement better than I do
\end{quote}
He would do so. 
Sometimes, the idea of the American Dream is misunderstood as something that should be applied to the society in general; However, it should be used by each individual as his / her own aim. 
Thus, even if that aim isn't reached, you know you've tried to do something right, which is the most important knowledge in life. 
With this advise, I'm saying goodbye --- till tomorrow. 

\begin{quote}
Hope for a better future, \\
and everything will break down. \\
Work for it and hope for nothing, \\
and paradise's to come. \\
--- W.G.
\end{quote}

\begin{quote}
The cold snow touched his hair;\\
he was cold, too. \\
Inside. \\
His guts were turning all around,\\
as the feelings strained to stay alive;\\
would they ever die?\\
Would he ever be cured again?\\
Nobody could;\\
he couldn't either. \\
--- W.G.
\end{quote}
