\chapter{Last Visit to Heaven / Hell --- The End?}
\label{cha:last-visit-to-heaven-sl-hell-the-end}
\subsection*{Originally published: \DTMDate{2006-02-03}}
\begin{quote}
Hello, I'm back again\ldots

This post may be one of the last in a series; Probably, I'll take some break, but I'm not so sure about that. 
You'll understand that if you read it.

He was wondering: Last Visit to Heaven / Hell --- The End?
\end{quote}

Friday --- the last day of the week of decision, if that was the week of decision. 
His granny was whistling the song \enquote{Strangers in the Night} when he began to type the following letters. 

Strangely, he felt that this had never been the week of decision.
Nothing could be changed that week, at least, nothing concerning O. 
That day, he'd felt that he got used to her. 

In matters of friendship. His method had succeeded, and the only thing that remained was that terrible headache of his. 
It would finally go away, and then, he would be able to be happy again. 
But there was something else that had remained: She had always been a vivacious person, and he'd adopted some of that energy that was inside her. 
He had always been too shy and too calm, and his own opinion was buried beneath the profiling he did; Now, he would be able to change that. 
He was happy he'd met her, after all. 
Even, if there wouldn't ever be a chance for a united future.

He was now quite sure that this was the end, that there was nothing more to come. 
It was finished. 
Life was back to normal again, if that is possible. 
Nearly.

When he heard her explain something about an operation hr boyfriend would soon undergo, he wished for some seconds that the risks were quite high. 
And he even imagined that he would be dead. 
Then, he realized what he would feel then. It would be impossible for him to look into her beautiful eyes once more. 
And he knew that this was wrong; He killed the thought. 
Just a memory would remain, so as to never repeat that. 
And these words, which contain that memory of his.

Seconds later, when she told them that the doctors once even assumed that he had cancer, but now seemed to be proven wrong, he was quite indifferent to that. 
He was stupefied. 
Fate was playing with him; This day, quite equal to the last day, he would sense a lot of things before they happened. 
And that was probably some gift that fate had equipped him with, to show him that the future is still there. 
Oh, yes, it was.

He'd knocked on her door that morning, for the last time, probably. 
Of course, it would be the last time for ages. 
He was sure of that. 
And she was \emph{not} together with her boyfriend, but with G. 
Thus, he didn't see her alone that day, and he was sure he would never be alone with that girl again, at least for some months to come. 
He could have told her a lot of things, but when he was alone with her, he didn't remember these; And when he wasn't, he didn't dare telling them. 
For some seconds, he was alone with G. that day, and she talked to him. 
She took the initiative.

Well, she still had a boyfriend, but that was the first sign of the friendship that had been there long ago since quite a long time, with the possible exception of the smile that both of them had exchanged often. 
But O. distracted them quickly, and G. seemed to prefer to stop talking to him. 
Ridiculous thing. There was something special about the two of them, and about him, but he couldn't make it out. 
Maybe, that was the thing that facinated him. 
That feeling to be together with somebody completely different. 
When he was able to watch O. in some mirror again, he could have a look at her hair: It wasn't completely the same colour, it seemed to contain all the colours there are, while it looked strangely organized and perfectly arranged all the same. In fact, he was pretty sure she hadn't dyed it, but he realized it looked as if she had done so. 
And it looked perfect.

The other strange thing he'd noticed apart from her clean, ivory skin was the way she moved: As if she was flying, barely touching the earth. 
She liked to dance, he knew that. 
Nevertheless, that gaver her the look of an angel, sometimes. 
And G. was quite similar, as far as that was concerned. 
All the same, she was completely different.

That day, he'd also sat next to a girl he'd always thought to be interesting; But she seemed to be more shallow than he'd thought. 
Nonetheless, she'd asked him more questions than ever that day. 
And he answered, using more words than he'd ever used that day, as she seemed to be really interested.\\
\textbf{FLASHBACK}\\
O.\ldots\\
She was sitting next to him. 
It was the time when she was without any boyfriend. 
The time when he didn't know that. 
The time when she'd asked even more questions, when she was really interested\ldots
\textbf{CUTOFF!}\\
Those times were gone. 
He was back to the present. 
This girl was still sitting next to him, but as they were working in a group, that was normal. 
And there was silence.

That girl and her best friend --- a girl, too --- were living in some kind of celibacy, as it seemed that they've never had some boyfriend and they announced publicly that they didn't want to. 
And that girl had also offended him several times, as he seemed to have strained her nerves when he thought that he was pleasing her, just by telling her which books she could read.........
Well, she didn't seem to like to read some book right now. 
She was more shallow than he'd thought. 
His profiling system had failed --- again. 
He would be careful now. 
One should never trust his senses.

He felt ill, but he knew that this would pass. 
He'd just lost part of his soul; it had died, or locked away, at least. 
But he knew it wasn't really locked away; His feelings for O. were still there, it was only that he didn't feel the pain anymore. 
And, that they had become weaker. 
Her initiative could wake these storms of emotion again, and he was deemed to wait. 
For now, he was cured.

When the temporary sickness had passed, that is. 
When he closed his eyes now, he could see her back; and she was moving, away from him. 
Hopefully, to some better place. 
Now, as he had lost the desperate longing, he wanted her to make her fortune, wherever that would be; and with whoever she would find it. 
He was just searching for her happiness, as he knew that he couldn't keep her. 
She was on her own. 
He was, too.

At another place, in another time, probably, even in another life, things would be different. 
Worse, or better. 
We won't know. 
And we don't want to know, either. 
Future is something one shouldn't play with. 

One single tear was forming when he thought about the past; One should know it, but contemplating about it was not always the nicest thing to do. 
But that could help. 
He suppressed the tear, knowing what he'd lost --- probably. 
When he finally sat in the bus again, he looked outside, seeing some of his friends. 

But what he didn't notice first, was P.'s friend waving at him, the girl that was multi-couloured. Now, she seemed to be emanating something between white and brown. 
And she was waving at him, before she did a complete turnaround to show him she was happy. 
And she was jumping, of course. 
Yeah, she was a vivid girl, too; But so vivid?
Was she liking him as somebody who would be more than just a friend?
He didn't know, and he would have to wait until he'd find out about it. 

But we'll have a look at his illness, that seemed to rob him of his senses, too, as he didn't notice that girl that had sat next to him though he \emph{knew} that she was walking just some metres away. 
But he just forgot to look. 
Thus, he couldn't see whether she'd seen him. 
But he saw O., though she didn't see him; and he waved at her. 
He couldn't reproach her that in any way, as she was driving; but at that moment, she had come to a halt, and had time to look. 
And she'd looked into his direction, nearly. 
He was so near he believed that he could see her eyes. 
And she knew that he was in that bus. 
The moment passed. 

He became crazy that evening. 
Well, sort of. 
He contacted O.'s best friend, using the same way he'd used with O., hoping that she would respond him, at least. 
And he'd set some kind of ultimatum: If he didn't think differently on Monday evening, he would be sure it was finished. It was now fate's turn; We know one should not put pressure on fate, and probably, that was an error of his; but he didn't know what to do otherwise. 
He began to tremble, when his body went cold and his brain boiled; he felt really ill. 
But he knew that this would soon go away. 
He was pretty sure.

But he wasn't so sure about the future of this story\ldots
Probably, the throughput will be reduced by a factor of two or three, as O.'s story seemed to be finished.

But life was still going on, and nobody knows how much things are yet to happen.
Change will always be. 
As long as time exists, that is. 
As long as \emph{consciousness} exists. 
We'll see, hopefully --- or not so hopefully. 

\begin{verse}
The fire was burning \\
the woods. \\
The water was refreshing \\
the animals. \\
The sun was lighting \\
the world. \\
And her face was blending \\
his soul. \\
--- W.G.
\end{verse}

\begin{verse}
Bang!\\
The next round had just begun. \\
He was back to the ring, \\
fighting for his life. \\
And it would be a fight, \\
till death; \\
It was the fight \\
for life itself, \\
the same fight \\
nobody could ever win. \\
--- W.G.
\end{verse}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_First_Era.tex"
%%% End:
