\chapter{What now?}
\label{cha:what-now}
\subsection*{Originally published: \DTMDate{2006-02-06}}
\begin{quote}
Hello, I'm there --- again!

Monday; long, lonely, boooooring Monday. 
A lot of things to write down, nevertheless. 
Probably, that means that I'll take another short break in the next time. 

Well, but for now, just one question is torturing me:\\
I'm asking: What now?
\end{quote}

Monday; the day he'd sit next to her again. And indeed, he did. Nevertheless, what the tow of them did was just smalltalk --- nothing more. 
And her best friend was even more talkative than she was, though she was seated one place farther away. 
What should he do? The emptiness was still there, and nobody in the world out there seemed to be interested in him. 
Not in the way he hoped people to be interested in him, that is.

A girl that was now sitting next to him in the library asked him something; he responded without hesitation, though he didn't know her. 
That was peculiar. 
At least, at the moment when she asked him what he'd like to be in the future. 
Which job he'd like to do. 
Interesting.

She smiled, but he knew that this was just a game. A game of interest, of friendship, a hope that this words she was telling him would pay off; somehow. 
In some future time. 
When she went away, she didn't say a thing; Not a word of goodbye or something like that. 
And he didn't, either.

The internet access was blocked in some way in the library; suddenly. Well, he had something to do --- he could write. And he did. 
Without hesitation, his fingers hopped among the keys, choosing the letters without realizing what they were doing. 
His mind did. The wonderful power of consciousness was controlling the simple, fast movement of his fingertips. 
They hit the right button most of the time. 
Amazing.

And that stupefied him, as he realized that this process of writing gave him new energy. It made him feel happy\ldots
Was this some kind of substitution or reparation for what had happened?

He'd proved the existence of God in the last text just by chance --- and for fun. 
All the same, he'd made some connection to Douglas Adams again: He'd proved that God didn't exist, using quite the same amount of words. 
He smiled again. 
But it wasn't worth a thing, that smile.

He'd once heard that mathematics could be erotics in the head; Well, writing --- and reading, of course --- could be the same. 
Now, he'd realized that. And when he'd looked at her again, that morning, he'd seen how pretty she was. And at the same time, he'd felt that it all was some kind of illusion. 
Just an image of something\ldots

A projection of consciousness?
And if beauty was an expression of thought, then that meant, that all matter was. 
Which explained, why our scientists would never ever find an explanation for it. 
If all our basic laws were just an illusion which was projected by conscience, then that meant inevitably, that we \textbf{made} our basic laws, in fact. Thus, this would explain \emph{why} there would never be such a thing as the GUT; And, why our scientific research would never end.

Interesting --- this was just some sort of model that explained everything. Quite. 
But he knew that it was really improbable. 
Finally, nobody could ever prove it --- but on the other hand, nobody would ever be able to prove it being wrong. 
Nice; this was some sort of theory all the philosophical scientists would like. 
Maybe, they wouldn't ever read this, and probably, they would never happen to like it. 
But we've got our own problems. Everybody has.

He took a look around. People began to ask him, what he was doing there, hitting the keys with his fingers --- and he told them, that he was just training. 
Training to write\ldots

Every once and then, P.'s friend walked up to him, looking how he was proceeding --- she knew what he was doing. 
And she'd already started reading his story.

Additionally, she thought that this story was real, which it was, in fact --- but he told her it wasn't, as he didn't want to tell her about O. In addition to that, he also didn't like to tell her about herself being part of that story; If she wished to know about that, she'd have to go on reading.

This morning, he'd looked at O. when her head was turned in his direction, and the two pairs of eyes met each other again. 
He feared for the stability he'd achieved now, and looked in some other direction quickly; She did the same. 
Amazing. 
Did the two of them feel the same way, at the same time?
No. 
She would feel different. 
Of course. 
Well, maybe not \emph{so} different. 
But that would just be one of the hopes that would never be fulfilled.

He looked around again --- Now, there were other people around him in the library, as he'd done a break, concerning his process of writing. There had been another lecture he'd had to attend, thought a lot of lectures had been cancelled that day. 

This day had been quite normal, in the end. With the possible exception of his feelings for O. --- they had changed. 
He'd locked them off, somewhere.

Another hour had passed by, and all the people around him were walking away; the library fell silent, and he was left alone, among the humming pair of computers that would receive some kilobytes that emanated from his fingers.

Information --- information technology. Something interesting. He'd always loved to play with modern gadgets\ldots
And now, he could simply type texts. Texts, which contained his memories, so that others could read them. How many people would finally find that page and download these texts?

Would there be some time when O. found them?
Would she read them?

Probably not; They were too long, and she didn't know who had written them. Which left him with the question if she would read those texts if she knew it\ldots
No. She always pretended to like reading, somehow, but she was one of the persons that had never really finished a book if they weren't forced to do so. It was no matter of discontent with the process of reading, but it seemed that she didn't reserve enough time to do so. 
\begin{quote}
What we love to do we find time to do.\\
--- from a small fortune cookie program
\end{quote}
Yes, she didn't love reading enough; She hadn't experienced the happiness of a real landscape unfolding itself in one's mind, the reality of an inspired imagination\ldots
Few people had.

In fact, he knew \emph{nobody} who'd really read something for the sake of his own experience. 
Nobody, who would agree with the power a book can unfold; the magic of words was something quite secret to most people. 
And few seemed to care about it.

To care about something was the basis of human intelligence, and finally, this meant that everybody had the same capabilities. In the end, this would mean that everybody could gain a sort of intelligence\ldots
Were our talents just the things which we liked most?
Was there \emph{nothing} one couldn't do?
Was everything just a matter of interest?

Maybe. He remembered how he'd asked O.'s best friend if she'd meet him, and bring O. of course, in their spare time, so he could show the two of them the strange methods he'd always used to learn. To explain to her what he was talking about, he told her about one of those methods, and she rather seemed to like it. 
Now, she hadn't answered him, nor had she ever arrived at the time he'd proposed.

And, after the long texts she'd wrote him about two months ago, he'd never read anything from her again. 
But that was nothing new: The two of them simply didn't seem to \emph{think} about the importance of the words they could transfer to others. And underestimating one's possibilities --- and one's importance --- are the basic flaws of most humans.

Great people always knew about the power of words --- and when I'm talking about \emph{great people}, that includes the good --- and the bad. 
I guess, all of you remember some examples from the history of our world, probably in more detail than I do.\\
\textbf{VISION}\\
Some vision had suddenly got hold of him: He was next to O., and their eyes met. He could see his own soul in the mirrors of her eyes, and he knew for sure, that she would see her's in his. 
Then, she asked him what he felt --- for her.

He thought for some seconds, before he answered: \enquote{It's a word with four letters, and I've never dared telling you.}\\
He felt her hand on his shoulder, and she smiled.\\
He smiled, too\ldots\\
\textbf{END}\\
The vision had passed, and he knew that it was just one of the last outbursts of emotion that were to come. He was still training to control himself. 
He'd sensed something, however: His eyes were regaining their colour, and their strength. His soul had been healed, and he knew that.

Standing at the bus stop, he could hear the loud humming of the motor of a bus that was waiting in front of him, just about two or three metres away. He looked to the left, as that would be the direction from which \emph{his} bus would arrive\ldots
And he concentrated. Finally, he thought he heard how the bus turned around the corner, and then, how it accelerated just to turn around the next one. 
Then, he saw it.

It was nearly impossible to hear that even when no other bus was standing there! And this one was pretty loud\ldots

He knew that something was different. Had he known something in advance again? This was the most realistic thing, though it wasn't realistic at all. 
That morning, the thing with the ruler which always was on her paper before she needed it hadn't worked; He had changed.

He knew that, and he realized the complete extent of that change when she started searching for her ruler, and told him she was doing so. As fast as he could, he passed her his; This would be one of the last resorts he'd give the \emph{feelings in chains}. Thus, he didn't want to lose it\ldots

But that morning, he'd seen Y. and her best friend in the bus. What had they been doing there? Normally, O. or G. would take the two of them --- or at least one of them --- on one of their cars\ldots
But he hadn't asked Y., thought he'd greeted her friendly, of course. But she was absorbed in talking to her \emph{(female)} friend and her younger brother. The scene looked childish, when her brother and her friend united in some sort of play to agree on something she didn't like. Of course, she noticed that, and all of them knew, that this was somehow a childish manner --- but they liked it nonetheless. 
The two of them were mocking her, no question, and even laughing about her way to laugh. 
And he sat there, enjoying the scene. 

Once, Y. greeted him and nobody except her --- and him, of course --- seemed to notice. 

It was one of the scenes which tell you that there is some sort of secret connection between you and the other person, but of course, this was all just on the basis of friendship. And she liked to play with such secrets --- he'd made that out, already. 
But we're not just to focus on her --- finally, he hadn't seen a lot of people that day, apart from P.'s friend and all the other people there are, but just for the glimpse of a moment. 
He was absorbed in his thoughts, and they seemed to feel the same way, too. 

Peculiar --- somehow, the environment always seems to reflect your own sensations. 
Then, he thought about the dialogs with P.'s friend, changing perspective so that he was now looking at it from her point of view. 
She could have felt offended, sometimes, as he didn't show as much interest as he could have shown. Maybe, he shouldn't. Maybe, he should. 
He didn't know.

Probably, he'd find out more about that tomorrow. 
And he was still waiting for O.'s best friend to react on his attempt to contact her. 
Is there now just time to wait and see, again?
If you want to find out, please stay tuned\ldots

\begin{quote}
Night was closing in; \\
nevertheless, there was still some light, \\
all around, \\
and inside. \\
The power of consciousness, \\
that would never die. \\
--- W.G.
\end{quote}


\begin{quote}
\emph{\textbf{Shooting Star}}\\
Standing at the bus stop, \\
he suddenly looked at the sky. \\
And he felt, that behind the clouds, \\
there was something. \\
Moving. \\
A shooting star. \\
He saw it, though the clouds were to thick; \\
and he wished what he'd always wished: \\
Health for all of them. \\
And luck, of course. \\
But something was missing. \\
O. \\
His wish for her love\ldots\\
It had been a victim to the process \\
of forget. \\
Now, he called the memory back again, \\
to return \\
to the place \\
it had been taken from. \\
And it sat down there happily, \\
so he could retire, \\
and gain stability, \\
again. \\
--- W.G.
\end{quote}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_First_Era.tex"
%%% End:
