\chapter{Back to Life?}
\label{cha:back-life}
\subsection*{Originally published: \DTMDate{2006-02-13}}
\begin{quote}
A long break, but there I am, again!

Hope you were looking eagerly towards this new post; at least, I was, as there were so many things happening I wanted to tell you. However, time is running short, as it's always doing\ldots

My question is: Back to Life?
\end{quote}

The weekend had passed in a horrible rush, and now, Monday was closing in. 
It had already passed, in fact. 
However, there were not a lot of things which had happened that day; at least, nothing of real importance. He thought about everything again, and he realized that everything was as important as one believed it to be. Finally, he agreed with himself that this day was not so irrelevant at all\ldots

But before we'll start with today, we'll have a look at Friday, as that's the day which was next in line. 
Friday; That day, the work together with P. had been finished, nearly. At least the part the two of them would do together, as the rest of the students that made up this group of four didn't really do a thing. She had been nice to him, and they'd both finished it together in their spare time, in the library. The girl that once had stood at the bus stop alone, the same that was now just having a new boyfriend, was sitting next to them, though she wasn't taking an interest in their work, really; But where else should she go?

That Friday morning at university; He couldn't remember having seen O. \emph{at all}. But it seemed to be of no importance anymore, and he knew that she just had a single lecture that day. Then, he remembered that she would reside in the auditorium next to the one he'd sit in; And he remembered having seen and looked at her, though it could also just be part of a vision his mind was proposing him to make things easier.

Again, he knew something before it happened, though he could also have found out by the usage of logical analysis: P. would miss the last lecture, but as she'd already told him she'd give the professor her work \emph{before} the lesson, he \emph{could} have known. And he had, indeed, as he'd hoped for her being there; Thus, he knew that this hope would never be fulfilled, as he didn't realize that it wouldn't. Not consciously, that is.

However, the evening would prove to be more important: He'd watch a film, which would be full of symbols telling him things about himself. 
Such a big amount of symbols was nothing that could be a result of chance; Fate had interfered once again --- or probably that undefined power that existed somewhere out there?
His heart raced as he realized that this was to say something, but he couldn't make a sense of it; Neither had O. nor her best friend answered to his attempts to contact them, nor had they contacted him in any way.

But the film could also be the signal of the relationship being over, without any future. 
He remembered, how the main actress was just \emph{playing} with the men she knew, quite unlike her sister in the film. Then, she'd even dared to take away her best friend, and that guy was proposing to marry her.

She didn't accept, and she betrayed him. In the end, when both had gone separate ways, as the mutual trust was killed, she was left alone, really feeling sad for the first time in her life. And that film had been called \enquote{The Truth}; A title so simple, a story so true --- and as complicated as life itself.

After she'd been alone for something about half a year, she got to know that this man was going to marry her sister; As a result, she decided to kill herself, got a revolver and went to his apartment, just when he was alone. Though he had been warned that something might happen, the two of them met each other, alone, once more. Before, when she'd visited him on the day before the marriage, they'd spend the night together; Then, he'd told her about the relationship he was having to her sister and sent her away. 
That was the trigger. 
And she pulled it when a struggle developed, he accusing her of having never loved him, and she telling him she couldn't live without him. 
All bullets hit him, and he was dead in an instance. When she turned the pistol to kill herself, it was empty, and just a \enquote{click} could be heard.
Thus, she'd have to use gas.

But before she was dead, some friends entered the apartment and rescued her. 
At this point, when the trial began, the film started. 
The outcome of it is not of real importance, and the way it was done is not so important, either; But one sentence she'd said is of vital importance to us: \enquote{We've both loved each other, but at different times\ldots}.

She'd learned the reality of that feeling too late, at the same time he'd given it up. 
The same thing that had happened to him and O., probably. But he wasn't so sure about her love anymore. 
But in the end, all chances were gone, anyhow, he'd realized\ldots
For now. 
He knew she had been presented a voucher to go diving, together with her boyfriend (from him), and he was quite sure she hadn't used it yet. Would he ever have liked to go diving? Yes, probably. 
Would she? Probably, too.

If the film was a sign, it meant that timing was the most important thing; A tune, a song was coming back into his mind: \enquote{Timing is everything, you gotta get it right\ldots}. Yes, you gotta; Chris de Burgh was right. 
But if you didn't realize that the clock was ticking, timing would be quite problematic. And the movie seemed to tell him that it was over. 
And it didn't leave room for hope. 
Would that help him?

He didn't want to find the answer, and decided to go on explaining what had happened on Saturday. L.-B. had phoned him, doing some smalltalk for nearly one and a half hour; She was really getting on his nerves, but he couldn't tell her, otherwise, these \emph{"listening sessions"} (as he nearly said nothing) would increase by a hundredfold. 
But that wasn't the important thing about Saturday; He had contact to P.'s friend again, just over the internet. They \enquote{talked} for quite a long time, until he had to go away. And he'd enjoyed it --- She had done the same, it seemed.

He'd missed P. herself just by five minutes or so on the world wide web, but the next day --- Sunday --- she'd phone him, to finish the work they'd begun. 
They did, and he enjoyed talking to her, too. But in some different way; However, he wasn't sure that the way he \enquote{talked} to P.'s friend was just \emph{friendly} --- or more. She didn't seem to know, either.

The next important day is today --- Monday. 
A lot of things happened that day, but nevertheless, we'll start with the morning, when the bus was having some problems. 
He started driving nearly half an hour too late; But in the end, he was able to catch up. This was some shocking experience: The timing was wrong, but with extreme effort, it could be corrected\ldots

Was this another sign? What should he do?
Monday was the day he'd sit next to O. again, in the first lecture of the day. Her best friend would sit next to her, too. He saw how she was searching for a bonbon in her bag, and her best friend looked inside that bag interestedly, not hiding her wish to receive one, too. O. looked at her, both smiling, and O. said: \enquote{You want one, too.}
She only answered: \enquote{Yes.}
And the bonbon was given to her, just \emph{after} she'd dropped one on his table. 
For him. 
Without having looked at him.

Of course, he accepted it and thanked her. Nevertheless, the scene looked somehow ridiculous, which made him enjoy it even more. 
He unfolded it himself, trying to make the same noise she'd made, while her friend tried to be quiet.

The thing with the ruler dropping on her sheet was something he'd do again that lecture; Once, that day, he'd missed the moment when she'd needed it, and the ruler of her best friend was to be used. 
He wouldn't fail again, he agreed with himself quietly.

When the lecture had passed, he knew that she'd have an exam, at least, to a high degree of probability; Thus, he said: "Good luck to all of you!", looking into O.'s and her best friend's direction. 
Both seemed not to notice, and they were gone faster than ever.

The next time he'd seen O.'s best friend, he'd asked her whether she'd seen his best friend, as he was searching for him. At first, she didn't know, and then, when he was about to leave, she noticed him about two metres away from the place they were located.

He fetched him to go to the library again, where they'd meet P. and her friends. He and P. were having a spare lecture now, but in fact, both were just fooling around. 
Later, he, P. and her friend \emph{(the very same girl we've talked about for so long now)} met again. This time, they were fooling around together, with the computer in front of them. After he'd answered some question of Y., got loose of L.-B. and sent the boy he thought G. was in love with away; And the girl that had asked him when sitting next to him, while O. was there, nearby, in silence. She may also be important in the future, and it will be more easy to give her a name, as he'd known her for some longer time; Something between six and eight years, in fact. We'll call her B., as her major colour is black, though she is also multi-coloured, in some way. But black is the sum of all colours there are\ldots

Well, she wasn't really interested in the work both had to do, and she \emph{wanted} to go, even though it wasn't finished; but before, he'd stood with her in front of that old picture with all those students, and she'd found him faster than he'd done himself, pointing out that this was really easy. And he'd told her that he found it hard to differentiate between G. and O. on that picture, but she'd proved what he'd thought before.

He felt guilty, as he talked about G. and O. as one entity, as \enquote{things} without names; He knew that O. would hate that. But his secret love was to be protected, if it still existed, burning somewhere deep inside; He knew it did.

We've stopped the moment he was together with P. and her friend in front of the screen, alone. Y. had just left, telling him once again that she thought that P.'s friend was searching for more than friendship --- and smiling.

The most important thing about the following scene is the moment when he leaned forward to watch waht was happening, coming so close to P.'s friend that he could make out her fragrance. It was some sort of perfume, of course, but he could also smell \emph{herself}. Normally, that's something we don't notice, as it's happening subconsciously, but he realized that the perfume \emph{fit}. Taking into account that she'd really \emph{waited} for him in the library, he wasn't so sure about his theory of a stable friendship anymore; Was there more to come?
If you want to know, then you'll have to wait, as this story is real --- and real-time.

Probably, the frequency and the length of the posts will be reduced, as exams are to come; But I'll try to go on!
Hope you stay tuned, and please look forward to the next post!

\begin{quote}
P. was embracing her friend; \\
was she longing for his embrace? \\
Did he long for her's? \\
Would he ever know? \\
Would the timing be right, \\
in some distant time? \\
Or was it, now? \\
Was he back to life? \\
So many questions; \\
and they can only be answered positively, \\
if you don't search for the answers. \\
--- W.G.
\end{quote}

\begin{quote}
The stars were falling down again, \\
like rain --- \\
eternal rain. \\
Their dust was blinding him, \\
and their light enlighting his soul; \\
What was happening? \\
He wondered. \\
He didn't ask. \\
He just let it happen. \\
He trembled: \\
Should he act? \\
Should he wait? \\
What was to be done? \\
--- W.G.
\end{quote}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_First_Era.tex"
%%% End:
