\chapter{Where to Go?}
\label{cha:where-to-go}
\subsection*{Originally published: \DTMDate{2006-02-20}}
\begin{quote}
Wilkie is back --- and he's still in good health!

That day was full of spare time, which meant that it was really exhausting, as he'd to spend these hours at university. 
However, he wasn't alone; but you'll find out later, when you decide to go on reading. 
\textbf{If} you decide to do so, that is.

In Front of a Fork: Where to Go?
\end{quote}

Monday; the day he'd see her pretty long. But this time, it was really different for the first time, as his feelings had changed to something that was even below a strong friendship; and it didn't feel as warm as it did before when he sat down next to her, and although some things he did made her laugh, he knew that it was just a kind of game --- nothing of importance anymore. However, the thing with the ruler would be the single action that would remain, reminding him of the feelings he'd once felt consciously; Still, he'd try to drop it on her paper before she'd grabbed the ruler from her best friend, and once, when she was pretty close to doing so as he was in need of his ruler himself, he quickly dropped it at the right place on the page in front of her, though her hand was already touching the ruler her best friend was currently using.

She wouldn't have touched his ruler while he was using it, it occured to him. However, even before this gadget of plastic that symbolized so much had crossed the border between him and her \emph{(in fact, it was just about to do so)}, she thanked him, moving her right hand back so it was close to the paper that was still in front of her again.

Her best friend seemed not to have noticed; However, she didn't seem to react on it. Later, when the lecture was paused for some minutes, she \emph{(her best friend)} offered O. something to eat; and then, she asked him directly if he wished for some of it, too. 
He agreed, of course.

Then, he watched O. interestedly, realizing that she ate the same peculiar way he did. Well, this time he hadn't done, as he was training not to do so in public. 
\emph{She} didn't seem to care, however. Once, when she was stretching herself in that very break, he had a close look at her face again, not being sure if sh'd noticed his observing look; She looked completely different to him now. He could \emph{see} the way she'd attracted many persons by symbolizing somebody helpless, incapable of defending herself, though she wasn't; But her face had changed, and the expression it was showing.

Now, it seemed to be more \emph{normal}. He wondered what made this face so \enquote{normal} and realized soon, that she didn't appear as somebody perfect anymore to his senses, which meant that the feelings were locked away, and the door shut tight.
But on the other hand, it could explain something else he'd heard that day: A woman his mother and his granny had talked to was complaining about her former husband having changed completely, turned over in some way, since he was together with his new girlfriend. Had the same thing happened to his once-beloved O.?

He hoped for it, as it was the only way to conclude that she was not the way she'd have been naturally; And, it meant that she would find herself again as soon as she'd learnt that adapting to somebody else is equal to self-destruction. And he was the one to know, as he'd used his profiling system since the day he'd learnt what the word \enquote{thinking} was meaning\dots{}
It dawned on him that it was now not the time to act towards her --- Persistence was the only thing to do. In addition to that, he'd still try to please her as much as he could, but not trying to push her to do something, anymore.

For now, waiting and seeing would be sufficient; but other problems were still lying ahead, waitingfor some decisions he felt incapable to make. He'd been together with P. a long time that day; A really long time. And he wouldn't know if this relationship they were having was still a strong friendship or something more\dots{}
On the other hand, her friend was with them sometimes, and she was also quite nice to him, leaving him stuck in between, as he didn't know what to do now. 
Was this the point of decision, or was it just some wrong interpretation of everything he knew?

He remembered P. doing things she wouldn't have done together with the other people he knew; not commanding him, not offending him in any way that could possibly hurt him, though she knew he was \emph{robust} and could have taken nearly anything. But she seemed to like pleasing him, as she didn't offend him even though he was disturbing her working. 
Probably, she was liking this distraction, but he wouldn't know, as she was some kind of special character who could also act in such a way without intending more than a friendship. 
Why was there \textbf{nobody} who could tell him what was really going on? The only thing he knew was that L.-B. was loving him, which seemed to be a fact that nobody could change --- sad for the two of them, as he didn't like her, even not in terms of a closer friendship. Comradeship, nothing more, would've been the thing he'd have agreed with.

He remembered how he'd recognized O.'s voice --- and that of her best friend --- once that day, while he was sitting in the library again, studying, without seeing one of those two. 
The other time he'd seen O. that day --- together with G. and her best friend --- was something that really happened by chance. In fact, he was with a professor, entering another auditorium, searching for something and talking to that man. Thus, O. and the others were located behind him. He didn't feel something, though he somehow realized he was a bit nervous, without knowing why that was the case. He knew the other people of that lecture, of course. And the moment he turned his head, O. seemed to have been on a lookout for him, as her look met his; just for the fraction of a second. Then, in an order he couldn't reconstruct right now, O., her best friend and G. greeted him, smiling and waving happily.

It was just some kind of game, and he remembered how they'd do the same when they saw that homosexual that happened to be their friend. 
Well, that was everything about that, as he just smiled in return, probably lifting his hand leisurely. He wouldn't remember the details, and when he exited the auditorium again, a last look wouldn't reveal a thing, though O. seemed to be nervous, somehow.

And G. had wondered some seconds before, why he was here and didn't have some lecture he'd have to attend; Well, she'd already found out on her own that he hadn't. 
And O. hadn't said a thing\dots{}

He went back to the library, to join P. and some other friends there. 
Y. asked him something, and he managed to keep L.-B. at some distance of about one metre. Applying his theory of hopes not being fulfilled, this would exactly fit into scheme: L.-B. entered he library, sitting down there, working, knowing that he'd arrive, thus choosing a seat close to his material which he'd left there, together with P. And she would be hoping for some conversation to develop; However, before, when she wished to ask him about something, he'd managed to pretend he was working hard, not being capable of helping her, while then somebody else was offering her help. And he was rescued, breathing out loudly to show P. what he was feeling. At that time, she seemed to be absorbed in her own thoughts, probably thinking about the way he'd dumped L.-B. Well, he wouldn't mind. And he felt that L.-B. seemed to be coping with it, too.

When the lectures were finished for both O. and him, he was walking next to his best friend, talking again. O. was alone, just having said goodbye to B.-B., who was heading with some friends of her for her car. He knew that he'd have stood at some place near to O.'s path if his friend had been gone already, and he felt as if he'd have talked to her, though he wouldn't know any topic. Probably, saying goodby would have been sufficient; However, this way was possibly more effective for the sake of his own future.

O. was gone, alone, lonely, though he was pretty sure that she was still having the same boyfriend. He couldn't help but feel some fractions of the old feelings again, of that small girl needing help, protection; He knew she didn't, but what role was consciousness assigned in that kind of game?

Today, there had been some kind of discussion about the way intelligence was dividing different classes of persons; And somebody had also mentioned that the way one was interested in something was changing the finaly outcome of the work. The people who were taken for the less intellingent would accept that role, not trying to change a thing; The people who were taken for the most intelligent would accept that role, too, not doing something anymore. The people who were caught in between, however, would try to be better, showing interest in everything. 
He was trying to be like this.

Only one who's interested in the details that are surrounding all of us will be able to make some sense of the world; and only if one is capable of understanding parts of it, one can really be intelligent, as talent is all around --- it's just a matter of \emph{using} it.

But we're not here to discuss about things he didn't want to say right there, as he knew it would take most people a long time to understand, while most wouldn't believe him at all; Before he could do so, his experiment should be put into practice, the thing O.'s best friend had agreed to and forgotten about. He wondered whether he'd try to do so with P.; We'll see. 
There's still time remainingto decide on that.

For now, we'll finish with the last important thing he'd done that day \emph{(up to now, that is)}: He'd waved at B.-B. and her friends, while she was driving her car; and then, when he was on his way home, he saw Y. and some of her friends heading for the train, though they would normally have been together with O., in her car. But she seemed to be alone, though he was pretty sure that G. at least was with her.

Be that as it may --- 
We're finished for today. 
Probably, we'll have a look at some lyrics tomorrow --- if time allows me to do so. 
Don't dump me, please!
Tell me what you think!


\begin{quote}
Running \\
was the water \\
in the sink. \\
Splashing \\
was the fresh liquid \\
when it hit the ground. \\
And rushing were his thoughts \\
without control \\
in rising anger; \\
But did he really wish \\
for a dumb mind? \\
Sometimes, he did. \\
But then, he knew, \\
that he'd miss so much; \\
Probably, he'd be happier, \\
if he didn't realize \\
the foundation of fact. \\
On the other hand, \\
he'd always search for it, \\
as this was his sense of life. \\
--- W.G.
\end{quote}

\begin{quote}
He'd realized, \\
that the number two \\
was mostly appearing together \\
with the three; \\
the number of her boyfriend. \\
But a relationship to close \\
is short --- \\
one too distant \\
is not successful. \\
There is no perfect relationship \\
except the one \\
of the two \\
persons \\
which are meant to be. \\
--- W.G.
\end{quote}
