\chapter{Just Exploring}
\label{cha:just-exploring}
\subsection*{Originally published: \DTMDate{2006-02-21}}
\begin{quote}
Hello! Are you still out there?

A short, but complicated day, as it would leave him contemplating about everything that had happened the weeks before; and remembrance is always a complicated thing, as it can capture our hearts without our noticing it.

He was waiting, looking; Just Exploring.
\end{quote}

Let's start with a quote, this time, to explain the heading if you haven't got it's meaning yet: 
\begin{quote}
  Now is a good time to explore.
  --- from a small fortune cookie program
\end{quote}
That was exactly what he had been doing for the last few days: Looking around, exploring the world. In a way, everybody did all the time, and he'd also done so since the beginning; However, he was now free again, being able to look around without any hindrace to his senses. 
Perception unlimited, one may call it.

But he knew he was missing a lot, and as he'd got used to talking to others more and more, his soul was longing for social contacts. 
P. had always been there, and she was now, too.

Something peculiar had happened: Today, L.-B. was after him again, but as she seemed to have noticed that he spend his time with P. in the library, and as he wouldn't change that so soon, she was following him around there, disturbing not only him, but P., too. 
And she offended her.

In a way, she seemed to be fighting, he realized that; but this fight would not be won, at least not by her. 
He was shocked when she asked him why he was always spending his time in the library, and added leisurely why he was always here, \emph{together with P.}. She seemed to assume that she could forbid him to make friends with her, but he wouldn't budge.

He would ignore L.-B. in the most offending way he could think of, giving the shortest answers possible, without any subjective expression. 
In addition to that, he talked to P., who was sitting nearby, turning away from L.-B., giving P. the highest priority. 
But there still was that memory gripping his mind now and then, all the time, that remembrance of O.'s\ldots
\begin{quote}
I remember all my life \\
raining down as cold as ice. \\
Shadows of a man, \\
a face through a window cryin' in the night, \\
the night goes into \\
Morning just another day; \\
happy people pass my way. \\
Looking in their eyes, \\
I see a memory I never realized how happy you made me. \\
{[\ldots]}\\[1\baselineskip]
you came and you gave without taking, \\
but I sent you away. \\
{[\ldots]}\\[1\baselineskip]
you {[\ldots]} stopped me from shaking, \\
and I need you today. \\[1\baselineskip]
I'm standing on the edge of time; \\
I've walked away when love was mine. \\
Caught up in a world of uphill climbing, \\
the tears are in my mind and nothin' is rhyming. \\[1\baselineskip]
{[\ldots]}\\[1\baselineskip]
Yesterday's a dream \\
I face the morning \\
Crying on a breeze \\
The pain is calling \\
{[\ldots]}\\[1\baselineskip]
{[\ldots]} won't you listen to what I'm gonna say \\
{[\ldots]} don't you let me going all the way \\
{[\ldots]} won't you listen to what I'm gonna say \\
And I need you today \\
{[\ldots]}\\
--- (I guess you'll know this song --- it's not that old, it's from 2004; thus, there's no need to give you the title)
\end{quote}
The last illusion of the past that had not yet been destroyed, as he'd just broken the connection of those feelings with O. \emph{(or rather, locked all events connecting her to that feelings away in some distant part of his brain)}. However, he could consciously access everything that had happened; Only the perception of emotion --- connected to O. --- was blocked.

And this left him with the powerful feeling of longing, as he'd lost something --- somebody --- without realizing \emph{who} had been that person; Nevertheless, this was the only way for him to cope with it, in the end.

And time would probably do the rest, if it was as powerful as all the \enquote{great men} kept telling everybody.

Music had once again become his substitute for something real; With this powerful language, his desperate longing didn't hurt as much as it had done before. And then, he understood the other sign he'd seen that day without knowing what it could mean: A sign \emph{(a traffic sign)} which in reality was presenting something completely different \emph{(in fact, some small town which just sounded quite equal to the word he'd read)} seemed to show him the word \textbf{\enquote{Betrayal}}.
But not in his mothertongue, but in German.

That not being peculiar enough, he'd realized that this sign was ambiguous: It could also mean that he'd denied his feelings for P. in some way, and his feelings for her friend, not to forget about the not-so-positive feelings towards L.-B. In fact, he kept betraying himself, and he felt sad, though --- or because of --- this was part of everybody's life.

Later that morning, when the lectures would be finished for that day \emph{(they finished a bit earlier on Tuesdays; however, there was enough work to do in the afternoon)}, he'd wait for the bus to arrive again. When B.-B. was arriving with some other girl, passing by about 10 metres in front of him without noticing he was there --- because she kept talking to that other girl --- he'd thought for an instance that this other girl was O., at least, when the two of them had been about 30 metres away.

Which, in the end, told him that his recognition of her was deteriorating. Not quite an hour ago, he'd seen her from just a metres distance, waving at nobody in peculiar, and he seemed to be the only person returning her smile. Nevertheless, she was not looking at him, but to some point in the air several centimetres next to his head; He was pretty sure that nobody in that direction would give back or at least realize the happiness she was emanating.

He had, but she seemed to pretend not to realize; G., who was normally less abled to realize such subtle communication \emph{(at least, that was the way he'd thought up to today)} was greeting him every time she was passing by, even if it took \emph{him} some time to notice her. And she didn't mind that her boyfriend was walking next to her, just smiling at him, as he knew him, too. 
Which left him realizing that this was some sort of friendship, indeed, though he'd always thought to be more linked with O.

She seemed to think differently, however. 
Or probably, she wasn't seeing things differently, but still felt the pain of him not having reacted on her\ldots\\
\textbf{CUTOFF!}\\
This wasn't true, it couldn't be. Otherwise, if they were really meant to be, another chance would arrive, and then, he'd grab it as soon as it was there. 
But we don't want to talk about O.

There are other persons interesting enough to have a look at, and when the next weekend arrives, there'll probably enough time to focus on his way of judging O. again. 
For now, we'll sum up the other things that had happened this Tuesday: In the morning, he'd reserver a seat in the bus for another girl he'd just talked to several times. She was quite complicated to deal with, in some way like O., but completely different; However, she wasn't the kind of character he'd love.

Nevertheless, a friendship seemed to be growing, and he was happy that his profiling system did even work with people others had once called \enquote{The Evil One with the Glasses}. 
A nice name, as it described the way she appeared if you had never passed through that border that isolated her from the world out there; and below, she was different from most of the others, as she seemed to understand some details of life most people didn't. As we've already learned, this was one of the ways intelligence could manifest itself.

The next interesting thing was the time in the bus, when he was going home; he slept, as he'd done once before he'd known O.; when he'd got to know her, he'd always be awake and wait for her or listen to her talking to others. But O. wasn't there, and things had changed\ldots

Sleeping was one of the most useful things to do when you're in a bus, as time seems to flow faster and finally, you feel refreshed when arriving. 
Before the bus reached the place where he was living, the driver was talking to him, this time for the first time since years. 
But his character had changed, and he was much more open-hearted, taking seat in the front to be able to understand the terribly pronounced sentences of the stranger, trying to make sense of the words that reached his ears.

Finally, there was some kind of communication, and he liked this social exchange. 
The rest of the afternoon, he'd be pretty alone again, left alone with his parents and his granny, and feeling abandoned in some way. 
Abandoned; he'd felt that way once before, this very day; Yes, when B.-B. was sitting in her car, not igniting it for several minutes; and he'd be in the bus before she'd gone. Probably, she was waiting for somebody; and he was alone, and nobody had noticed him.

No! One girl had waved at him, when she passed by on her bike. But this was not some real kind of waving, as she'd just raised her hand a bit, while he had really waved, something he'd copied from O. 
For now, the day was finished. 
Hope you'll wait for more to come\ldots
What do you think about all this? Please tell me\ldots

\begin{verbatim}
Masses huddling around oneself 
    lonely      abandoned 
          killed 
           dead; 
that's the way life is going. 
--- W.G.
\end{verbatim}

\begin{quote}
Is fire \\
stronger than water? \\
Is a blizzard \\
more destructive than a flood? \\
Is love \\
more powerful than friendship? \\
Who can tell \\
without killing part of himself? \\
Who can disturb the balance of live? \\
I don't think anybody can, \\
without losing his balance of life, \\
and himself, \\
in a flood of fire. \\
--- W.G.
\end{quote}
