\chapter{No Time}
\label{cha:no-time}
\subsection*{Originally published: \DTMDate{2006-02-22}}
\begin{quote}
Still there? Well, I'm in a hurry today; this'll be a short one!

You may ask me why I'm posting something \emph{at all} if there's no time to write something long; well, some interesting aspects have just come into being, and I don't want you to miss them. Hope you share my opinion!

Typing as fast as he could: No Time!
\end{quote}

This time --- as there is no time left --- we'll focus on the really important points. 
This morning, the bus was so late that the girl he'd normally reserved a seat for wasn't there; she had already gone. Nevertheless, when they reached university, his bus had catched up, and the two of them walked next to each other on their way, talking. And finally, when the first doors came in sight, she said: \enquote{Ladies first!}, after having opened it. Well, she continued to do so with the others, and he kept smiling, even laughing about it, as he knew she was a bit sarcastic.

Another memory flashed into his mind: O. had once opened the door for him, though it had normally been the other way round; and he'd thanked her, thinking about this fact for more than some minutes. But this time of too much focus on such details was gone; However, there were still many things of less importance worth thinking about. 
That girl who'd opened the doors today: One of his friends had asked him what he'd do if he was to be her perfect partner according to some test, and he'd evaded the answer, pretending to give a negative one, though he was pretty sure that he'd indeed never be together with that girl by means of more than friendship.

L.-B. was still trying to poke through the shell he'd errected, but she wouldn't succeed. And P. was trying to protect him, as she knew what a hard time L.-B. was giving him. 
This morning, he had been pretty sure that P.'s friend was liking him more than P. herself, and she'd given him her texts she'd written in her spare time, and even some works she'd done for university; in a digital form, of course, using the same device he'd used.

P., however, seemed to act quite similar, though she didn't give him something like that, but talked to him most of the time. 
His life felt once more not empty, as he wasn't caught up in the silly and childish talks of the other boys. However, he'd also noticed he'd copied some sounds P.'s friend liked to make, without really having realized that; but he kept using them, and felt that something was changing.

But more news were yet to come: Another girl, about which we've talked a lot \emph{(a good friend of one of the protagonists in this story)} had just found a new boyfriend, somebody he knew. Most people --- including O. --- thought that this relationship wouldn't last very long, and he agreed with them. 
Memories\dots{}

Yes, he remembered having explained some scene that had been going on some time ago. That girl was sitting next to that boy, and he had been pretty sure that she'd had a boyfriend at that time; However, she would have to be single to make friends with him. That moment, when this boy had touched her belt, had occured to characterize her being dealing more leisurely with such things --- now, it seemed to have been the event that foreshadowed what was to come. Somehow, he'd known but not believed it, as it seemed to be too improbable; Now, he knew, and it took him some time to realize how long he hadn't really talked to her. And  every time she was passing by, a smile or even waving her hand was something he'd see and return.

The same way he did with everybody, though O. seemed to have ceased to do so, while G. was doing that the more. 
This morning, he'd seen O., greeting her, while she also greeted him; but when he followed her gaze, which was again strolling way up and down the wall without looking at something in peculiar, he knew that she didn't dare look into his eyes. Which would mean, that she had once loved him\dots{}

And this afternoon, when she arrived at university for some party, disguised, he could just make out G. and several other people, but not O., though he knew she was amongst those people who were passing by. Another boy was standing next to him, talking now and then, looking at the crowd, too; and O. suddenly began to look in their direction, though she was walking some metres away, and greeted them by waving and shouting. He couldn't make out the point her eyes were fixing on, but it seemed that he'd caught her look for some seconds. And it even took him some second to realize that it really was O. who was passing there, as he'd never believed her greeting him; and he didn't believe that she'd wave this way towards the other boy. G., however, really smiled at him, waving a bit, not shouting, but always repeating this gesture when meeting him somewhere, as if it was some kind of reflex\dots{}

When his opportunity to go home would not have arrived so late, he wouldn't have seen any of it, as his lectures had been finished already, and the same party O. and G. were attending would be repeated the next day. Then, he'd be there.

Chance had showed him once again what it could do. Life was not really predictable, however, one may agree to the leading signs fate is presenting to everybody. On the other hand, one can't know if the outcome of following them will finally be positive or negative; Nevertheless, trying is the only way to find out, and this process is called life. 
There was no time to do more: His head was feeling numd, and only some programming and some writing would relax him that evening; even the time to explore the text of P.'s friend was limited, and he could just have a look at the amount of material he'd received. This weekend, he hoped, he could have a closer look at it.

For now, he was tired to the death, having slept far too short a time, and having worked too long; soon, he'd find some hours to relax, and then, he'll probably write some more texts. 
This day will be finished in two hours, but the next one will probably give some deeper insight; however, the lecture on Monday together with O. would be cancelled. 
Please look forward to the next one\dots{}
And be so kind to give me your opinion\dots{}

\begin{quote}
Fantasy destructive, \\
memories killing, \\
thoughts explaining; \\
or just making things \\
more complicated, \\
leaving you stuck \\
at some place \\
you don't want to be. \\
--- W.G.
\end{quote}

\begin{quote}
The power of your soul \\
is represented by the power \\
a look of you can unfold; \\
and if one doesn't dare to look back, \\
one fears to do so, \\
having seen you're dangerous --- \\
and interesting. \\
Toxic; \\
intelligent and just. \\
One's eyes will tell you \\
about the power \\
of one's soul; \\
be careful \\
when looking into a mirror: \\
Don't be afraid of your innermost parts. \\
And dare to return the gaze of others, \\
to find out about yourself. \\
Life is full of danger, \\
and one is to accept it, \\
to deal with it --- \\
and to be lucky, \\
saturated and content. \\
--- W.G.
\end{quote}
