\chapter{Ultimate Betrayal?}
\label{cha:ultimate-betrayal}
\subsection*{Originally published: \DTMDate{2006-04-04}}
\begin{quote}
Hi!

Nice to see you're still with me\ldots

This time, I'll just give you a short report on the recent events; soon, there'll be more time, but this will be accompanied by the fact that not real information is to come --- probably. A new story is to be introduced in the next weeks, probably even in the next days; OliFre is still working on the new system, as he tries to do something perfect, in quite the sammer manner I always like to do things. However, this takes some time, and I know that something perfect can grow forever.

So: Please be patient, go on reading --- and tell me about your thoughts!

Was this the: Ultimate Betrayal?
\end{quote}

Yes, that was the thing he was wondering about; what should he do?
But before we start thinking about that, you as the reader shall be given some more information on all the things that had happened in the last few days after a quiet weekend full of work. 
Thus, we shall start with Monday.

The day, when he saw O. once more, and this time, she was not as sad as she had been the last time, but full of joy, as she'd always been. He would not be able to fetch any more information, but this time, he would be able to talk to her for some minutes, and the conversation would be \enquote{The Way Old Friends Do}. For those who don't know about the song which is entitled with this five words: It's about the end of a relationship and the beginning of individuality once more. Thus, it was a conversation between friends; but we shall first have a look at some more details. For a start, she still accepted his sitting next to her, and seemed to enjoy it; he was remembered of the evening when she'd told G. that she would like to sit next to him; the day when he talked to her very long, as none of her \enquote{real} friends was there; the evening when she would even be together with him when her boyfriend arrived\ldots

Then, he'd felt it was some kind of friendship, though she was still kept in the thought that there was something special between the two of them --- which was true. When it came to food, she seemed to be sure that he'd eat the same things she did --- this kind of similarity was something she'd figured out, and he knew about that, though he was not completely the same concerning all those things. Still, it was something special\ldots

It had gone. And now, he was just sitting there in front of his computer, this time with headphones on, English music ringing through his brain, washing the thoughts and aligning all of them in a row now and then, swirling them around the next moment, just to sort them once more, giving insight, emotional reactions and making one stupid, sometimes. Music was a dream, but this was part of evolution: The good things would be sorted out, and the others would die. Music was the catalyst for the evolution of thought.

And he just sat there, listening to it, typing in a horrible speed, disregarding the fact that it would probably be something that would influence the condition of his keyboard and his language in a negative way; writing a text, a book, his Life in a Nutshell to remember HER and to cope with that memory. 
Poor being, he was. 
Rich in emotion, that is.

And he who knows and conceives in an extraordinary way will always be hurt because he is deemed to feel immense happiness, resulting in gigantic pain. 
But we should continue with the reality, or the dream of it, as there's nothing out there which could decide whether our reality is a dream or reality; how could we dare to call the things we conceive reality without being able to prove it?

While he was sitting next to her, there was just the normal amount of a word exchanged now and then, a hearty laugh and a smile. Still, he didn't dare looking at her for a longer time. Once, she'd talked to P., who was sitting behind; he wondered that the two of them were really talking to each other, as he'd never realized that they \emph{could} or \emph{wanted} to do so. But there was nothing more than the words that were necessary; then, she was also talking to him.

About a book that he'd always wanted to read, but never done so. It was still located somewhere there in his house, but he felt he would not have the time to read through it. She had to, and this seemed to be one of the first books she really liked and \emph{wanted} to read, as it was crazy.

He knew that he'd like it, too, but he felt that the real interpretation of it would probably not be the result of her liking it; and this was his motivation to read a good book. 
Yes, he was different. He'd always been, and he would always be; his core was not to change. There was no such thing as a flashable memory in a human being, and it could not be updated, but just be changed by adding some amendments or changing the things that were there; but the way it would develop had been decided long ago.

He breathed in, looked around --- and remembered once more the rest of the conversation, which was not really important, as it had just been about that book, lacking information and anything of importance to us. Today, he'd seen O. once more: She'd just been standing some ten metres away, and soon, she would be passing by. Though he was talking to somebody else, his eyes were following her in fractions of a second, so one may not notice it at all or interpret it as a sign of nervosity. There was something interesting; when she had just reached the point when she would be closest to him, her head turned a bit so she was half-facing him, though her eyes seemed to be pointing at some point in the middle of the air, looking down a bit. Probably, she was just trying to listen to somebody walking next to her, but he was pretty sure that there was nobody talking to her; on the other hand, she may have been just thinking. He felt that this was all wrong. It was some reaction that had not been made consciously; she had been reacting on him, and though this would probably never be the basis for a relationship, there was something that bonded them together, whether they liked it or not.

He'd noticed just now.

This was a bond he could not break, but he wondered whether he could --- and \emph{should} --- try to forget about it, which would make it even stronger --- if he was right, that is.
This would be the Ultimate Betrayal.

But there was something else that may also be called like that: P. had today told him something. It seemed like he could not deny it, and he couldn't. She'd promised him a present, and hat she would fetch him some day from his house.

He didn't like that, as he was \emph{different}. I guess you've already figured that out: His profiling system was now changing, and he was adapting, but the innermost part of his character would stay the character of an hermit, until there would be the special person to change that, and he was very sure that P. was \emph{not} to be that person. And he did not want to be forced into anything, though it seemed that he'd never make a decision on anything.

Indeed, he was slowly gaining an opinion on everything, and this was a hard processfor an hermit. He felt it was necessary, but he knew it would be a strain on his life itself, as it would threat the quality of his profiling system.

Thus, he needed to get rid of this forced offer. He told his mother about these offers, but nothing more about P., and she was already not liking her, as there was some story that had taken place in the past; P. had said something she had felt, but it was too early to appeal to him, and his parents had heard and interpreted it wrongly.

Now, his mother thought she was after him; he would not be able to deny that, however, though he'd rather think that she searched for a strong friendship at university. But it was this insight of an hermit in the real meaning of things --- even if this insight was probably just an illusion, but it seemed to be true for the person itself --- that separated him from the world. He could not escape this so easily, and he did not want to lose it.

This was the special thing about P. that had taken place just today; now, he just sat there, his fingers racing in the speed of his thoughts and his eyes being caught by the special light that illuminated his keyboard. Probably, this would do them any good, but the felt it was guiding him towards new ideas.

L.-B.\ldots
Something quite nice was going on about her. One girl from university was slowly becoming her friend, and when the two of them were together, L.-B. would realize the stupidity of staying with that boy who seemed to be so boring --- when she was there. This friendship helped him to get rid of her, but he knew that it would probably not last eternally. However, it would help him.

His brain was empty now once more, but he knew that this was just a result of the amount of information that had been transferred into these lines; it would be full of chaos in some minutes once more, as he was still alive. 
I hope you'll check for more to come soon, as I'll try to tell you more as soon as I'm able to\ldots
Just stay tuned\ldots
Any opinions?

\begin{quote}
An hermit \\
knows. \\
An hermit \\
feels. \\
And what he knows and feels \\
is the illusion \\
of his life \\
he can't escape. \\
--- W.G.
\end{quote}

\begin{quote}
Wild \\
is the course of nature \\
and life. \\
Strong \\
is the wind \\
that leads our lives. \\
And the only control there is, \\
the only reality there'll ever be, \\
is the rule of chaos. \\
--- W.G.
\end{quote}
