\chapter{Dreams out of Control}
\label{cha:dreams-out-control}
\subsection*{Originally published: \DTMDate{2006-04-13}}
\begin{quote}
Hello!

I'm glad you're still with me. This time, some details have hanged my way of thinking without me being able to control it --- but find out for yourself!

What he experienced were: Dreams out of Control.
\end{quote}

Several days had gone by, and what had happened were just details, tiny little things; but details are the most influening things there are, as they appeal to our unconsciousness in a subtle way, even if you noticed some of them. These details are the utilities of fate to lead us to our destiny. 
\begin{quote}
A routine will turn into an enchanting adventure. \\
--- from a small fortune cookie program
\end{quote}
Right now, he was wondering what this routine would be; it had to be enchanting. And then, he realized that this sentence the program had told him on Tuesday went very well with the one he'd received on Wednesday: 
\begin{quote}
Look for a dream that keeps coming back. It is your destiny. \\
--- from a small fortune cookie program
\end{quote}
Dreams; the most subtle way to influence a human being, as we often forget about them without having realized even the tiniest part of their real intentions. He had watched his dreams. 
And though he'd never thought about O. before he'd fallen asleep, she was there. As a consequence, he wondered why she was there, and there was no \textbf{logical} explanation. The only thing he'd remembered to have dreamt of before today was the face of O.; there had been some action around her, he felt he could even remember having talked to her, but tis was lost, as he'd just remembered it once and then forgotten about it.

Today, on Thursday, he went through his dreams more cartefully. After the \emph{normal} things that would be explained by sorting in his memories, the things you'd forget about seconds later, there was O., surely enough. And he could also remember some parts of that dream.

He sat in the bus, and O. was just in the last row, him sitting one row in front of her. Somewhere, there was G., too. Most peculiarly, he had not dropped his bag on the seat next to him, so that it was empty.

When he recalled this scene of his dream now, he realized that there was something familiar about it; this scene had been burnt into his memory. He had indeed sat right there, and O. and G. were placed in exactly these locations. This was the day when he just sat there quietly, his love for G. still under development, and him asking G. a single question about a book she was holding. He didn't know it, and she'd told him, laughing, that it was \textbf{important}, in a way, as most people read it; \enquote{cult} was the exact word she'd used, and he could still remember it. In addition to that, he could still remember where O. had been, though he had not consciously felt his love at that time.

And what had happened next in his dream was something that had never happened at all, while this scene was blacked out in that video he'd been showed by his own mind at night.

O. and G. would exit the bus, but in the dream, his sight would be totally different: G. would not be important, but O. woudl stop next to him, carrying many things; as the bus stop was still far away, and as the seat next to him was empty, he did something he'd never have done \emph{(at least not at this time, because he was still young and had not yet learned to deal with people without fearing everything)}; He asked O. whether she wouldn't like to sit next to him for the next moments until the bus stopped.
She did.

The two of them talked a bit, and they were happy; at this moment, his dream broke off.

The most interesting thing was the fact, that O. had always asked \textbf{him} whether she could sit next to him. But this dream had told him something by making this contrast so apparent: He should have not only agreed wit O., but shown signs of liking her. He should have returned her gestures. And he should have done so long ago, probably even before she'd started to do so. 
But time was gone; so he was left with sorrow.

Today, he'd received another phrase by that program: 
\begin{quote}
Others are anxious to get to know you better. \\
--- from a small fortune cookie program
\end{quote}
For several minutes, he'd hoped that this would point at O., and that it was to say that she was alone once more; then he'd realized that there were too many people there at university that would like to know him better.

Too many people he would \textbf{not} like to know better, people like L.-B., or P. whom he liked as a friend --- but nothing more. 
He realized he'd used P.'s and L.-B.'s name in one sentence, and felt the shiver of logical interference in his emotions. 
But this was the way it was. Things changed, all the time.

This afternoon, he was driving once more; he felt reminded of O. by several things now. The road, and the way he was driving, seemed so similar to her way; or, at least, to the moment when he'd been together with her in the car. All those villages passing by out there, only going through them without being interested in these centres of life, as the real centre was somewhere near\dots{}

It had gone. She had gone. He'd even imagined him talking to her boyfriend that day, and he'd thought he \emph{had to} meet somebody he knew out here; he didn't. Nobody was in the city he had finally arrived at; masses of people were, but nobody he knew.

Slowly, he figured out that it was all about sorrow. Sorrow was the source of his power, as it was the leak, the thing to keep him down, the thing that was below zero and kept everything else above it. Yesterday, he'd heard that song once more; that song he liked, and O. liked too, while most other people of their age didn't. Why hadn't he told her\dots{}?

What he heard was an imitation of the original in another language being played in the radio of his mother; then, he'd started playing the original on his computer, and he was transporting things up and down the house while his speakers were crying.

Inside him, there were tears, too. Though they had been bound long ago, still\dots{} sorrow would remain. Forever.

He wondered what O. was doing; at the same time, he wondered whether he could use a similar logical technique that had worked with P. and G. to forget about O. He felt he could never do that. What was next? He'd listen to all his music once more, even if that took hours; that was something that would make him sad and depessive, and this mood would probably be the basis for happiness. And, he promised this one, he'd start working on all those things he'd never done; there was a lot to do.

Probably, this would be the basis for change. 
We all should wait to find out. 
So, please come back here\dots{}
And tell me what you think!

\begin{quote}
Drops of fire \\
falling down \\
from heaven to hell. \\
The world in between, \\
sometimes full of light, \\
sometimes full of pain; \\
None could win, \\
neither water, \\
nor fire; \\
and if one did, \\
both would be destroyed. \\
Evil was nothing without Good, \\
and Good nothing without Evil. \\
--- W.G.
\end{quote}

\begin{quote}
Tears \\
can be wet, \\
can be calm, \\
can be silent, \\
can be loud. \\
But all tears are a sign \\
of emotion. \\
And they are all made of water, \\
the symbol of life. \\
--- W.G.
\end{quote}
