\chapter{Cutting Close}
\label{cha:cutting-close}
\subsection*{Originally published: \DTMDate{2006-04-26}}
\begin{quote}
Hi! Yes, I'm still alive...

Too many days had passed, too many things have happened --- and I've probably just now figured out what I was to do. You'll be able to find out when you continue reading!

He was: Cutting Close.
\end{quote}

The two weeks of absence from university had been finished on Monday, and great changes came along with that. 
\begin{quote}
Someone has complimented you today in your absence. \\
--- from a small fortune cookie program
\end{quote}
This quote had been given to him on Saturday, followed by this one: 
\begin{quote}
A pleasant surprise is in story for you. \\
--- from a small fortune cookie program
\end{quote}
on Sunday. Finally, today (on Wednesday, that is) he'd received the following: 
\begin{quote}
You will be spoken well of by somebody you look up to. \\
--- from a small fortune cookie program
\end{quote}
Now, he was left to cope with these, and though he'd already figured out that those lines were repeated as he'd already seen nearly all of them, he felt that they were important, nevertheless. You may decide in which way they are when regarding the following events: 
We'll begin with Monday, the day of the most interesting value for him. That Monday, he sat next to O. once more, and as he'd now realized that he hadn't thought of her all the time anymore, he \emph{knew} that she'd talk to him for some longer time. At least, that was what happened, and later on, he used this explanation for it. So, you may ask about what topics the two of them had talked; as his time off university wasn't that interesting, she'd told him about her vacation, and he'd listened carefully. But before that conversation took place, there was something even more interesting: She didn't have a good pen to write anything down, and as he noticed she was searching for one, he offered her his ballpoint. She accepted gladly after having told him she'd need it till the end of the day --- at least. 
He didn't bother.

She realized how wonderful this pen wrote, and he explained her that the mine was the important thing, as it was also included with more expensive ballpoints. Realizing that it was also included with less expensive ones, he told her so, and she answered that he was contradicting himself. He didn't come up with the answer he'd figured out later: That life was contradicting itself. Thus, he didn't say a thing, but smiled when she did.

Then, some minutes later, the real communication began, and he just became to know some interesting details, which are not worth to be mentioned here, but which are important to him: Details about her holiday, her being invited to a party and being probably unable to go there and several other things. What he noticed, however, was the fact that when her best friend was talking to somebody else, she chose him to talk to. And his happiness about this fact destroyed more beautiful minutes, as the positive events had just risen to a new high.

The day before that Monday, he'd seen a picture of her --- quite an old one --- and just viewed it with a tiny viewer on another screen. Then, there was nothing special about her anymore, and he could not feel that power that she was emanating.

This memory and the new events were the basis for his new development. The trigger was the thing on Tuesday, when O. gave him that pen back, stopping and asking him whether he wanted to have back his ballpoint now. He didn't deny to wish for that, and she began searching. When she didn't find it directly, he told her it wouldn't be a problem to give it back later on, and told her he'd already taken another one with him.

She told him the same and found it. Handing it over to him, he asked her how her exam was, as he'd heard that this one hadn't been so beautiful. She was happy, as she'd received a mark that was real good. 
Thus, he was happy too. But when another boy arrived, the same one we've mentioned several times before (the one who'd given a present to O., while he'd probably never given one to his own girlfriend), he wondered about the words that boy had said. \enquote{What's going on here?}, were those words, and O. had responded that they were \enquote{dealing}. 
That was the way she was, but on the other hand, it showed him the way this boy was, though he couldn't be sure about that. 
So, what was this new development that resulted from all these details?

He decided to go on with listening to that old music he had. He needed to 'Cut the plant of his love Close to the ground', so that the seed would still be there; but the memory --- all memory --- had to be put away. He was happy he'd stored it right here, in these texts, though he felt he could never really forget about it. But he needed to; he must become sad and hopeless, and he had to forget about his love completely. This was the only way, the only possibility to escape this vicious circle, as he could only make her become his friend again if he didn't care. Only then, fate would allow the two of them to stay together.

This would be a very hard job to do, but he must take up to it, or at least try to do it, as the hour of happiness was always preceded by the hour of disaster. 
He wondered whether a human being was characterized by the diversity of good and bad in his life, and he tried to figure out whether unhappiness or happiness would be better. 
But as everything was complementary and would eradicate each other, as both had to appear in the same amount for the universe to stay stable, he realized that there was no difference: Good and Evil were the same things. The only variable thing there was was the so-called \emph{amplitude}, and he wondered how it was controlled and whether his plan to rise it enormously would work. 
This meant he was to become totally sad and hopeless now, and he should probably also stop continuing this project for some longer time.

Then, he wondered why he hadn't asked O. why she had still not had the possibility to receive his messages from that contacting attempt long ago; but he felt that he had forgot because he \emph{knew} it was hopeless. This was the first step.
And there was hope, a light burning down the road that would safeguard his treading the right path, though he must do so without knowing about that light being there and without realizing it's meaning; this light was the fact of O. having said something on Monday.

When he'd told her about all that pictures of students that had been in the papers, she'd told him the following sentence: "Yes, I've seen \textbf{us}". The way she used that word implied something, which was at least some kind of friendship; and it told him he was really treading the right path.
He had to continue.

P. was now coming close: She and her friend were talking to another girl, when she explained one mustn't care about others thinking that two people of opposite sexes who were friends were a couple; and then, she took the example of the two of them, but the way she explained that and the looks she threw at him implied something more.

Her friend was still smiling, and our protagonist realized that P. was explaining this thing \emph{two} times, watching out for his reaction. 
But he didn't react.

He would not let her come close --- he was shut in himself, and this nutshell would not be broken by that girl. 
Her friend had given him some more texts, and he would read them, of course; but not now, as his time was really limited to something around nothing. 
But he needed to write, and he knew that he'd now be able to deal with the Nature of Being; he knew the way he had to go. 

The way of hardship is the only way to happiness.

He just had to rise the amplitude, and everything would go better and worse. While that did not necessarily mean that O. and he would become a couple, it was the best way, and he really felt that. 
He'd taken the ballpoint into his hands that day, and done something esoterical with it; a flow of energy from himself was merged with the energy O. had left. Even if that was just an invention to make people buying books and giving money to others, he felt something.

The two waves of energy seemed to join, and waves of shudder suddenly ran down his spine, as if these two energies were in sync. He didn't care if that was scientifically possible. He just felt it, and this made his decision final.

He had to do the right steps. 
He had to stop writing for some time, and invest more of it into other projects. Probably, he'll still continue writing here, but not that often anymore. 
And we'll leave out O. for some time.

This day, he stood next to R., and she was talking to some girl whom he could have helped, but didn't because of a lack of time; she needed some help with her work, and a professor had asked him to help her, but he'd explained this man that there was no time to do so.

All were unhappy about it: The professor, the girl and himself. He had rarely denied to offer his help, but he knew he had to. 
And he had to pay for it, as R. rarely talked to him but focussed on that girl --- she was new, and had to be found out about.

R. would still be there some weeks later, and he knew that there was some pre-friendship connecting them; that was all he wanted, a friendship, and all he could ask for. Probably, this would even be the possibility to help his best friend, who was loving her.
But this would all happen later on, \emph{if} it would happen.

Y. would be there tomorrow, and he'd given in to her asking him for his help. This would be no problem, though L.-B. was going on his nerves probably more than ever, and stole his time. 
His best friend seemed to know who O. was for him, as he used some small phrases with special accent; he realized that, but he was still decided not to tell him. Probably, this problem would be solved soon, if all of them left university the next year. 
We shall wait and see what is going to come.

Please come back here, and tell me what you think; I'll try to continue writing as soon as possible, also concerning the other project\ldots

\begin{quote}
Tears could be wept, \\
of joy and sorrow; \\
Hope could be kept, \\
of life and destruction. \\
And all is the same to us: \\
Each hope, each tear, each cry, \\
each memory, each discovery, each word, \\
all that is spoken, all that is heard, \\
all that comes in and goes out; \\
As for happiness we must pay with pain, \\
and for pain we'll be granted happiness; \\
Paying is granting, \\
and happiness is pain. \\
--- W.G.
\end{quote}

\begin{quote}
Sorrow, \\
sweet surrender, \\
happiness, \\
pain, \\
love, \\
bitter victory, \\
sadness, \\
healing. \\
Contrast is life, \\
and life is contrast; \\
Control one of the members \\
of each pair, \\
and you can control your life. \\
Loving so strong you feel dead, \\
to receive the vividst of love; \\
Fighting till you die, \\
to win your life; \\
Boring yourself to the enc of your life, \\
to be entertained to start living forever; \\
Starving yourself to death, \\
to gain food for thousands; \\
It all is the same, \\
there is the same level of contrast, \\
the same amplitude \\
about it; \\
you just have to decide for that, \\
and you can control your life. \\
But the equilibrium \\
is not to be changed. \\
--- W.G.
\end{quote}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_First_Era.tex"
%%% End:
