\chapter{Introduction}
\label{cha:introduction}
Hello!

I hope you're still the way you have been before. The last months have been full of changes, and most were'nt good, though there are few things that have not been sorted out in some way. This first post is just to give you an idea of what has happened; It's a Preface, and the real story will be continued in the next posts that are to come, less often, but still somehow regularly.......
I'm glad to see you're still with me, and I want to thank OliFre for his further work on this system that makes the presentation of my texts really unique. I hope you feel the same way. 
Still, no opinions in any way have arrived, but he who wants to be understood has to be patient. Now, I can't do a thing but continue, and if not for anybody out there, then at least for me myself. 


[u]Another beginning:[/u]

[b][u]Preface[/u][/b]
YOur first question may probably be: Why "Second Era"? What has happened of such importance? 
Be told that loads of things have changed. Even if it's not a really new chapter of life, it's a new character and atmosphere that has developed in the world around me, influencing me and all the others around me. Though I feel that most things didn't work out the right way, I'll leave the final decision to you....... 
In the following few lines, I'll try to regenerate the atmosphere that accompanied my writing for so long hours in the "First Era". The real contents are to follow later on, so please be patient. 
Few people have realized the way the world is working, and those who think they have haven't. Only those who want to forget about all of it know what's really going on. This is what you'll find out in the "Second Era" when accompanying Wilkie Goldentongue once more. 
To give you an overview: His complete character had been changed by external suppression. The few people he trusted, and his so-called [i]"friends"[/i] had betrayed him in a way that now seemed to belong to their normal way. He wondered whether it was really he who had changed, but you can find out about that by yourself when this "Second Era" starts growing. In the beginning, there will be a summary of the key events; Of course, you won't miss any details. 
One may want to ask Wilkie about O. and her boyfriend; they still seem to be a couple. Had Wilkie managed to forget about her? No, he hadn't. Not until some days before that post, and then, he didn't kill her memory by himself, as she was doing it by changing to a person he didn't recognise anymore as the once beloved "O.". It was a major change, quite the same change that had taken hold of his surroundings. 
Still, things are changing. In a way, he was in love with O.; but she didn't exist anymore. He wondered what would have happened if they had found themselves to be a couple earlier; how would he have reacted now? Would she have changed in the same way, was it her boyfriend's fault, or was destiny the cause of all that forces of destruction? 
A cruel cold got hold of him, in a physical and psychical way, for he tried to replace the magic that had been lost around him. He was exhausted in a deadly way. 
Only few constants had remained, among them P. and some of her friends; He was now trying to address people he felt to be interested in cooperation, and the number of these had shrinked, approaching zero. Few of his old friends were among them. 
But he knew he could be successful without them. Even if he was left alone, he had everything he'd need, as he knew more about life than most of them. But if this knowledge is something worth to own is a different question, as ignorance may be a very wise counselor. It was not only O. who had changed him. 
The world had changed, probably to change him in her turn. He had changed, too; But who can judge which change was more positive? 
It's your's to decide, and your's alone. 
More information is to come soon, be prepared for shocking realities and truths you may already have experienced in some other way. 
To be continued...
This month, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

Life can be the achievement of wisdom - 
or an expression of happiness. 
Somebody ignorant showing happiness is happy; 
somebody wise showing happiness is sad. 
Only one who trusts the ignorant may find happiness; 
but only one who trusts the wise may realize the truth. 
[i]W.G.[/i]

Have you seen the star? 
Now, it's gone. 
It's not to return again. 
Happiness is temporary, 
and so is sorrow. 
Only emotion is eternal, 
and the change of it is the thing 
we simply call life. 
Can you see the flames? 
The burning houses? 
The fleeing creatures? 
This is emotion, too. 
Matter is an expression of thought, 
and we are in the middle of it, 
realizing less than a thing. 
[i]W.G.[/i]
%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_Second_Era.tex"
%%% End:
