Hello! 

A shocked, terrified and crazy hello. Things had happened that nearly were beyond my understanding, but I know this is to be. Things that turn O.'s life into a tragedy --- from my point of view, though this might be accompanied by temporary or even long-term-happiness for her. However, this was the last, final and inevitable proof that the person he had taken to be O. wasn't this person anymore. She had --- finally --- gone, if she'd ever been there. 
A distorted image is all we can grasp when looking at somebody else --- and it is often far too late that we realize that the plain image is not the same at all. 
We shall start now sharpening our view to see the image that has been hidden behind the fog of love for so long. 
Raise the curtain, and let the plays begin! 

[u]The tombstone of O.:[/u]
\textbf{[u]Requiescat in Pace[/u]}
[quote]
R.I.P. --- The last thing we see 
of a human being; 
and whenever that might be --- 
in spite of our seeing 
before this tragic loss 
of something once so living 
we must feel more distant 
from that person --- 
beloved or not, 
human or God, 
matter or emotion, 
as hate or devotion; 
Your mind being ported 
to an image even more distorted, 
or clearer to extent unknown; 
The seeds of memory 
finally sown. 
[/quote]
The person once called O. with love had gone, being replaced by one of the empty shells we see walking everywhere around us. \emph{They} do not look, \emph{they} can not see, \emph{they} can neither hear not witness anything their senses reveal to them. \emph{They} are controlled by something they can never control. 
\emph{They} are lost. 
And \emph{they} can not be rescued --- not in time, because they shall refuse such rescue. 
Maybe, he was one of \emph{them}, too --- but he felt he wasn't. What he didn't know was whether O. had always been like \emph{them} somewhere inside --- He wondered whether his mind had only imagined her to \emph{see} what seemed hidden for \emph{them}. The tiny details, the wonderful sensations of single moments whose existence others wouldn't even realize. 
May this be the movement of the particles making water when your finger penetrates its surface --- the way a leaf takes in the wind --- the sound the ocean makes when caressing the sand of the beach, or the seemingly simple way of members of the human race to unconsciously control their tone of speech, the thousands of movements of the muscles in their faces or the movements of their eyes. 
Now, he had lost quite all of the blindness the existence of O. had made him accept. A blindness of senses everybody would accept if to be given the O. of his life, but not having to accept it was the privilege of those who had really been given the O. of their lives. 
However, things were different now. It was not that O. had physically gone, rapt away by some explicable or impossible decision of fate --- No, physically, she was still out there, under his very nose. What had been rapt away was the bond that had once unified the person herself and his idea of O. 
You have already learned that she was alone again, and knowing about the accompanying change upon her character that seemed to be temporary, you may assume what had happened if been told that she was the old way again --- but ignoring him even more, being blind for the sensations of sensual perception. 
We must go back in time more than half a year to understand about the cause of this sudden blindness, impersonating Y. and having a look at her boyfriend in these months. 
At some time around January, Y. had been together with a boy, and though I don't really remember whether I've given you a more detailed description of this person already, we shall do this now. He changed girlfriends very quickly, a relationship just lasting some months; Y. must in some way have been fascinated by that boy who appeared to be interested in history and science, though he was mostly learning things automatically rather than really understanding them. Ignoring the fact that Y. seemed to change boyfriends quite quickly, too, this boy was in some ways proud of such relationships, while Y. was really searching for something, it seemed. He couldn't offer her this something. 
For that reason, it was her decision to quit that relationship once and for all, and though our protagonist had somehow felt that this was to happen, he had remained silent. Today, Y. was over some boyfriends more, while she seemed to be alone now again, keeping up a friendly attitude towards him all the time. Her friendship to G. seemed to have splintered long ago as it had been too close, and her singular and best friend at school seemed to be another girl she was with most of the time. 
His eyes searched the trees outside the library for a movement, but everything was keeping still. People around him made muted sounds, and all the world seemed to stand still while he was writing, hammering at the keyboard in front of him, remembering what had happened so long ago. This boy had also gone over several girlfriends, or rather they had overcome him, I guess. 
Back to the close present: L.-B. had phoned him on the 24th of October, and even once before since that tragical scene some weeks ago. He realized he couldn't fight her growing fondness, but had to accept it, ignoring it as best as he could so as to stop any possible progress, yet without hammering her soul. She'd have to be faced with an ignorant, not-so-intelligent and sensible boy to learn he wasn't hers at all. 
P. was now sitting next to him, reading in a book, and just some minutes before, she had refused to read the chapter he had prepared for her. As she didn't know about the contents and had given reason for it --- she didn't want to start with anything else if she wasn't forced to while reading another book --- he accepted her point of view. Destiny had chosen this universo to work out this way --- or his mind had, or whoever was in charge of controlling one's flow of fate. 
The world had been normal until that very moment at the end of L.-B.'s call --- or, in fact, it was just becoming normal and had been spinning all around just before. Who could judge this? 
The last days, he had been recovering slowly from a shock that had gripped his complete body. Now, equipped with information as you are, bursting for the explanation, we shall start with the report. The report how the tombstone was set up, and the description of the person who chose the letters engraved in the cold, hard stone. A merciless report of a final farewell. 
He had just answered some mathematical problems to L.-B. on the phone, when he realized she was finished and now frantically searching for more topics to talk about. She wanted to share everything with him, while he couldn't help but listen quietly all these times, just breaking his silence with the sound of air blowed through his nose now and then to express a laugh he didn't really feel. 
This time, that laugh would stick in his soul. L.-B. mentioned the boy whose character has just been described, commenting on his peculiar, offensive and well-known way of changing girlfriends. He wondered how L.-B. suddenly came to give her opinion on that boy, but lovers may do strange things, and he didn't dare ask her for that would probably lengthen the one-directional conversation that was so hard to endure, and the more he wished for its end, the longer it would become. 
However, this time, she had good reason to talk about that boy, though she didn't know a thing about the effect this would have on him. Not the glimpse of it. 
It took him nearly a second to understand the name of that boy's new girlfriend, for his mind seemed repulsively, unwilling ta accept such a thing to come true. 
It was impossible, unnatural, against all order that had been maintained in that world of cruel chaos --- till now. 
And for seconds, minutes, hours, a night and a day he'd just believe it half-heartedly; It could not be true, he had to have been mistaken. 
The name L.-B. pronounced --- so he thought --- the name of \emph{O.}, and she added that she had just realized when these two people came to university again, after that tragic holidays. 
The next thing he did was breathe out, so as not to irritate L.-B. by laughing once more at the sharp edges of the shattered glass of life's mirror. 
He felt the perfect actor, and the ultimate, ignorant and blind sheep that had just watched and imagined things that had never been true. And the very next day, Wednesday that is, he saw O. suddenly entering the same area he was standing in, and she said the follwing words: 
"Where have they all gone?" 
Destiny's last words, as if chosen from a play. If she'd ever been O., then this was her decision to tread a path without return, being alone and without hope, accompanied by devil's companions. 
However, there had still been a half-hearted reaction is his heart, a combined feeling of happiness and sorrow. It vanished soon when her new boyfriend appeared behind her. 
He could watch the two of them from a distance of some three or four metres, and he saw them stand close to each other, maybe not even having noticed his presence, for he had set up an aura of invisibility by looking as boring as one could. This was something he mostly did as the born hermit, and even P. had to surrender to this magic talent or burden, however it might be called. 
Their hands met. The moment of truth, as he'd still doubted truth and reality up to this moment. He had \emph{not} misunderstood L.-B., the messenger not knowing the meaning of the information she transported over the line for sheer ignorance concerning the few words her beloved person had uttered in her presence. She had underestimated the importance of the spoken or written word. 
And he had underestimated O.'s shallowness. 
His love had always been based on the feeling that there was something deep inside that girl --- maybe there was, but she had betrayed this magic right now. For one second on this terrible Thursday, the subdued magic gave him a last sign: Having ignored him up to know, she had now retreated into the 'safe haven' of love to that boy, and could take a look at him. 
She didn't see he saw what was going on, and as she finally realized, her eyes moved away. For less than a second, she stared at him in the auditorium. This was the thing his trained senses had waited for, and he perceived emotions that made him think that she tried to understand his thinking. Probably, she wondered whether he was happy this way, and what she should have done or left undone in the past. 
Earlier that day, there had been a small struggle, but he had already cut the bond that had once been so strong. Her new boyfriend asked him for some information, and she was trotting behind, trying to find that information, too. Not a fraction of the friendship that had once linked him and that girl was to be seen in her movements, her eyes or her soul. Everything was subject to a terrible sort of containment. 
He remained invisible, reflecting the total ignorance she offered him. At the same time, he was helping the girl that was present when the first denial took place, the girl that still was in a perfectly stable relationship, with some maths stuff, and one of P.'s friends with some piece of information technology. Or had all this happened later on? He was tired, and his memory would not be able to help him out. 
No, he remembered things well now: That girl had already started with asking him or was just planning to do so, while he had been in the midst of helping P.'s friend until that boy took the computer to do some "few seconds research". 
He found what he was searching for, but it seemed to be sheer luck. Even O. had not believed that this could be true, but it was. Fate just crashed the computer, but the information was still displayed. 
The girl he had been helping with maths joined in a short discussion about some biological topic, and the boy was resisting on some opinion O. refused to accept. 
It was a matter of taste and belief. 
A fundamental thing. 
The other girl kept out of it, and O. simply finished arguing, though he felt she didn't like to do so. She had certainly searched the presence of this guy to gain a feeling of safety, for he was very tall and \emph{appeared} to be intelligent, as you have read before. And all of a sudden, he knew why the boy was changing girlfriends so quickly: He was a temporary station on a path of development, offering the illusion of safety and shelter. 
Nevertheless, O.'s not knowing about it made him realize her lack of sensual perception, her denial of her own magic powers, her worshipping the power of ignorance. 
That Friday, the last thing he had done before he had to run to the bus was trying to explain something to P. and her friend, but they seemed to get it wrong and a small struggle between him and P. was interrupted by the bus' ariving --- He experienced the feeling of having run away, but he could do nothing about it. The part of him that felt guilty and insatisfied with his leaving in the middle of fighting a war he would have won was in constant conflict with the part that knew he should secure some distance from P., for he felt he'd probably come to close. Thus, he wondered whether he should contact her that weekend to explain things or wait until these two days had passed --- very likely, he should choose the latter. 
With O., there had been signs, of course. \emph{Many} signs of inbelievable clarity, and it was just now that he understood; the suddenly orange coloured wall at university, an impossible thing to happen by chance, and all those numbers..... 
Just this Friday, he had chosen some numbers he'd use for calculation and seconds later, the professor gave them the constant they should use. The number he had chosen before was 343, and it was valid for a temperature of 20 degrees. One may notice the coincidence of '2' being a number closely linked to O. and '343' being the number he'd seen just above him on the ceiling in that tragic night of the past, lying awake, his thoughts rushing somewhere around O. 
All that had lost importance now. The bond was broken, all love gone with the wind. 
The hermit was alone once more in the middle of the crowd, sensing the presence of other beings that could not recognize neither him nor the existence of fate and its signs. 
O. --- orange --- a word that may have developed out of 'or', the word for gold or golden --- was not a thing more that an imagined reality, the letters engraved on its tombstone describing what had happened in an imaginative, searching and attracted mind that had been lost for long. 
Now, the hermit had to secure his independence, finding refuge in continuous, but not repititive work and thought. Retreat to see --- become invisible to know --- and know to realize that knowledge may never be the solution for the problems of mankind. 
But it was path that could be chosen. 
Slowly, he was treading along this path, searching for the next empty page that would be filled --- eagerly, it might be hiding some hundred metres apart, but he could also stumble upon it every minute. 
Watch him, and please don't forget to come back so we can have a look at that page together! 
To be continued...
This month, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

Betrayal 
can be ignorance, 
invisibility, 
lying, 
hiding, 
stealing --- 
or simply 
plain love. 
\emph{W.G.}

Can you see the ball 
the children use to play? 

If you can, 
is your seeing sharp enough 
to make out their happy faces 
and all the smiles jumping around 
at this place that had been a graveyard 
some hundred years before? 

What about your watching 
the wrinkled face of a grandma, 
standing there, 
watching, 
smiling, 
crying, 
for the first person she had ever learned 
to love 
may be found below the feet of these children? 

Her love is still alive, 
vividly on a strive 
to join the man who'd betrayed 
her being just most openly delayed --- 
A wave of lost emotion, 
long gone devotion, 
nights of staring 
at the flaring 
of her fire. 
He'd been a liar, 
but he had not possessed her love. 

If love be a dove, 
she had catched it with a glove, 
and he had lost what she had gained: 
The love she'd attained 
had been given to her without 
the knowledge of this lout, 
and he shall never realize 
the bigness and the size 
of what had happened --- 
for she would withdraw, 
not bound by any law, 
leaving him alone in crowds 
of ignorant and lonely louts; 
She had received the biggest gift, 
and he had lost a chance so swift. 
\emph{W.G.}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_Second_Era.tex"
%%% End:
