Hello all of you out there, 

Many changes have gone through me. I cannot withstand to pass my experiences on to you, for I have betrayed my mind so often it has ceased to follow me completely. Maybe I have to share so as to receive my lost conscience back. 
I will start with a poem I had begun to built out of long-lost words more than a yeat ago: It fitted back then, it shall also fit now. 

[quote]
All that we see 
whether be or not to be 
whether to you or up to me 
is interpreted by our lonely wits; 
cut up in tiny bits, 
patches glued together; 
some just out of leather, 
or tiny, fluffy balls of wool; 
Somebody sitting on a stool 
keeps always watching, 
his feelings touching
the depth of our souls 
in burning emotion 
waking long-lost devotion 
leaving us with our notion 
to cross ourselves 
ending up on the shelves; 
read by the witty, 
but understood by the mad; 
the crazy and distorted pictures 
lost in everlasting mixtures; 
and clear is mixed and mixed is clear, 
black and white are to be grey, 
and only the crazy one may see 
what is to be. 
[/quote]

The title of the post that should have contained this poem was "Madhouse Inhabited". It should habe dealt with the dance of life catching us in it's magnetic maelstrom, and the truth of this world that can only be found in mad eyes. Mad eyes that are judged to be mad while we're looking through our own... 
Madness is still with me, and I cannot help to give it up --- as we are always accompanied by our death only to be alive, madness' company keeps us sane. Right now, I feel like I'm much closer to madness than to sanity. But you shan't be left with these confused words without explanation. 
Your first question will most certainly be: Why has there been such a long break? So much empty room? 
My life has not been empty. Well, it has. As I now look back, I have learnt how to deal with something completely different --- I have for the first time of my life worked in a real team. And it had made me happy, though it had drained me. But before we can have some deeper insight into the more and less recent happenings, you shall be confided my thoughts on the 24th of March at two am, in the middle of the night, thoughts I had written down and just now found the time and power to continue... Now, it is time for you to learn about reality. 
This night, at about two pm, on the 24th of March, the second era had ended. This was definitely the time when I had slowly begun to realize that a joyful --- because painful --- time of my life had come to an abrupt ending. While writing down these words, I'm lying in my bed and my eyes are slowly filling with tears, tears of sorrow, tears of final knowledge of a former alien world. I had thought that I had known a lot about this place we live in, but I had not --- now, my character and my innermost soul had been overturned. But before I finally continue writing the story, I have to express the pain the months without laying down a word had given me --- once, I had even started, done a poem and found a title --- "Madhouse inhabited" --- but this was all small now, and a span of time that had been only a few days had been stretched out to years. We will now be able to follow a way from confusion through aggression and an inexplicable extent of work to minutes of blissful, now finally mostly absolute farewell. This is what I have to tell, and finally it's 'me', not 'him', who tells a story of gaining a new life, a life of self-confidence and insight into emotional, abyssal graveyards. After this second era, that might be finished after just a few chapters, impressed by remembrance and newly gained inspiration, a short third era is to follow, concluded with a longer fourth era. What might happen after that, I dare not tell --- the plan of my life is yet to clear up to the beginning of the first era, so that I must fear (or hope) it will not be fulfilled. But let's finish this introduction here now and start to drink in the detail of mental pictures, of memories, concluded by a dance of farewell with O., the two of us being alone on the dancefloor... 

[u]Let's start with this drink:[/u]
\textbf{[u]The Bottle of Chaos[/u]}
First of all, his best friend had found himself a girlfriend --- L.-B. Then, around Christmas time, P. had ceased not to be been in a relationship. As if this wasn't enough, very important exams were waiting to be taken --- by all of them. And in addition to that, there were many things that had to be prepared for --- the final farewell. They would all take part in that. 
This is the moment to tell you, the reader, that I have lied --- in one point, that had not been so important for the story up to now, but that will explain what "the final farewell" is all about. This lie was a lie of concealment, but most people had found out who he was, nevertheless. Still, people like O. and G. stayed unknown, though his best friend had his assumptions. The problem was that he knew about B. --- he had told him --- and about L.-B., of course. But taking into account he still did not seem to know who R. was, he wondered how far he had really followed his story. But even if nobody would read it --- it was his story, his emotions, his life in a nutshell. My life in a nutshell. And just right now, when he was searching for a good position in his bed to continue writing, he looked at the clock: It was close to 3:43 am. First, let's tell you about the lie: I have not attended university yet. It took all place at school, with teachers, courses, pupils and all that. It's 3:43 now, the time when he had first felt that there was some kind of fate linking him and O. 
Things have changed now, you will learn soon. But first, let's continue with the sudden reign of chaos --- tomorrow. This night, the outline for the chapters to come will be made, no more --- then, I shall sleep and finish this chapter before the sun goes down again. 
And that was the moment when my notes from that night ended. Ended to be concealed for a long, long time, but still they are as vivid in my mind when I read them as if they had just been written down by myself. By the self I had once been, by the self I want to be again... 
I have found this document with some further notes and keywords I had left with it, and I want to tell you all the other things that had moved the swirling ingredients of my bottle of mind that evening of the final farewell. That most important, most wonderful evening in my life up to now... 
Though my mind is currently fading, losing it's once owned clarity, I will try to regain it to remember my brightest memories in all their brilliance. Maybe, this will be the path to healing my painful, unseen disease... 
The "Final Farewell" shall be the main topic of the next chapter, and it shall mark a change of my existence. Now, I will tell you about the persons that have influenced me up to then and are still influencing me now --- underestimated beings, more powerful in their subtle actions than I had ever expected them to be. 
To prepare you for what is to come, I shall tell you that I am German, but English feels even closer than my mothertongue, though I have learnt it at school. English seems to be the language of my former existence before I was even born, and it's anchored far deeper in the twitched paths of my mind than anything else. 
At the moment, I am studying physics, and that said, I have no lie left that I have not told you about. From now on, you are much closer to me than my closest friends. 
The bottle of chaos has been opened --- let the plays begin! 
It was January, and all my friends and me were on the way to attend the most important exams of their lives up to this point. All were in a rush, time was more valuable than ever, and his best friend found himself a girlfriend. Even worse: A really complicated girlfriend, L.-B. Now, his best friend would more than once contact him via phone or internet and talk to him about L.-B.'s newest inventions to make him feel bad. The problem was, that it felt more than clear to both of us that L.-B. seemed to be after me, in fact. She had seemed so all the time, and she let him feel it. His best friend, however, stayed loyal to both of them and did anything to please her until he had denied himself. That was the point when I told him to stop, but he didn't listen. He went on. He changed more and more, some other friends planned to go and rescue him in a childish manner, but it was all in vain. His former self had been buried by the power of a forcing feeling and he could not escape it, nor could anybody rescue him without risk to destroy his soul. With his best friend self-imprisoned under the rule of a dictator, I had to turn to others --- and to myself. 
The most important tests of our lives passed faster than we could ever have believed, and though I felt I had performed badly, I had best results. And I was tired to the death, and this state would last --- in fact, I'm still tired today. Tired so strongly I cannot even concentrate enough to keep my thoughts in a straight line for minutes. I hope you will understand and try not to notice my bad and far-too-simple English and my chaotic style of writing. My thoughts had been enclosed in a bottle of chaos for over a year now, and the bottle has just exploded as my brain has ceased to obey me, leaving me searching for words. 
But we are still in the past, in the time that followed the tests. The weeks that should have been full of recreation and sleep, but had been invaded by new ideas that took over the what should have been the boredom of recreation. This was the time when I had silently given myself into the hands of an exhausting fate. 
It was in these months when I learned that one of P.'s best friends had become lesbian --- she had always been very friendly and still was, but her new girlfriend was far too old for her and had an impact on her friendship to P. They had been very close friends, she had living only a few houses apart and they had met regularly. Now, P. was left in a lost state, and I was lost with her. As lost as I had always been, and still was. 
I had had long phone talks with P. then, and we are still best friends, though time has physically seperated us for more than half a year with the exception of very few occasions. 
But I am again not sticking to the past. Back then, we could be together and wonder about the solutions to infathomable mysteries of the surrounding society. But we had never really talked about O. or anything that really closely adressed me. There was some privacy I would never give up to anybody except this collection of words here. 
B. had also be of concern in this time, when she had started to ignore me after I had talked to her a lot via the internet. She had felt harassed, I learnt later on. The thingy she had blocked in the past was blocked again, for a long time now, and when it was unblocked again weeks later, everything I had commented there --- all of my comments I had put in so much thinking --- had been deleted. 
A wild fury came over me. I controlled myself and asked for explanations. She had "cleaned up" and deleted all things that had not been so important. Why does one delete comments? She claimed it was by chance that some of my comments had been victims of this mass-murder. I explained to her that she had deleted all my comments. And she accused me of knowing too well what I had written. 
This was the moment when I started to believe that I might not have overestimated her. But maybe she really was some kind of artist you could not deal with. An artist that could not control her own rage sometimes, offering destruction to free herself again. 
And I had never really been free, not since my childhood. 
R., B.'s best friend, had also affronted me, and though she had made her small attack a bit less agressive before it was published, I still felt uneasy about it. Nobody knew about my queasy feeling about it, but friends with similar thoughts passed this feeling on to R., and the message must have made it's way through B.'s family to finally reach R. You will learn more about this in the story of the "Final Farewell". 
But now, we shall stick to a type of chronological order. I will try to concentrate as much as possible, though I'm currently sitting at a train station, waiting for a ride to work before I may finally come home. The first train has already passed, I was too slow --- but maybe, fate will grant me another chance. 
But I promised you to stick to the story of a past that is more present now than ever. Dancing was the art that began to fascinate me more and more, and I began to watch some of the dance shows that flooded the country and took records of all dancing films I could get. It was to be my escape from the reality that was yet to come. 
That time, between the most important exams of our lives and the final farewell, I must have been happy without realizing it to the full extent of happiness' glory. My thoughts about what could have been and what would be were subdued, and warm feelings of friendship with everybody were flooding me so strongly I didn't realize I was loosing myself. My character was buried deeper and deeper, and I used more and more excuses to be like the others wanted me to be. The profiling system was perfect now, and it had left me presenting myself more shallow than I had ever wanted to be. 
Happiness is always accompanied by a voluntary or involuntary loss of depth. 
Now, I can see things more clearly, but you shall see for yourself what has really happened. 
I was more and more retreating into chatting with people via the internet, watching TV, interpreting complicated films (which made me feel better because it granted allowed my to feel a bit more individual again, in the end) and not reading anymore. 
It was this not reading that might have sealed my loss of depth, my character's breakdown I'm feeling now much more than ever. 
It was the aftermath of love. Denial and resignation. I couldn't help to tread the path so many psychologists have observed watching us, though I knew about it --- maybe, because I knew about it. Things we know about belong to the facts our minds forget about most easily. 
This train station with it's dark clouds and loud trains is clearing my thoughts up, giving them a brightness I have missed for over a year now, steady rain washing the mud old, once shiny polish leaves when you put on more and more of it without washing it off once upon a time. 
Finally, O. had been a symbol of happiness. And my questions about shallowness or depth, happiness or depression, finally made sense... 
L.-B. was more important in these days, or maybe just far more active. Now, she was my best friend's girlfriend and she gave both of us a hard time. I tried to keep out of it, but when my best friend told me about all her small difficulties I had been forced to learn about in the last years, I decided to try to change her. It was some time after they had come together, that I actively contacted her and tried to make her think about her own being. She didn't change her position in any way. And finally, after weeks of ups and downs, I had to give up when her mother, a teacher, accompanied her on the line and handed her the words she was to speak. I had been close, and she must have felt, for she did not see any way out anymore... 
So the only way out of her self-made imprisonment was to throw me out of her mind. And she simply told me, with a few words. This was not my way to give up, I kept talking to her, and she had to react, making things even more complicated --- for her. Soon after I had finally started to ignore her, too, she adressed me again and asked me whether I wanted us to stay friends. I told her that everything was fine, that I had never wished to make her feel uncomfortable --- and that we could certainly stay friends (though, in fact, I had never felt really friends with her, despite --- and because --- everything she had done). 
This state was to last some weeks, and finally, she told me that "I could phone her some Sunday as I had done in the good old days". 
No, you're right, I'd never ever phoned her. Maybe once in those 9 years to ask for a homework when I had been ill --- but that had been it. She had always be the moving part in her self-invented machine, and she had moved driven by a force unknown to me. 
All these ups and downs were, to my distress, not helpful to change her in any way. She would stay as she had always been, and I cannot wonder anymore where my best friend's former character has gone today. 
But I do not want to talk about L.-B. anymore --- certainly, she also had a small role to play on that occasion that accompanied the evening of the final farwell, but there is much more to come. Just this very night, I have learned much more about myself and how my life might be than in the last weeks. 
But for now, we are still stuck in the past and awaiting the final farewell. These weeks preceding that most important event had left me searching for closer friendships and new social groups. I had found my destiny in a small group of people who also liked my favourite book and talked to them on the internet, but soon, the lack of time took that happiness from me. Nevertheless, I learned that there are many people out there, more than I had ever expected. 
Humans like to misinterpret things by applying their own perspective, and I certainly had. 
For now, I shall call this chapter finished. The Final Farewell will be an event full of complex communication, lost emotions and new people that had been underestimated up to then --- people, that are to play more than a small role in my life. 
I hope you are still with me and look forward to our recatching the present, a time that is even more chaotic, now also including my work as student, accompanied by social interference. 
To be continued...
This month, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

A love be hidden in a chest, 
laid there to unwillingly rest, 
by one disobeying its truth --- 
lonely and helpless this love be divined, 
not ever be found by the hiding mind; 
an angel known to our soul may find 
what we have laid down 
in a moment of frown. 
\emph{W.G.}

Endless fear is creeping up, 
grabbing my soul, eating me up, 
leaving my heart banging alone, 
forever shaking in similar tone. 
\emph{W.G.}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_Second_Era.tex"
%%% End:
