Hello out there, 

you must know that this chapter was planned to be one of the most important ones. However, time has postponed my writing for so long that most of the further details have been lost. While I am now talking to people you are still to learn to know, I try to remember what has been, and how I came to be the person I am right now. It was this special evening that made my heart twitch, that changed my whole sight on the world. But we shall begin right now, you shall see what had happened of such utter importance. 

[u]Dance of freedom:[/u]
\textbf{[u]Final Farewell[/u]}
It was an evening most of them had looked forward to. For me, it also was an event I had been wating for --- but at the same time, I had feared this moment as the last thing they all would share. After that evening, he knew, their lives would start to change directions, diverge in the different ways the particles of an explosion take. 
I would not sit near to O., but to Y. and P. --- together with our families, we all were placed on the higher level in the big hall that took all of them. O. and G. were both placed below with their families, while G. was even standing in front of them all, talking on stage, greeting them and announcing the first scenes to be shown. All in all, the scenes on stage were not so interesting --- of far more interest was what would happen in front of it, on the dancefloor. But for now, we are still sitting on the balcony, with my parents, Y. and P. close to me. P.'s best friend was there, too, and when the music began to play, I started to take some pictures. P., sitting in front of me, was blinded more than once for I was using a big flash to take in more details. 
This was the slow way the evening started, and soon, all of them began to eat something, only smalltalk connecting their lives right now. Once, when I went up the stairs after talking to some of my friends down there, I was intercepted by R. She began to address him in a way he had never seen about her --- she was ashamed. She had said something about him she didn't mean, I had already told you that she had learnt about that from B. And now, she was apologizing herself. I was reacting quite easily, telling her it was not of such importance, and finally, she was smiling. The brother of one of his friends was passing them by and told me that he would not have made it that easy. But I had, that evening was going to be one of the last times we met, her descending the stairs and me ascending them to reach the balcony again. 
This was how the more interesting part of the evening began. When I went down again, the dancing began. First, the dance with L.-B. was to be endured --- to be truthful, she was dancing like a stick. My best friend knew that, but he didn't flinch, he just watched. It seemed to be all she wanted, and we danced once more, me without emotion, until the evening began. I danced through all the friends I've had --- except P., she didn't want to dance, so it was her best friend's turn. 
The most time, I danced with a girl you still do not know. She was very intelligent, nice and a good friend of P.'s, and it was very difficult to find a colour to account for her multilateral personality. There was something black and grey inside her, but also some hidden colours... she was very interesting, and we will call her N. so as not to cunfuse her with other colours. 
I liked her, we understood each other, and we had become friends. Whenever she had a technical problem, I would help her. But this evening, her boyfriend became jealous of me ---  the first time in my life, I was regarded as somebody who could be --- dangerous. Somebody who was attractive. Finally, he would force her to leave with him when the evening was nearly finished. 
But yet, something of much more importance was to happen. Something, that would make the world turn faster for a moment, only to lead it to a sudden halt forever after, maybe. A few seconds with closed eyes and open mind... 
It was all about dancing. Dancing with the \textbf{one}. I was standing in front of the dancefloor, watching a dance show done by G., O. and some others I knew. They had all been to the same dancing school I was attending now. 
It must have been this evening that O. was close to being single again. The details were and are still out of reach, but she seemed happy, and nevertheless, there was something going on inside her. 
And it was just a few minutes later when I shily asked her for the next dance. She did not seem surprised, maybe because I had repeated this wish some time before --- she must have known this was to come, but she had never reacted. Now, she had to. 
Hands met, smiles shone, the music took our minds to form a last unity just for a few moments. It would not last for long, but long enough to \emph{feel}. 
It was easy, and she was flying --- my hope for a camera to take us in seemed to be frustrated --- I was not there to take them, and my father who would eventually have taken one was still up there. We were alone, and the moment filled my mind. It was a simple dance, all I could do, but nevertheless, there was fun and happiness accompanying the situation. And sorrow. 
She was a bit reserved, her feelings seemed piecewise simulated, but still, there was a subtle glow emanating from her face and her smile. It was as it had always been... 
However, the dance was gone very fast and the music was too happy for the moment. I might have danced with a glaring puppet of a fairy's world in the midst of reality. 
After that, we stood next to each other for a while and watched the scenery, and she appeared to ignore my looks that asked for another dance. She seemed to postpone it to another time that might never come. That should never come? 
Then, her boyfriend took her away, a few minutes later. 
Happiness without proximity, eagerly awaiting something in silence, quick departure. Left deranged. 
Silence in the middle of the crowd. 
Silence ever after. 
This was the final farewell, the short goodbye that had to come once upon a time. And it was fast, and somehow --- satisfying. Suddenly gone, last emotion conserved. 
Rotating on, dancing with the others to integrate this last emotion, to understand. 
Hands meeting and parting, emotions departing. Happiness that had been simulated was now felt, and when all of them were on the stage together, singing along the last song unified, dancing, memories passing by. That had been before the final farewell, which had been the final cut, the opening of a new life. 
Right now, I am sitting in the meeting place of my old school, the place where I had been supposed to meet mey best friend. I had come too late, he was already gone, and memories passed me by. The right mood... 
Remembering what hat been. Rotating flashbacks. Just seen the people who had teached me to dance. 
Seconds of eternity, longer than anything ever been. You can name a function that produces all real numbers by just using those between one and two. By just using the smallest interval you can imagine. 
The limits of imagination had had expanded that moment of the final farewell to eternal infinity. Never fading, just differently struck by sun's rays, shoven aside or not thought of. 
Neverfading memories are the most valuable things we have. We should keep and part them, as infinity can never be lessened. 
Living into another world. This place was so different that it might have been a parallel universe. Time, the unidirectional dimension, parting them. 
Right now, only books can travel through the ocean of time and memories. Movies try and sometimes succeed, but they can not hold what humans can feel. Not even books can. Not even humans can... 
Watching birds, eating an angel cake. Dreaming. Seconds away from getting lost. 
As quickly as the world had been overturned, the memory had been conserved for the evening, for the life. I stayed calm until I was home, and I will never forget the following night that brought me back to writing again. You need time to understand, and will to go on. This moment, I had both. 
The interesting feeling of eternity shrinking and growing, shrinking so small it might last forever inside your mind, and then growing so big you see it can not be held. 
Tired you are by turning worlds, having been thrown by the tossing waves of life's watery stream; thy eyes closing without a word, thy mind racing even faster. 
And then, there was just sleep and silence. No more sounds, only silent dreaming, without a word. The most important moment of my life up to now had passed --- she had gone. Have I ever seen her since? 
Once, twice, thrice, maybe even more often I have seen her from some distance --- that is, I have never seen her again. 
Would I want to see her again? Disturb a memory still partly kept untouched, uninfluenced by the pain we lay upon ourselves when love becomes reality? There was a longing for somebody, but it was indefinite again. And the memory was most precious. 
Much more memories were to come, last moments, goodbyes --- but the first one was always the most influential. 
An era had ended with a swirling dance, another one would surely come. 
To be continued...
This month, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

Memories running, 
trotting around, 
making a stomping, 
teargrinding sound. 
Feelings, emotions, 
terribly bound, 
Long-lost devotions 
hitting the ground. 
\emph{W.G.}

Merry-go-round, 
wheels and their sound, 
behind paths of the living, 
ghosts show all their giving, 
memories undone, 
new emotion won. 
Round and round and roundaboutly, 
life is turning, turning loudly. 
An eye's blink may make smiles so stern, 
a year's sake may make hearts go burn. 
Happiness is took so fast, 
happy be who neither know
nor realize what is to come, 
living life in boredom. 
\emph{W.G.}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_Second_Era.tex"
%%% End:
