Hello everybody out there, 

you have waited long, very long, and many things have happened since the last time I talked to you. So many things, yet so short a time in my memory... 
It had been about friendship, giving up so many times on too many things and finally about working at a speed completely not comparable to what I have described the last time. I am still to confused what exactly is the essence of these months, what will stay with me and what will be washed away by time quite soon. However, what really made me write again happened tonight, in the other world that's always close to us, in a \emph{dream}. 

[u]Memories undeleted:[/u]
\textbf{[u]Dreams resist Time[/u]}
It is now the time when there should be some moments without any sorrows, without any work --- the holidays. The past months had been full of learning, sometimes not very rewarding. Not a second had been really off-duty, as duty was self-imposed and always around... 
Studying had become a constant flow of learning, in the evening talking to others, taking part in their lives, and giving oneself up totally. My feelings were lost, only to return when watching a film that was so full of emotions I could not help but cry and feel again. And some people I had learnt to know at university became so close friends that they nearly understood me, that is, the \emph{current} me living in that moment of time. They had given me strength to carry on, to not lose the daily fight against the heartless machinery trying to force us to continue our studies. In the last weeks, however, there was only silence, silent friendship and silence inside me... 
In the last days, however, I really felt there was no friend such close anymore. I escaped in another world, a world of movies that are more easily understood, an adventure game that did not take too much concentration, and I just let my mind fly free, my thoughts running the paths they wanted to take. And finally, they chose a path that made me continue writing here, a path of memories, which still seem to be among the most valuable things I possess, as nothing ever got so close again as O. once did... 
She had not been in my active thoughts for very long a time, not even that Saturday, when I met my comrades from school on a birthday party. Of course, neither G., nor O., nor anybody else with such a name was there --- however, there were people I liked a lot, too, and they made me realize that it was now time not to study, but to do something completely different, to get some time off. And my mind did exactly that tonight, it got back to the past, presenting eternal memories and dreams that I ought to have had, but never made. 
At some time around morning, my dreams focussed on some kind of party, and all the people from the past seem to have been there. However, they were not clearly distinguishable, but two other persons were --- with two elegant umbrellas (or had it been two hats?), they arrived at the party, and as I seemed to have been my old self, I just waved at them and made some place those two could talk to the others. 
Of course, it was G. and O. who had arrived. But then, the dream went differently, not that close anymore to the reality I had lived through so many times. O. commented a bit louder so as if to address everybody, that nobody had greeted them in any way, and the schemes I had thought the two of them wanted to talk to appeared to vanish, joining the fog of the things around us I did not focus on, though I still remember it was a environment somewhat colourful, free and open, featuring some kind of elegancy, wisdom, eternity and loneliness at the same time, while not seeming inappropriate for a party. 
Quickly, I turned back to her, told her I had greeted her by waving at them, and smiled. Now, I realize that this must have been more brave than most things I had done before, though it was --- in fact --- not very special. However, it would show I wanted to please her, and that was something I had never really been able to express before in her presence. In this dream, she reacted realistically, a bit unhappy and hurt, but nevertheless hiding a warming smile in her face. 
A few seconds later after I had looked into her eyes, everything vanished into the void of dreams, and then, the two of us were alone together, closer, and talking softer. I cannot remember the exact words, but I embraced her, and the realized it was O., and embraced her as strong as I could, not wanting to let her go again. And that was the moment when we would have to kiss, and though I can't remember the kiss itself, I remember that it was to come... 
All of a sudden in this unpredictable dream, I felt I definitively had to go somewhere, I did not know why, where and how long, I think it must have been as simple as going to the closet, whyever my self in this dream thought this moment was appropriate. 
The next thing I remember was being with somebody completely different, but somehow \emph{known}, meeting under similar circumstances, and just before the kiss should take place, I felt that something was not right, and even heard O. calling, and then the dream slowly broke off, though I think I made my way back to O.... 
How am I supposed to feel about this? Was this other person the picture of O. in another time, was the first person O. at all? The dream left me confused, and it was followed by a less emotional, but also confusing dream, in which I had to flee from a robber out of some flat with a wife that was suddenly with me. 
Peculiarly, I remembered all those dreams quite clearly when I woke up, and I never had such dreams before, I can't even recall really having dreamt about O. or a girl at all, and not in such detail. Maybe, something inside me is still searching for her, or for her memory, or for a way to travel back in time --- would I really want that? Almost certainly, this would destroy the \emph{me} I am now, and I would not be sure what it would be replaced with. Another me in another universe might have already had all that experience, but still, I think the different paths are somehow equalized. I have not been close to her, but have taken one of the most beautiful (though also painful) memories, and another self might have been close to her and not known a life without her, maybe not feeling how valuable that life with her is, and even another self might have broken up already without understanding anything. 
If all those are somehow equivalent ways, why not accept mine? Why do we always have to grasp the impossible? 
I just remembered another part of the dream, there was music, some kind of a band was playing a song about a deadly angel, which was sounding quite happy. Fragments all over my mind, and no complete picture forming itself. Let me close my eyes for a second. 
The scenery was back, but no more details can be made out, only silence. Why had \emph{she} come back? Am I still in love, and if, with her or with the phantom of her's that is the perfect picture of the person I will once fall in love with, the picture prepared for eternity? 
Maybe, the other one was G. --- no, it can't be, she looked different. What I recall is that the feelings toward "the other one" were not that strong. Was it a symbol for everybody else? A symbol made up to escape a predetermined fate? Am I just a runaway from a destined path, lying to myself? Maybe I am --- but I am not powerful enough to do anything about it. Though I do not think O. is my final destiny, my dreams seem to think so --- but do they only because they can only see the past? 
Nobody appears to be reading this, I even told some close friends about it, but they do not seem quite close enough... 
My eyes are becoming wet, I do not know what to do next. Maybe, just see how others are dealing with their lives to ultimatively deal with my own... 
Please be with me and help me understand what my life is about... 
To be continued...
This month, by Wilkie Goldentongue...

--------------------------------------------------------------
(If you want to comment on this, please start a new thread; this one is reserved for this story, my life, the story that'll never end, while the end is still near, coming nearer every minute; it's just around the corner...)

Captured in a dream, 
eternity's stream, 
long forlorn, 
of wishes born? 
Not a second to lose, 
it's dealing a bruise, 
and then there is time 
to remember this rhyme: 
Who is it calling? 
And why am I falling... 
\emph{W.G.}

Eyes wide open but nothing to see; 
she's not out there, but inside of me. 
Am I kissing a quantum mirage 
inside that painted entourage? 
Another reality captured in dreams. 
Do I remember? Oh yes, it seems, 
Slowly approaching and stepping back, 
due to my special disgusting lack 
of courage, to just walk up there and say 
I'll love you, come whatever there may. 
\emph{W.G.}

%%% Local Variables:
%%% mode: latex
%%% LaTeX-command: "latex -shell-escape -synctex=1 --file-line-error-style"
%%% ispell-local-dictionary: "british-ize-w_accents"
%%% TeX-master: "../My_Life_in_a_Nutshell_-_Second_Era.tex"
%%% End:
